\documentclass[11pt,a4paper,draft,DIV11]{scrartcl}	%twoside
%\usepackage[a4paper,hmargin=2.8cm,vmargin=2.8cm]{geometry}
\usepackage[utf8x]{inputenc}
\usepackage[bookmarksnumbered=true]{hyperref}
\usepackage[color]{showkeys}
\usepackage{scrtime}
\usepackage{amsmath,amsthm,amsfonts,amssymb}
\usepackage{dsfont,wasysym,mathtools}
\usepackage{gitinfo}

% Footer:
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\rfoot{Page \thepage}
\lfoot{Commit \gitAbbrevHash \ on \gitCommitterIsoDate \ (\jobname.tex)}

% Set enumerate environment using roman counters
\renewcommand{\theenumi}{{\rm (\roman{enumi})}}
\renewcommand{\labelenumi}{\theenumi}

% Nicer marginpar with smaller font
\let\oldmarginpar\marginpar
\renewcommand\marginpar[1]{\-\oldmarginpar[\raggedleft\footnotesize #1]%
  {\raggedright\footnotesize #1}}

%%%%%%%%%%%%%%%%%%%%%%%%% Theorems etc %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newtheorem{thm}{Theorem}[section]
\newtheorem{cor}[thm]{Corollary}
\newtheorem{prp}[thm]{Proposition}
\newtheorem{lem}[thm]{Lemma}
\newtheorem{dfn}[thm]{Definition}
\newtheorem{exm}[thm]{Example}

\newtheorem*{rem}{Remark}
\newtheorem*{hyp}{Hypothesis}

%%%%%%%%%%%%%%%%%%%%%%%% Gustavo's aliases %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\R}{\mathds{R}}
\newcommand{\N}{\mathcal{N}}
\newcommand{\K}{\mathcal{K}}

%%%%%%%%%%%%%%%%%%%%%%%% Notation %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\ad}{\operatorname{ad}}	% abbreviation for iterated commutators
\newcommand{\fock}{\mathcal{F}}		% fock space symbol
\newcommand{\di}{\textrm{d}}		% differential (for integrals)
\newcommand{\Lcal}{\mathcal{L}}		% calligraphic L
\newcommand{\Ncal}{\mathcal{N}}		% calligraphic N
\newcommand{\Kcal}{\mathcal{K}}		% calligraphic N
\newcommand{\Vcal}{\mathcal{V}}		% calligraphic V
\newcommand{\Hcal}{\mathcal{H}}		% calligraphic H
\newcommand{\Ocal}{\mathcal{O}}		% big-O, order-of
\newcommand{\tilV}{\tilde{\mathcal{V}}_N}		% symbol for the smeared potential energy part of the hamiltonian
\newcommand{\tilK}{\tilde{\mathcal{K}}}		% smeared kinetic energy
\newcommand{\estlist}[2]{\underline{Line \ref{l#1}, summand #2:}}
\newcommand{\nestlist}[2]{line \ref{l#1}, summand #2}
\newcommand{\Nestlist}[2]{Line \ref{l#1}, summand #2}
\newcommand{\hc}{\mbox{h.c.}}		%hermitian conjugate
\newcommand{\scal}[2]{\big<#1,#2\big>} % scalaer product
\newcommand{\cc}[1]{\overline{#1}}	% complex conjugate
\newcommand{\Rbb}{\mathbb{R}}		% real numbers
\newcommand{\Cbb}{\mathbb{C}}		% complex numbers
\newcommand{\Nbb}{\mathbb{N}}		% natural numbers
\renewcommand{\Re}{\operatorname{Re}\,} 	%RealPart
\renewcommand{\Im}{\operatorname{Im}\,} 	%ImaginaryPart
\newcommand{\norm}[1]{\lVert#1\rVert}	%Norm
\newcommand{\ev}[1]{\big<#1\big>}	%expectation value
\newcommand{\ph}{\varphi_t^{(N)}}	% solution of N-dependent Hartree equation
\newcommand{\phdot}{\dot{\varphi}_t^{(N)}}	% time derivative of solution of N-dependent Hartree equation
\newcommand{\phddot}{\ddot{\varphi}_t^{(N)}}	% second time derivative of solution of N-de Hartree equaution
\newcommand{\sqn}{\sqrt{N}}		% square root of N
\newcommand{\project}[1]{\lvert #1 \big>\big< #1\rvert}	% orthogonal projection operator
\newcommand{\Tr}{\operatorname{Tr}}	% Trace
\newcommand{\dxyNV}{\frac{1}{2}\int \di x\di y N V_N(x-y)} % abbreviation for the one-half integral dx dy NV_N(x-y) which appears everywhere
\newcommand{\dxyV}{\frac{1}{2}\int \di x\di y V_N(x-y)} % abbreviation for the one-half integral dx dy V_N(x-y) which appears everywhere
\newcommand{\tLcal}{\tilde \Lcal_N(t)}
\newcommand{\tLcalo}{\tilde \Lcal_N(0)}
\newcommand{\xn}{\mathbf{x}}		% x = (x_1. dots x_N)
\newcommand{\gradone}{\nabla_2}

\newcommand{\be}[1]{\begin{equation}\label{eq:#1}}	%begin equation with label
\newcommand{\ee}{\end{equation}}
\newcommand{\bd}{\begin{displaymath}}			% abbreviation begin displaymath
\newcommand{\ed}{\end{displaymath}}

\newcommand{\tagg}[1]{ \stepcounter{equation} \tag{\theequation} \label{eq:#1} } % add tag and label in align*-environments

\newcommand{\eqr}[1]{\eqref{eq:#1}}			%eqref with prefix :eq

%%%%%%%%%%%%%%%%%%%%%%%%% main content %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%\allowdisplaybreaks

\author{Bonn}
\title{GP equation}

\begin{document}
\maketitle

\begin{abstract}
 Gross-Pitaevskii equation, Bose-Einstein condensate with repulsive interaction, Squeezed coherent states, Bogoliubov transform, Mean-field limit, Hartree equation.
\end{abstract}

\section{Introduction and Main Result}
We consider a system of $N$ identical bosons with repulsive interaction. This system is described on the Hilbert space $L^2_s(\Rbb^{3N})$ by the Hamiltonian
\bd
H_N = \sum_{j=1}^N (-\Delta_{x_j}) + \frac{1}{N}\sum_{i<j}^N N^3 V(N(x_i-x_j)).
\ed
We assume that the unscaled potential $V \in C^\infty_c(\Rbb^3)$ is non-negative and spherically symmetric. The scaling is chosen in such a way that for $N \to \infty$ formally $N^3 V(N(x_i-x_j)) \to \delta(x_i-x_j) b_0$, where $b_0 = \int V$.

We use the short-hand $V_N(x) = N^2 V(Nx)$.

We are interested in the time evolution of factorized initial wave functions, which we see as a model for a Bose-Einstein condensate in a trap:
\bd
\psi_N(\xn) = \prod_{j=1}^N \varphi(x_j),
\ed
where $\varphi \in H^4(\Rbb^3)$ is a one-particle wave function normalized to $\norm{\varphi}_{L^2} = 1$. The time evolution is given by the solution to the Schroedinger equation 
\bd
i \partial_t \psi_{N,t} = H_N \psi_{N,t},\quad \mbox{with inital data } \psi_{N,0} = \psi_N.
\ed

The function $f_N = 1 - w_N: \Rbb^3 \to \Rbb$ is the solution to the zero-energy scattering equation
\bd
\left(-\Delta + \frac{1}{2}V_N \right) f_N = 0
\ed
with boundary condition $\lim_{\lvert x\rvert \to \infty} f_N(x) = 1$. The scattering length $a_0$ of the potential $V$ is given by
\bd
8\pi a_0 = \int \di x NV_N(x)f_N(x),
\ed
which is clearly indepedent of $N$.

The modified Hartree equation reads
\be{modHartreeEqu}
i \partial_t \ph = -\Delta \ph + \left(N f_N V_N \ast \lvert \ph\rvert^2 \right) \ph,
\ee
where we denote by $\ph$ the solution to the modified Hartree equation with initial data $\varphi^{(N)}_0 = \varphi$.

We expect that in the limiting case of large $N$, the dynamics of the Bose-Einstein condensate is well described by
\bd
\psi_{N,t}(\xn) \simeq \prod_{j=1}^N \varphi_t(x_j),
\ed
where $\varphi_t$ is the solution to the Gross-Pitaevskii equation
\bd
i \partial_t \varphi_t = - \Delta \varphi_t + 8\pi a_0 \lvert \varphi_t\rvert^2 \varphi_t
\ed
with initial data $\varphi_0 = \varphi$.

Note that for the unmodified Hartree equation
\[
i \partial_t \ph = -\Delta \ph + \left(N V_N \ast \lvert \ph\rvert^2 \right) \ph,
\]
so with $N V_N \to b_0 \delta$ we formally obtain the limiting equation
\bd
i \partial_t \varphi_t = - \Delta \varphi_t + b_0 \lvert \varphi_t\rvert^2 \varphi_t,
\ed
while in the modified Hartree equation $N f_N V_N \to 8 \pi a_0 \delta$, which by \cite{ESY2010} is expected to be the correct limiting equation.

\begin{thm}[Time Evolution of Factorized States] \label{thm:main_factorized}
 Let $\psi_N(\xn) = \prod_{j=1}^N \varphi(x_j)$ for some $\varphi \in H^4(\Rbb^3)$ with $\norm{\varphi}_{L^2} = 1$. Denote by $\psi_{N,t} = e^{-it H_N}\psi_N$ the solution to the Schroedinger equation with initial data $\psi_{N,0}= \psi_N$, and let $\gamma_{N,t}^{(1)}$ be the one-particle reduced density matrix associated with $\psi_{N,t}$.

 Furthermore, let $\varphi_t$ be the solution to the Gross-Pitaevskii equation with initial data $\varphi_0 = \varphi$.

 Then there exist constants $C$, $K_1$ and $K_2$, which do not depend on $N$ and $t$, such that for any one-particle Hilbert-Schmidt operator $J$
\bd
\left\lvert \Tr\left(J \gamma_{N,t}^{(1)} \right) - \Tr\left( J \project{\varphi_t}  \right) \right\rvert \leq \norm{J}_{HS} \frac{C}{N^{1/4}}e^{K_1 e^{K_2 t}}.
\ed
\end{thm}

\begin{rem}
$k$-particle densitys. 
\end{rem}

Literature: BBGKY, Grillakis-Machedon-Margetis, Pickl, Rodnianski-Schlein.

Organization: Lift to Fock Space. The Bogoliubov Transformation. Controlling the Number of Quantum Fluctuations by a Gronwall estimate. Time Evolution of Factorized States and Proof of the Main Theorem. Appendix on Generator-Estimates. Appendix on Hartree and Gross-Pitaevskii equation. Appendix: Bounds on the Bogoliubov Transformation.

Remarks on notation: We use the symbol $C$ throughout the paper for constants which might be redefined from line to line, but which are always independent of $N$ and of time $t$.
The notation
\[
  A \apprle B
\]
means that $A \le C B$ for some constant $C$.
Notice that we use $\sup_x$ as a short-hand for $\operatorname{esssup}_{x\in \Rbb^3}$. In accordance with \eqr{no1}, our notation has to be read as $\norm{p_x}_{L^2} = \left( \int \di y\, \lvert p(y,x\rvert^2 \right)^{1/2}$.

If we write expressions like $\nabla_1 p$ for any integral kernel, this means the gradient with respect to the first variable of the integral kernel.

Notice also that though $k$ maybe depend on $t$ through $\ph$, we do not indicate the $t$-dependence of $k$ explicitly anywhere, similarly for the other integral kernels $s$ and $p$. However, some lemmata are formulated for general $\varphi$ where the modified Hartree equation does not play any role.

The symbol $a^{\#}$ can stand for both $a^\ast$ as well as $a$.

\section{Fock Space Representation}
The bosonic Fock space over $L^2(\R^3)$ is the Hilbert space
\[
  \mathcal{F} = \bigoplus_{n \ge 0} L^2(\R^3)^{\otimes_s n} = \mathds{C}
  \oplus \bigoplus_{n \ge 1} L^2_s(\R^{3n}),
\]
with the convention that $L^2(\R^3)^{\otimes_s 0} = \mathds{C}$. Here
$L^2_s(\R^{3n})$ is the subspace of $L^2(\R^{3n})$ consisting of all functions
that are symmetric with respect to arbitrary permutations of the $n$
variables. Vectors in $\mathcal{F}$ are sequences $\psi = (\psi^{(n)})_{n
\ge 0}$ of $n$-particle wave functions $\psi^{(n)} \in L^2_s(\R^{3n})$. The
inner product on $\mathcal{F}$ is defined as
\begin{align*}
  \langle \psi_1, \psi_2 \rangle & = \sum_{n \ge 0} \langle \psi_1^{(n)},
  \psi_2^{(n)} \rangle_{L^2(\R^{3n})} \\
  & = \overline{\psi_1^{(0)}} \psi_2^{(0)} + \sum_{n \ge 1} \int dx_1 \cdots
  dx_n \overline{\psi_1^{(n)}}(x_1, \dots, x_n) \psi_2^{(n)}(x_1, \dots, x_n).
\end{align*}
An $N$-particle state with wave function $\psi_N$ is described on
$\mathcal{F}$ by a sequence $(\psi^{(n)})_{n \ge 0}$ where $\psi^{(n)} =
0$ for all $n \neq N$ and $\psi^{(N)} = \psi_N$. The vector $(1, 0, 0, \dots
) \in \mathcal{F}$ is called the vacuum, and is denoted by $\Omega$.


For $f \in L^2(\R^3)$, the creation operator $a^*(f)$ and the annihilation
operator $a(f)$ on $\mathcal{F}$ are defined as
\[
  \begin{split}
    (a^*(f) \psi)^{(n)}(x_1, \dots, x_n) & = \frac{1}{\sqrt{n}} \sum_{j=1}^n
    f(x_j) \psi^{(n-1)}(x_1, \dots, x_{j-1}, x_{j+1}, \dots, x_n), \\
    (a(f) \psi)^{(n)}(x_1, \dots, x_n) & = \sqrt{n+1} \int dx \,
    \overline{f(x)} \psi^{(n+1)}(x, x_1, \dots, x_n).
  \end{split}
\]
The operators $a^*(f)$ and $a(f)$ are unbounded, densely defined, and closed.
Note that $a^*(f)$ is linear in $f$, while $a(f)$ is anti-linear. The creation
operator $a^*(f)$ is the adjoint of the annihilation operator $a(f)$, and
they satisfy the canonical commutation relations
\[
  [a(f), a^*(g)] = \langle f, g \rangle_{L^2} \qquad \text{and} \qquad [a(f),
  a(g)] = [a^*(f), a^*(g)] = 0
\]
for $f,g \in L^2(\R^3)$. It is useful to introduce the self-adjoint operator
\[
  \phi(f) = a^*(f) + a(f).
\]


We will make use of operator-valued distributions $a_x^*$ and $a_x$, with $x
\in \R^3$, defined so that
\[
  a^*(f) = \int \di x\, f(x) a^*_x \qquad \text{and} \qquad a(f) = \int \di
  x\, \cc{f(x)} a_x
\]
for $f \in L^2(\R^3)$. For these distributions, the canonical commutation
relations assume the form
\[
  [a_x, a_y^*] = \delta(x-y) \qquad \text{and} \qquad [a_x, a_y] = [a_x^*,
  a_y^*] = 0,
\]
where $\delta$ is the Dirac delta distribution.


The number of particles operator $\mathcal{N}$ on $\mathcal{F}$ is defined as
$(\N \psi)^{(n)} = n \psi^{(n)}$. Eigenvectors of $\N$ are vectors of the form
$\{0, \dots, 0, \psi^{(m)}, 0, \dots \}$ with a fixed number of particles.


The Hamiltonian $\Hcal_N$ on $\mathcal{F}$ is defined as $(\Hcal_N
\psi)^{(n)} = \Hcal_N^{(n)} \psi^{(n)}$ with
\[
  \Hcal_N^{(n)} = \sum_{j=1}^n (-\Delta_{x_j}) + \sum_{j=1}^n
  \sum_{i=1}^{j-1} V_N(x_i - x_j).
\]
By definition, the Hamiltonian
$\Hcal_N$ leaves sectors of $\fock$ with a fixed number of particles
invariant and $[\Hcal_N,\Ncal] = 0$, i.\,e.\ $\Hcal_N$ conserves the number of particles. Clearly $\Hcal_N^{(N)} = H_N$, therefor
\[
e^{-it \Hcal_N} (0,\dots,0, \psi^{(N)},0,\dots) = (0,\dots,0, e^{-itH_N}\psi^{(N)},0,\dots), 
\]
so we have embedded the time evolution of the $N$ boson system in Fock space.

Using the distributions $a_x^*$ and $a_x$, we can express the operators $\N$
and $\Hcal_N$ as
\[
  \N = \int dx \, a_x^* a_x
\]
and
\[
  \Hcal_N = \K + \mathcal{V}_N
\]
with
\[
  \K = \int dx \, \nabla_x a_x^* \nabla_x a_x \qquad \text{and} \qquad
  \mathcal{V}_N = \frac{1}{2} \int dx dy \, V_N(x-y) a_x^* a_y^* a_y a_x.
\]
We call $\K$ the kinetic energy operator, and $\mathcal{V}_N$ the potential
energy operator.


The following lemma provides some useful bounds to control creation and
annihilation operators in terms of the number of particles operator and the
kinetic energy operator.


\begin{lem} \label{l:a}
  Let $f \in L^2(\R^3)$ and $g \in H^1(\R^3)$. Then, for any $\psi \in
  \mathcal{F}$,
  \begin{equation} \label{aNorm}
    \begin{aligned}
      \norm{a(f)\psi} & \leq \norm{f}_{L^2} \norm{\Ncal^{1/2}\psi}, \\
      \norm{a^*(f)\psi} & \leq \norm{f}_{L^2} \norm{(\Ncal+1)^{1/2}\psi}, \\
      \norm{\phi(f) \psi} & \leq 2 \norm{f}_{L^2} \norm{(\N+1)^{1/2} \psi}
    \end{aligned}
  \end{equation}
and
\be{agradnorm}
\norm{a(\nabla g)\psi}  \leq \norm{g}_{L^2} \norm{\Kcal^{1/2}\psi}.
\ee
\end{lem}

For $f \in L^2(\R^3)$, we define the Weyl operator on $\mathcal{F}$ as
\[
  W(f) = e^{a^*(f) - a(f)}.
\]
A state of the form $W(f)\Omega$ is called a coherent state.


In the following lemma we collect some well-known properties of Weyl operators
and coherent states.


\begin{lem}[Weyl Operators and Coherent States] \label{l:W}
  Let $f, g \in L^2(\R^3)$.
  \begin{enumerate}
    \item \label{l:W1} The Weyl operator satisfies the relations
      \[
        W(f) W(g) = W(g) W(f) e^{-2i \Im \langle f, g \rangle_{L^2}} = W(f+g)
        e^{-i \Im \langle f, g \rangle_{L^2}}.
      \]
    \item \label{l:W2} The operator $W(f)$ is unitary on $\mathcal{F}$ and
      \[
        W(f)^* = W(f)^{-1} = W(-f).
      \]
    \item \label{l:W3} We have
      \[
        W(f)^* a_x W(f) = a_x + f(x) \qquad \text{and} \qquad W(f)^* a_x^*
        W(f) = a_x^* + \overline{f(x)}.
      \]
    \item \label{l:W4} Coherent states are
      eigenvectors of annihilation operators:
      \[
        a_x W(f)\Omega = f(x) W(f)\Omega \qquad \text{and} \qquad a(g) W(f)\Omega
        = \langle g, f \rangle_{L^2} W(f)\Omega.
      \]
\iffalse    \item \label{l:W5} The expectation of the number of particles in the
      coherent state $\psi(f)$ is given by $\| f \|_{L^2}^2$, that is,
      \[
        \langle \psi(f), \N^2 \psi(f) \rangle = \| f \|_{L^2}^2.
      \]
      Also the variance of the number of particles in $\psi(f)$ is given by
      $\| f \|_{L^2}$ (the distribution of $\N$ is poisson), that is,
      \[
        \langle \psi(f), \N^2 \psi(f) \rangle - \langle \psi(f), \N \psi(f)
        \rangle^2 = \| f \|_{L^2}^2.
      \]
    \item \label{l:W6} Coherent states are normalized but not orthogonal to
      each other. In fact,
      \[
        \langle \psi(f), \psi(g) \rangle = e^{-\frac{1}{2} (\| f \|_{L^2}^2 +
        \| g \|_{L^2}^2 - 2 \langle f, g \rangle_{L^2} )} \qquad \text{so
        that} \qquad |\langle \psi(f), \psi(g) \rangle| = e^{-\frac{1}{2} \| f
        - g \|_{L^2}^2}.
      \]\fi
  \end{enumerate}
\end{lem}


\section{Bogoliubov Transformation}
Let $f(x,y)$ be a function of two variables, $f\colon \Rbb^3\times\Rbb^3 \to \Cbb$. To simplify the notation we write
\be{no1}
  f_y(x) = f(x,y)
\ee
so that
\[
  a(f_y) = a(f(\,\cdot\,,y)) \qquad \text{and} \qquad a^*(f_y) =
  a^*(f(\,\cdot\,,y)).
\]
For notational convenience, it will be useful to slightly abuse notation and
write
\[
  a_y + a(f_y) = a(\delta_y + f_y).
\]

For $k \in L^2(\R^3 \times \R^3)$, define the operators $B(k)$ and $T(k)$ on
$\mathcal{F}$ as
\[
  B(k) = \frac{1}{2} \int dxdy \, (k(x,y) a_x^* a_y^* - \overline{k(x,y)} a_x
  a_y)
\]
\marginpar{I think this cf. 2 is out of place for two reasons.}
and (cf.\ \cite{GMM2010})
\[
  T(k) = e^{B(k)}.
\]


\begin{lem}[Bogoliubov transformation] \label{l:bt}
  Let $k \in L^2(\R^3 \times \R^3)$ with $\nabla_1 k \in L^2(\R^3 \times
  \R^3)$.
 
\marginpar{I would put the (i) and (ii) back to follow the editorial format
of Lemma \ref{l:W} (or remove both)}
  The operator $T(k)$ is unitary on $\mathcal{F}$ and
      \[
        T(k)^* = T(k)^{-1} = T(-k).
      \]
  The creation and annihilation operators transform as
      \be{no4}
        T(k)^* a_y T(k) = a(c_y) + a^*(s_y) \qquad \text{and} \qquad T(k)^*
        a_y^* T(k) = a^*(c_y) + a(s_y)
      \ee
\marginpar{Where is $p$ below? How about $c$? I would just write ``with''.
Below is stated that $p, r, s \in L^3$}
      with $p, s \in L^2(\Rbb^3\times\Rbb^3)$ given by
      \begin{alignat*}{2}
        c & = \delta + p, & \qquad p & = \sum_{n=1}^\infty \frac{1}{(2n)!}
        \big( k \overline{k} \big)^n, \\
        s & = k + r, & \qquad r & = \sum_{n=1}^\infty \frac{1}{(2n+1)!} \big(
        k \overline{k} \big)^n k,
      \end{alignat*}
      where $\delta$ is the Dirac delta, and the product of functions in the
      power series is the convolution of integral kernels, that is $fg(x,y) =
      \int dz \, f(x,z) g(z,y)$. Furthermore,
      \begin{alignat*}{2}
        \| p \|_{L^2} & \le e^{\| k \|_{L^2}}, \qquad & \| \nabla_1 p \|_{L^2}
        & \le 2^{-1} e^{1 + \| k \|_{L^2}} \| \nabla_1 k \overline{k}
        \|_{L^2}, \\
        \| r \|_{L^2} & \le e^{1 + \| k \|_{L^2}}, \qquad & \| \nabla_1 r
        \|_{L^2} & \le e^{1 + \| k \|_{L^2}} \| \nabla_1 k \overline{k}
        \|_{L^2}, \\
        \| s \|_{L^2} & \le e^{\| k \|_{L^2}}, \qquad & \| \nabla_1 s \|_{L^2}
        & \le 2 e^{1+\| k \|_{L^2}} \| \nabla_1 k \|_{L^2}.
      \end{alignat*}
\end{lem}
\begin{rem}
Notice that the integral kernels $c$ and $s$ are defined by series similar to those of the hyperbolic cosine respectively the hyperbolic sine. 
\end{rem}


Let $f$ be the solution of the zero-energy scattering equation
\[
  \left( -\Delta + \frac{1}{2} V \right) f = 0
\]
with normalization $\lim_{|x|\to\infty} f(x) = 1$. We will write
\[
  f = 1 - w
\]
with $\lim_{|x|\to\infty} w(x) = 0$. The scattering length $a_0$ of $V$ is
defined as
\[
  a_0 = \lim_{|x| \to \infty} w(x)|x|.
\]
Since $V$ has compact support, we have
\[
  f(x) = 1 - \frac{a_0}{|x|} \qquad \text{for } |x| \ge R,
\]
where $R$ is such that $\text{supp} \ V \subset \{ x \in \R^3: |x|
\le R \}$. From the zero-energy scattering equation, we also have the identity
\[
  \int dx \, V(x) f(x) = 8 \pi a_0.
\]
By scaling, the scattering length of the potential $V_N(x) = N^2 V(Nx)$ is
$a_N = a_0/N$, and the zero-energy scattering equation for the potential $V_N$
is
\begin{equation} \label{eq:scattering}
  \left( -\Delta + \frac{1}{2} V_N \right) f_N = 0,
\end{equation}
where $f_N = 1 - w_N$ with $w_N(x) = w(Nx)$.
% Note that $w_N(x) = a_N/|x|$ for $|x| \ge R/N$.


\begin{lem}[Zero-energy scattering equation \cite{ESY2010}] \label{l:w}
  Let $V \in C_c^\infty(\R^3)$ with $V \ge 0$, and suppose that $V$ is
  spherically symmetric with scattering length $a_0$. Let $f_N = 1 - w_N$ be the solution of the zero-energy scattering
  equation \eqref{eq:scattering} with scaled potential $V_N$. Then, the
  following hold with constants uniform in $N$.
  \begin{enumerate}
    \item \label{l:w1} There exists a constant $C_0 > 0$, which depends on the
      unscaled potential $V$, such that
      \[
        C_0 \le 1 - w_N(x) \le 1 \qquad \text{for all} \ x \in \R^3.
      \]
    \item \label{l:w2} Let $R$ be such that $\text{supp} \ V \subset \{ x \in
      \R^3 : |x| \le R \}$. Then,
      \[
        w_N(x) = \frac{a_0}{N|x|} \qquad \text{for all} \ x \in \R^3 \
        \text{with} \ |x| > R/N.
      \]
    \item \label{l:w3} It follows from \ref{l:w1} and \ref{l:w2} that
      \[
        |w_N(x)| \le \max\{a_0, R\} \frac{1}{N|x|} \qquad \text{for all} \ x
        \in \R^3.
      \]
    \item \label{l:w4} There exists a constant $C$, depending only on
      $V$, such that for all $x \in \R^3$:
      \[
        \lvert\nabla w_N(x)\rvert \le C N \qquad \mbox{and} \qquad |\nabla w_N(x)| \le \frac{C a_0}{N |x|^2}.% \qquad |\nabla w_N(x)| \le
       % \frac{C \rho}{|x|}, \qquad |\nabla^2 w_N(x)| \le \frac{C \rho}{N^2
       % |x|^2}.		%% Here equations which were mentioned in ESY were left away.
      \]
    \item \label{l:w5} It follows from \ref{l:w4} that
      \[
        |\nabla w_N(x)| \le \max\{ C_1, C a_0 \} \frac{2N}{N^2|x|^2 + 1}
        \qquad \text{for all} \ x \in \R^3.
      \]
  \end{enumerate}
\end{lem}



\begin{lem} \label{l:kernels}
  Let $\varphi \in H^1(\R^3)$ and let $f_N=1-w_N$ be the solution of the
  zero-energy scattering equation. Suppose that
  \[
    k(x,y) = - N w_N(x-y) \varphi(x) \varphi(y).
  \]
  Then, there exists a constant $C$, uniform in $N$, that depends only on the
  unscaled potential~$V$, such that: 
  \begin{enumerate}
    \item \label{k}
      \[
        \| k \|_{L^2} \le C \| \varphi \|_{H^1}^2, \qquad \| \nabla_1 k
        \|_{L^2} \le C \| \varphi \|_{H^1}^2 \sqrt{N}, \qquad \| \nabla_1 k
        \overline{k} \|_{L^2} \le C \| \varphi \|_{H^1}^4.
      \]
    \item \label{kr} For almost all $x,y \in \R^3$,
      \[
        |k(x,y)| \leq N |\varphi(x)| |\varphi(y)|, \qquad |r(x,y)| \le e^{C \|
        \varphi \|_{H^1}^2} |\varphi(x)| |\varphi(y)|.
      \] 
    \item \label{sup} Let $p$ and $s$ be the integral kernels defined in Lemma
      \ref{l:bt}, and suppose further that $\varphi \in H^2(\R^3)$. Then,
      \[
        \sup_{x \in \R^3} \, \norm{p_x}_{L^2} \apprle e^{C \| \varphi
        \|_{H^1}^2} \norm{\varphi}_{H^2}, \qquad \sup_{x \in \R^3}
        \norm{s_x}_{L^2} \apprle e^{C \| \varphi \|_{H^1}^2}
        \norm{\varphi}_{H^2}.
      \]
  \end{enumerate}
\end{lem}


\begin{prp} \label{p:wphi}
  Let $\varphi \in H^1(\R^3)$, and let $f_N=1-w_N$ be the solution of the
  zero-energy scattering equation. Then, for almost all
  $x,y \in \R^3$,
  \begin{align*}
    \norm{N w_N(x-\cdot)\varphi(\cdot)}_{L^2}^2 & = \int dz \, N^2 w_N(x-z)^2 |\varphi(z)|^2 \le C \| \nabla \varphi
    \|_{L^2}^2, \\
    \norm{N w_N(x-\cdot)w_N(\cdot - y)\varphi(\cdot)}_{L^2}^2 & = \int dz \, N^2 w_N(x-z) w_N(z-y) |\varphi(z)|^2 \le C \| \nabla \varphi
    \|_{L^2}^2, \\
    & \quad  \int dx dy \, N^2 |\nabla w_N(x-y)|^2 |\varphi(x)|^2 |\varphi(y)|^2 \le
    C N \| \varphi \|_{H^1}^2,
  \end{align*}
\marginpar{There is clearly a notation issue here.}
  where $C$ is a constant, uniform in $N$, that depends only on the unscaled
  potential $V$.
\end{prp}


\begin{proof}[Proof of Proposition \ref{p:wphi}]
  Using Lemma \ref{l:w}\ref{l:w3} and Hardy's inequality, we find that
  \bd
    \int dz \, N^2 w_N(x-z)^2 |\varphi(z)|^2  \le C_1^2 \int dz \,
    |x-z|^{-2} |\varphi(z)|^2 \leq 4 C_1^2 \| \nabla \varphi \|_{L^2}^2,
  \ed
  where $C_1 = \max\{a_0, R\}$ is a constant from Lemma \ref{l:w}. This proves
  the first estimate.


  Now, by H\"older's inequality and the above estimate,
  \begin{align*}
    & \int dz \, N^2 w_N(x-z) w_N(z-y) |\varphi(z)|^2 \\
    & \le \left( \int dz \, N^2 w_N(x-z)^2 |\varphi(z)|^2 \right)^{1/2} \left(
    \int dz \, N^2 w_N(z-y)^2 |\varphi(z)|^2 \right)^{1/2} \le 4C_1^2 \|
    \nabla \varphi \|_{L^2}^2.
  \end{align*}
  This proves the second estimate.


  Finally, by Young's inequality, Sobolev's inequality, and Lemma
  \ref{l:w}\ref{l:w5},
  \begin{align*}
    \int dx dy \, N^2 |\nabla w_N(x-y)|^2 |\varphi(x)|^2 |\varphi(y)|^2 & \le
    N^2 \| | \nabla w_N|^2 \|_{L^1} \| \varphi \|_{L^4}^4 \\
    & \apprle C_2 N \| \varphi \|_{H^1}^4 \int dx \, \frac{N^3}{(|Nx|^2 +
    1)^2} \apprle C_2 N \| \varphi \|_{H^1}^4,
  \end{align*}
  where $C_2$ is a constant from Lemma \ref{l:w}, that depends only on $V$ and
  $a_0$. This proves the third estimate and concludes the proof of the
  proposition.
\end{proof}

\begin{proof}[Proof of Lemma \ref{l:bt}]
% Funny behavior here. Forcing hyphenation...
\marginpar{We might omit this first part? Isn't standard? We might well
start just at the top of the next page.}
  The operator $B(k)$ is unbounded, densely defined and anti-self-ad\-joint.
  Hence, by the spectral theorem, the unitary operator $T(k) = e^{B(k)}$ is
  well-defined and $T(k)^* = T(k)^{-1} = T(-k)$.


  Let $\chi$ be the characteristic function, and consider a real number $M >
  0$. We give a proof of the formulae on the subspace $\chi(\N \le M)
  \mathcal{F}$, and then we indicate how to extend it to the whole
  $\mathcal{F}$. First, note that $B(k)$ and $a(f)$ are bounded operators on
  $\chi(\N \le M) \mathcal{F}$. Recall the formula
  \[
    e^X Y e^{-X} = Y + [X,Y] + \frac{1}{2!} [X,[X,Y]] + \cdots
  \]
  Then, observing that $[a_w a_z, a_y] = [a_w^* a_z^*, a_y^*] = 0$ and
  \[
    [a_w a_z, a_y^*] = \delta(w-y) a_z + \delta(z-y) a_w \qquad \text{and}
    \qquad [a_w^* a_z^*, a_y] = -\delta(y-w) a_z^* - \delta(y-z) a_w^*,
  \]
  one easily finds the expression
  \begin{align*}
    T(k)^* a_y T(k) & = e^{-B(k)} a_y e^{B(k)} = a_y - [B(k), a_y] +
    \frac{1}{2!} [B(k), [B(k), a_y]] + \cdots \\
    & = a_y + \int dx \, \sum_{n=1}^\infty \frac{1}{(2n)!} \big( 
    \overline{k} k \big)^n(x,y) a_x + \int dx \, \sum_{n=0}^\infty
    \frac{1}{(2n+1)!} \big( k \overline{k} \big)^n k(x,y) a_x^* \\
    & = a_y + \int dx \, \overline{p(x,y)} a_x + \int dx \, s(x,y) a_x^* \\
    & = a_y + a(p_y) + a(s_y) = a(c_y) + a(s_y).
  \end{align*}
  We next prove the estimates for the integral kernels $p$, $r$ and $s$. 


  Let $fg$ be the convolution of integral kernels $f, g \in L^2(\Rbb^3\times\Rbb^3)$. Then, by H\"older's inequality,
  \[
    \| f g \|_{L^2} \le \| f \|_{L^2} \| g \|_{L^2}.
  \]
  Hence, applying this to the series for $p$, we get
  \[
    \| p \|_{L^2} \le \sum_{n=1}^\infty \frac{1}{(2n)!} \| k \|_{L^2}^{2n} \le
    e^{\| k \|_{L^2}},
  \]
  and similarly $\| r \|_{L^2} \le e^{\| k \|_{L^2}}$ and $\| s \|_{L^2} \le
  e^{\| k \|_{L^2}}$. Furthermore, since the series for $p$, $r$ and $s$ are
  absolutely convergent, we can write
  \begin{align*}
    \nabla_1 p & = \frac{1}{2} \nabla_1 k \overline{k} + \nabla_1 k
    \overline{k} \sum_{n=2}^\infty \frac{1}{(2n)!} (k \overline{k})^{n-1}, \\
    \nabla_1 r & = \nabla_1 k \overline{k} \sum_{n=1}^\infty \frac{1}{(2n+1)!}
    k ( \overline{k} k)^{n-1}, \\
    \nabla_1 s & = \nabla_1 k + \nabla_1 k \sum_{n=1}^\infty \frac{1}{(2n+1)!}
    (\overline{k} k)^n.
  \end{align*}
  Thus, similarly as above,
  \begin{align*}
    \| \nabla_1 p \|_{L^2} & \le 2^{-1} e^{1+\| k \|_{L^2}} \| \nabla_1 k
    \overline{k} \|_{L^2}, \\
    \| \nabla_1 r \|_{L^2} & \le e^{1+\| k \|_{L^2}} \| \nabla_1 k
    \overline{k} \|_{L^2}, \\
    \| \nabla_1 s \|_{L^2} & \le 2 e^{1+ \| k \|_{L^2}} \| \nabla_1 k
    \|_{L^2}.
  \end{align*}
This completes the proof of the lemma.
\end{proof}


\begin{proof}[Proof of Lemma \ref{l:kernels}]
  \ref{k} We will repeatedly apply Proposition \ref{p:wphi}, Sobolev's
  inequality, Leibniz' rule, and the triangle inequality. We begin with
  \[
    \| k \|_{L^2}^2 = \int dx \, |\varphi(x)|^2 \int dy \, N^2 w_N(x-y)^2
    |\varphi(y)|^2 \le C \| \varphi \|_{L^2}^2 \| \nabla \varphi \|_{L^2}^2
    \apprle C \| \varphi \|_{H^1}^4
  \]
  and
  \begin{align*}
    \| \nabla_1 k \|_{L^2} & \le \| N w_N(x-y) \nabla \varphi(x) \varphi(y)
    \|_{L^2} + \| N \nabla w_N(x-y) \varphi(x) \varphi(y) \|_{L^2} \\
    & \le C \| \nabla \varphi \|_{L^2}^2 + C \sqrt{N} \| \varphi \|_{H^1}^2
    \apprle C \sqrt{N} \| \varphi \|_{H^1}^2.
  \end{align*}
  This proves the first two estimates in \ref{k}. Now,
  \[
    \| \nabla_1 k \overline{k} \|_{L^2} \le \| I \|_{L^2} + \| J \|_{L^2}
  \]
  with, by Proposition \ref{p:wphi},
  \[
    \| I \|_{L^2}^2 = \int dx \, |\nabla \varphi(x)|^2 \int dy \,
    |\varphi(y)|^2 \left| \int dz \, N^2 w_N(x-z) w_N(z-y) |\varphi(z)|^2
    \right|^2 \apprle C^2 \| \varphi \|_{H^1}^8
  \]
  and, using Hardy's inequality,
  \begin{align*}
    \| J \|_{L^2}^2 & = \int dx \, |\varphi(x)|^2 \int dy \, |\varphi(y)|^2
    \left| \int dz \, N^2 \nabla w_N(x-z) w_N(z-y) |\varphi(z)|^2 \right|^2 \\
& \apprle \int \di x\di y \lvert\varphi(x)\rvert^2 \lvert \varphi(y)\rvert^2 \left\lvert \int \di z \frac{\lvert\varphi(z)\rvert^2}{\lvert x-z\rvert^2 \lvert z-y\rvert} \right\rvert^2 \\
& \apprle \int \di x\di z_1 \di z_2 \lvert \varphi(x)\rvert^2 \frac{\lvert \varphi(z_1)\rvert^2}{\lvert x-z_1\rvert^2} \frac{\lvert\varphi(z_2)\rvert^2}{\lvert x-z_2\rvert^2} \int \di y \frac{\lvert \varphi(y)\rvert^2}{\lvert z_1-y\rvert \lvert z_2 - y\rvert} \\
& \apprle \int \di x \lvert \varphi(x)\rvert^2 \int \di z_1 \frac{\lvert \varphi(z_1)\rvert^2}{\lvert x-z_1\rvert^2} \int \di z_2 \frac{\lvert \varphi(z_2)\rvert^2}{\lvert x-z_2\rvert^2} \norm{\nabla \varphi}_{L^2}^2\\
& \apprle C \norm{\varphi}_{H^1}^8.
  \end{align*}
  Therefore,
  \[
    \| \nabla_1 k \overline{k} \|_{L^2} \le \| I \|_{L^2} + \| J \|_{L^2}
    \apprle C \| \varphi \|_{H^1}^4.
  \]
  This completes the proof of part \ref{k}.


  \ref{kr} By Lemma \ref{l:w}\ref{l:w1} $w_N \leq 1$. Hence
  \[
    |k(x,y)| = N w_N(x-y) |\varphi(x)| |\varphi(y)| \leq N |\varphi(x)|
    |\varphi(y)|.
  \]
  This proves the first estimate in \ref{kr}.
  
  
  To bound $|r(x,y)|$, observe that, by H\"older's inequality, Proposition
  \ref{p:wphi} and part \ref{k},
  \begin{align*}
    & |( k \overline{k})^n k(x,y)| = | k \overline{k} ( k \overline{k})^{n-1}
    k(x,y)| \\
    & = |\varphi(x)| |\varphi(y)| \, \left| \int dz_1 dz_2 \, N^2 w_N(x-z_1)
    w_N(z_2-y) \varphi(z_1) \varphi(z_2) \overline{k}(k
    \overline{k})^{n-1}(z_1,z_2) \right| \\
    & \le |\varphi(x)| |\varphi(y)| \, \| \overline{k} (k \overline{k})^{n-1}
    \|_{L^2} \\
    & \quad \times \left( \int dz_1 N^2 w_N(x-z_1)^2 |\varphi(z_1)|^2 \int
    dz_2 \, N^2 w_N(z_2-y) |\varphi(z_2)|^2 \right)^{1/2} \\
    & \le |\varphi(x)| |\varphi(y)| C \| \nabla \varphi \|_{L^2}^2 \| k
    \|_{L^2}^{2n-1} \le |\varphi(x)| |\varphi(y)| C^{2n} \| \varphi
    \|_{H^1}^{4n}.
  \end{align*}
  Thus,
  \[
    |r(x,y)| \le \sum_{n=1}^\infty \frac{1}{(2n+1)!} |( k \overline{k})^n k
    (x,y)|\le |\varphi(x)| |\varphi(y)| e^{C \| \varphi \|_{H^1}^2}.
  \]
  This completes the proof of part \ref{kr}.


  \ref{sup} We give a proof of the estimate for $\sup_{y \in \R^3} \| s_y
  \|_{L^2}$. The proof for $\sup_{y \in \R^3} \| p_y \|_{L^2}$ is similar.
  First, by H\"older's inequality and Proposition \ref{p:wphi},
  \begin{align*}
    |(k \overline{k})^n k(x,y)| & = \left| \varphi(y) \int dz \, N w_N(z-y)
    \varphi(z) (k \overline{k})^n(x,z) \right| \\
    & \le |\varphi(y)| \left( \int dz \, N^2 w_N(z-y)^2 |\varphi(z)|^2
    \right)^{1/2} \| (k \overline{k})^n(x,\, \cdot\,) \|_{L^2} \\
    & \le C \| \nabla \varphi \|_{L^2} | \varphi(y)| \, \| (k \overline{k}
    )^n(x,\, \cdot\,) \|_{L^2}.
  \end{align*}
  Hence, using part \ref{k},
  \[
    \| s_y \|_{L^2} \le \sum_{n=0}^\infty \frac{\| (k \overline{k})^n k(\,
    \cdot\,,y) \|_{L^2}}{(2n+1)!} \le |\varphi(y)| \sum_{n=0}^\infty
    \frac{C^{2n+1} \| \varphi \|_{H^1}^{2n+1}}{(2n+1)!} \le e^{C \|
    \varphi\|_{H^1}^2} |\varphi(y)|.
  \]
  Therefore, by Sobolev's inequality,
  \[
    \sup_{y \in \R^3} \| s_y \|_{L^2} \le e^{C \| \varphi \|_{H^1}^2} \sup_{y
    \in \R^3} |\varphi(y)| \apprle e^{C \| \varphi \|_{H^1}^2} \| \varphi
    \|_{H^2}.
  \]
  This proves part \ref{sup} and completes the proof of the lemma.
\end{proof}


\section{Dynamics of Quantum Fluctuations}
We use the short-hand $T_t = T(k)$ with
\bd
k(x,y) = - N w_N(x-y) \ph(x) \ph(y),
\ed
where $\ph$ is a solution of the modified Hartree equation. We also write $W_t = W(\sqrt{N}\ph)$.
We define the time evolution of quantum fluctuations by
\bd
U_N(t) := T^\ast_t W^\ast_t e^{-it \Hcal_N} W_0 T_0.
\ed
To simplify the notation we sometimes write $U_t := U_N(t)$ as a short-hand.

\subsection{The Generator of Quantum Fluctuations}
The generator $\Lcal_N(t)$ of quantum fluctuations is defined by
\bd
\Lcal_N(t) U_N(t) = i \partial_t U_N(t).
\ed
We calculate that
\begin{align*}
\Lcal_N(t) 	& = (i \partial_t T^*_t) T_t + T^*_t \left( (i \partial_t W^*_t) W_t + W^*_t \Hcal_N W_t \right) T_t \\
		& = (i \partial_t T^*_t) T_t + T^*_t \Lcal^{(0)}_N(t) T_t
\end{align*}
where
\marginpar{What if we raise this to a prop.: ``$L_N^{(0)}$ does not contain
linear terms is $a_x$, and is given by\dots''}
\be{no3}
\begin{split}
\Lcal^{(0)}_N(t) & = \Kcal + \Vcal_N \\
		& \quad + N^{1/2} \left[  a^*\left( (w_N N V_N \ast \lvert \ph \rvert^2)\ph \right] + \hc  \right) \\
		& \quad + N^0	    \left[  \frac{1}{2}\int \di x \di y\, NV_N(x-y)\left( \cc{\ph(x)} \cc{\ph(y)} a_y a_x + \hc \right) \right] \\
		& \quad + N^0	    \left[  \int \di x \di y\, NV_N(x-y)\left( \lvert \ph(x) \rvert^2 a^*_y a_y + \cc{\ph(x)} \ph(y) a^*_y a_x \right) \right] \\
		& \quad + N^{-1/2}\left[  \int \di x \di y\, NV_N(x-y) \left( \cc{\ph(x)} a^*_y a_y a_x + \hc \right)  \right] \\
		& \quad + N b(N,t),
\end{split}
\ee
with a phase $b(N,t) \in \Rbb$ which, like all phases appearing in $\Lcal_N(t)$, will be dropped from now on without any further comment. (Notice that $\scal{U_N(t)T^\ast_0 \Psi}{(\Ncal+1)U_t T_0^\ast \Psi} = \scal{\tilde U_N(t)T^\ast_0 \Psi}{(\Ncal+1)\tilde U_t T_0^\ast \Psi}$ for all $\tilde U_N(t) = e^{i\theta_N(t)} U_N(t)$ with $\theta_N(t) \in \Rbb$.)

In \eqr{no3} we have made use of a cancellation in the term $\Ocal({N^{1/2}})$ (term which is linear in creation/annihilation operators) due to $\ph$ satisfying the modified Hartree equation \eqr{modHartreeEqu}.
%\bd
%i\partial_t \ph = -\Delta \ph + \left(f_N N V_N \ast \lvert \ph \rvert^2 \right) \ph.
%\ed
Compare to \cite{RS2009}, but notice that due to the factor $f_N$ in the modified Hartree equation, in our case the cancellation is incomplete. This is essential for ensuring the correct coupling constant $8\pi a_0$ instead of $b_0$ in the Gross-Pitaevskii equation and ensures important cancellations (see below). These cancellations are revealed through the Bogoliubov transformation, to be calculated now.

We first identify cancellations between linear terms originating from the transformation \eqr{no4} of linear terms and linear terms originating from normal-ordering the transformation of cubic terms
\begin{align*}
T^*_t \Lcal^{(0)}_N(t) T_t \\
= \int \di x\, T^*_t a^*_x T_t \bigg[ &   \frac{1}{2}(-\Delta_x T^*_t a_x T_t) \\
& + \frac{1}{4}\int \di y V_N(x-y) T^*_t a^*_y a_y a_x T_t \\
& + N^{1/2} \ph(x) \int \di y\, w_N N V_N(x-y) \lvert \ph(y) \rvert^2 \tagg{linearterm} \\
& + \frac{1}{2} \int \di y\, NV_N(x-y)  \ph(x) \ph(y)  T^*_t a^*_y T_t \\
& + \frac{1}{2} \int \di y\, NV_N(x-y) \left(  \lvert \ph(y)\rvert^2 T^*_t a_x T_t + \ph(x) \cc{\ph(y)} T^*_t a_y T_t  \right) \\
& + N^{-1/2} \int \di y\, NV_N(x-y) \cc{\ph(y)} T^*_t a_x a_y T_t  \bigg]\tagg{cubicterm} \\
& + \hc
\end{align*}
Between the terms \eqr{linearterm} and \eqr{cubicterm}, after normal ordering and plugging in $c = \delta + p$ and $s = k + r$, we find that the linear term is cancelled up to two remainder terms (the $N^{1/2}$-term, line \eqr{linearterm}, is completely cancelled). The result is:
\begin{align*}
& T^*_t \Lcal^{(0)}_N(t) T_t = \int \di x\, T^*_t a^*_x T_t \bigg[   \frac{1}{2}(-\Delta_x T^*_t a_x T_t) \\
& + \frac{1}{4}\int \di y V_N(x-y) T^*_t a^*_y a_y a_x T_t \\
& + \frac{1}{2} \int \di y\, NV_N(x-y)  \ph(x) \ph(y)  T^*_t a^*_y T_t \\
& + \frac{1}{2} \int \di y\, NV_N(x-y) \left(  \lvert \ph(y)\rvert^2 T^*_t a_x T_t + \ph(x) \cc{\ph(y)} T^*_t a_y T_t  \right) \\
& + N^{-1/2} \int \di y\, NV_N(x-y) \cc{\ph(y)} \bigg( r(x,y) + \scal{p_x}{s_y} + \\
& \qquad \qquad  a^*(s_x) a^*(s_y) + a^*(s_x) a(c_y)  + a^*(s_y) a(c_x) + a(c_x) a(c_y)  \bigg)  \bigg] \\
& + \hc
\end{align*}
Now we apply the Bogoliubov transform \eqr{no4} everywhere, multiply out all the terms and normal order all terms. To simplify the expression a bit, notice that many terms appear twice, e.\,g.\ in the hermitian conjugate or with $x$ and $y$ interchanged:
\begin{align*}
& T^*_t \Lcal_N^{(0)}(t) T_t = \\ 
& \frac{1}{2} \int \di x\, \left[ a^*(c_x) a(-\Delta_x c_x) + \boxed{2 a^*(c_x) a^*(-\Delta_x s_x)} + a^*(-\Delta_x s_x) a(s_x) \right] \tagg{cancellation_kinetic} \\
& + \frac{1}{2}\int \di x \di y\, NV_N(x-y) \times \\
& \times \Big[   \frac{1}{2N}\bigg( a^*(c_x) a^*(c_y) a(c_y) a(c_x) + 4 a^*(c_x) a^*(c_y) a^*(s_x) a(c_y) \\
				      & \qquad\qquad + 2 a^*(c_x) a^*(c_y) a^*(s_y) a^*(s_x) + 2 a^*(c_x) a^*(s_x) a(s_y) a(c_y) \\
				      & \qquad\qquad + 2 a^*(c_x) a^*(s_y) a(s_y) a(c_x) + 4 a^*(c_x) a^*(s_y) a^*(s_x) a(s_y) \\
				      & \qquad\qquad + a^*(s_y) a^*(s_x) a(s_x) a(s_y) \bigg) \\
& + \frac{1}{N}\bigg(   \boxed{a^*(c_x)a^*(c_y) \scal{c_y}{s_x}} + a^*(c_x) a(c_y) \scal{s_y}{s_x} \tagg{cancellation_normalorder} \\
			& \qquad\quad + a^*(c_x) a(s_y) \scal{c_y}{s_x} + a^*(c_x) a(c_x) \scal{s_y}{s_y} \\
			& \qquad\quad + 2 a^*(c_x) a^*(s_x) \scal{s_y}{s_y} + 2a^*(c_x)a^*(s_y) \scal{s_y}{s_x} \\
			& \qquad\quad + a^*(c_y) a(s_x) \scal{c_y}{s_x} +  a^*(s_y) a(s_y) \scal{s_x}{s_x}\\
			& \qquad\quad + a^*(s_y) a^*(s_x) \scal{s_x}{c_y} + a^*(s_y) a(s_x) \scal{s_y}{s_x}   \bigg) \\
& + \ph(x)\ph(y) \Big( \boxed{a^*(c_x) a^*(c_y)} + 2 a^*(c_x) a(s_y) +a(s_x) a(s_y) \Big) \tagg{cancellation_standard} \\
& + \ph(x) \cc{\ph(y)} \Big( a^*(c_x) a(c_y) + 2 a^*(c_x) a^*(s_y) + a^*(s_y) a(s_x) \Big) \\
& + \lvert \ph(y) \rvert^2 \Big( a^*(c_x) a(c_x) + 2 a^*(c_x) a^*(s_x) + a^*(s_x) a(s_x) \Big) \\
& + \frac{2}{\sqrt{N}}\cc{\ph(y)} \bigg(    a^*(c_x) a^*(s_x) a^*(s_y) + a^*(c_x) a^*(s_x) a(c_y) + a^*(s_x) a^*(s_y) a(s_x)\\
					    & \qquad\qquad\qquad\quad + a^*(c_x) a^*(s_y) a(c_x) + a^*(c_x) a(c_x) a(c_y)+ a^*(s_x) a(s_x) a(c_y) \\
					    & \qquad\qquad\qquad\quad + a^*(s_y) a(s_x) a(c_x) + a(s_x) a(c_x) a(c_y)    \bigg) \\
& + \frac{2}{\sqrt{N}}\cc{\ph(y)} \bigg(    a^*(s_x) \scal{s_x}{s_y} + a^*(s_y) \scal{s_x}{s_x}  + a(c_y) \scal{s_x}{s_x} + a(c_x) \scal{s_x}{s_y} \\
					    & \qquad\qquad\qquad\quad + a^*(c_x)r(x,y) + a^*(c_x)\scal{p_x}{s_y} + a(s_x)r(x,y) + a(s_x)\scal{p_x}{s_y}		\bigg)    \Big] + \hc
\end{align*}
We now proceed to identify a cancellation between the second summand in line \eqr{cancellation_kinetic}, the first summand in line \eqr{cancellation_normalorder} and the first summand in line \eqr{cancellation_standard}. To see the cancellation, we expand $c = \delta + p$ and $s = k + r$ and use the product rule for the Laplacian $-\Delta_x k(y,x)$, then notice that the lhs of the zero-energy scattering equation \eqr{scattering} appears. There are however some, more regular, remainder terms left, see \eqref{l7}, \eqref{l8}, \eqref{l14} and \eqref{l18} in the final result for the generator.

Our final result for the generator is:
\begin{align}
& T^*_t \Lcal_N^{(0)}(t) T_t = \nonumber \\ 
& \frac{1}{2} \int \di x\, \bigg[ a^*(c_x) \int \di y\, a^*_y \Big( N \nabla w_N(x-y) \nabla_x \ph(x) 2 \ph(y) \label{l7}\\
& \qquad\qquad \qquad\qquad \qquad	+ Nw_N(x-y) \Delta_x \ph(x) \ph(y) - \Delta_x r(y,x) \Big) \label{l8}\\
& \qquad\qquad 			+ a^*(c_x) a(-\Delta_x c_x) + a^*(-\Delta_x s_x) a(s_x) \bigg] \label{l9} \\
& + \frac{1}{2}\int \di x \di y\, NV_N(x-y) \times \nonumber \\
& \times \Big[   \frac{1}{2N}\bigg( a^*(c_x) a^*(c_y) a(c_y) a(c_x) + 4 a^*(c_x) a^*(c_y) a^*(s_x) a(c_y) \label{l10}\\
				      & \qquad\qquad + 2 a^*(c_x) a^*(c_y) a^*(s_y) a^*(s_x) + 2 a^*(c_x) a^*(s_x) a(s_y) a(c_y) \label{l11}\\
				      & \qquad\qquad + 2 a^*(c_x) a^*(s_y) a(s_y) a(c_x) + 4 a^*(c_x) a^*(s_y) a^*(s_x) a(s_y) \label{l12}\\
				      & \qquad\qquad + a^*(s_y) a^*(s_x) a(s_x) a(s_y) \bigg) \label{l13}\\
& + \frac{1}{N}\bigg(   a^*(c_x) a^*(c_y) \Big( r(y,x) + \scal{p_y}{s_x} \Big) + a^*(c_x) a^*(p_y) k(y,x) \label{l14} \\
      & \qquad\quad + a^*(c_x) a(c_y) \scal{s_y}{s_x} + a^*(s_y) a(s_y) \scal{s_x}{s_x} + a^*(s_y) a(s_x) \scal{s_y}{s_x} \label{l15}\\
      & \qquad\quad + a^*(c_x) a(s_y) \scal{c_y}{s_x} + a^*(c_x) a(c_x) \scal{s_y}{s_y} + a^*(s_y) a^*(s_x) \scal{s_x}{c_y} \label{l16}\\
      & \qquad\quad + 2a^*(c_x) a^*(s_x) \scal{s_y}{s_y} + 2a^*(c_x)a^*(s_y) \scal{s_y}{s_x} + a^*(c_y) a(s_x) \scal{c_y}{s_x}    \bigg) \label{l17}\\
& + \ph(x)\ph(y) \Big( a^*(c_x) a^*(p_y) + 2 a^*(c_x) a(s_y) +a(s_x) a(s_y) \Big) \label{l18}\\
& + \ph(x) \cc{\ph(y)} \Big( a^*(c_x) a(c_y) + 2 a^*(c_x) a^*(s_y) + a^*(s_y) a(s_x) \Big) \label{l19}\\
& + \lvert \ph(y) \rvert^2 \Big( a^*(c_x) a(c_x) + 2 a^*(c_x) a^*(s_x) + a^*(s_x) a(s_x) \Big) \label{l20}\\
& + \frac{2}{\sqrt{N}}\cc{\ph(y)} \bigg(    a^*(c_x) a^*(s_x) a^*(s_y) + a^*(c_x) a^*(s_x) a(c_y) \label{l21}\\
					    & \qquad\qquad\qquad + a^*(c_x) a^*(s_y) a(c_x) + a^*(c_x) a(c_x) a(c_y) + a^*(s_y) a(s_x) a(c_x) \label{l22}\\
					    & \qquad\qquad\qquad + a^*(s_x) a^*(s_y) a(s_x) + a^*(s_x) a(s_x) a(c_y) + a(s_x) a(c_x) a(c_y)  \bigg) \label{l23}\\
& + \frac{2}{\sqrt{N}}\cc{\ph(y)} \bigg(    a^*(s_x) \scal{s_x}{s_y} + a^*(s_y) \scal{s_x}{s_x}  + a(c_y) \scal{s_x}{s_x} + 							a(c_x) \scal{s_x}{s_y} \label{l24}\\
					    & \qquad\qquad\qquad + a^*(c_x)r(x,y) + a^*(c_x)\scal{p_x}{s_y} + a(s_x)r(x,y) + 			a(s_x)\scal{p_x}{s_y}		\bigg)    \Big] \label{l25}\\
&+ \hc
\end{align}

\begin{rem}The cancellations enable us to give the necessary estimates for all terms of the generator, see appendix \ref{ch:generatorestimates}. If we had not identified the cancellation between the boxed terms, there would be contributions of order $N^1$.
\end{rem}


\subsection{Estimating the number of fluctuations}
The estimates in this section hold for the expectation value $\ev{\cdot} = \scal{\psi}{\cdot\psi}$ in any state $\psi \in \fock$. Especially, $C$ stands for constants independent of $N$, $t$ and $\psi$.

We define
\bd
\tilV := \frac{1}{4} \int \di x\di y\, V_N(x-y) a^\ast(c_x) a^\ast(c_y)a(c_y)a(c_x).
\ed
(Notive that through the $t$-dependence of $c$, the operator $\tilV$ is time-dependent. However, as this does not play any role in our proof, we do not indicate this time-dependence and $\tilV$ should always be read as belonging to the same time $t$ like the other objects in the equation where it appears.)

\begin{lem}
\label{lem:kvbounds}
There exists a constant $C$ such that
\bd
\ev{\Kcal} + \ev{\tilV} \leq 2 \ev{\Lcal_N(t)} + C \norm{\ph}_{H^2}^4 \ev{\frac{1}{N}\Ncal^2 + \Ncal + 1}.
\ed
As $\Kcal$ and $\tilV$ are non-negative operators, the same upper bound holds for each of $\Kcal$ and $\tilV$ individually.
\end{lem}
\begin{proof}
We know that $\Lcal_N(t) = (i\partial_t T^\ast_t)T_t + T^\ast_t \Lcal_N^{(0)}(t)T_t$ with $T^\ast_t \Lcal_N^{(0)}(t)T_t$ written out in \eqref{l7} through \eqref{l25}. We now write only line \eqref{l9} and the first summand in line \eqref{l10} explicitly, all the other terms we collect in $\Lcal_{\textrm{rest}}$:
\begin{align*}
\Lcal_N(t) & = \frac{1}{2} \int \di x\, a^\ast(c_x) a(-\Delta_x c_x) + \frac{1}{2}\int \di x\, a^\ast(-\Delta_x s_x)a(s_x) \\
& \quad + \frac{1}{2}\int \di x\di y\, NV_N(x-y) \frac{1}{2N} a^\ast(c_x) a^\ast(c_y) a(c_y) a(c_x) + \Lcal_{\textrm{rest}}.
\end{align*}
We define $\tilK := \frac{1}{2} \int \di x\, a^\ast(c_x) a(-\Delta_x c_x)$ and observe that
\bd
\ev{\frac{1}{2}\int \di x\, a^\ast(-\Delta_x s_x)a(s_x)} = \frac{1}{2}\int \di x\, \norm{a(\nabla_x s_x)\psi}^2 \geq 0,
\ed
so by leaving away this non-negative term we obtain
\be{Lcalbound}
\ev{\Lcal_N(t)} \geq \ev{\tilK + \tilV} - \lvert\ev{\Lcal_{\textrm{rest}}}\rvert.
\ee
We now collect the estimates for lines \eqref{l7}, \eqref{l8} and \eqref{l10} through \eqref{l25} from appendix \ref{ch:generatorestimates} and use Lemma \ref{lm:timederivative} to obtain an upper bound for $\lvert\ev{\Lcal_{\textrm{rest}}}\rvert$, i.\,e.\ a lower bound for $-\lvert\ev{\Lcal_{\textrm{rest}}}\rvert$.
(To simplify the notation we insert factors of $\norm{\ph}_{H^2} \geq \norm{\ph}_{L^2} =1$ in some places, leave away prefactors $\frac{1}{N}$ and $\frac{1}{\sqrt{N}}$ where they are not needed to controll a $\Ncal^2$, and use that $1 \leq 1/\varepsilon$. Numerical prefactors are absorbed into $C$.)
\bd
\lvert\ev{\Lcal_{\textrm{rest}}}\rvert \leq C \norm{\ph}_{H^2}^2 \left( \frac{1}{\varepsilon}\ev{\frac{1}{N}\Ncal^2 + \Ncal + 1} + \varepsilon\ev{\Kcal+\tilV} \right).
\ed
So using \eqr{Lcalbound} we conclude that
\bd
\ev{\Lcal_N(t)} \geq \ev{\tilK+\tilV} - C\norm{\ph}_{H^2}^2 \left( \frac{1}{\varepsilon}\ev{\frac{1}{N}\Ncal^2 +\Ncal+1} + \varepsilon \ev{\Kcal+\tilV} \right).
\ed
Combining this with $\ev{\tilK} \geq \ev{\Kcal} - C\left(\varepsilon\ev{\Kcal} + \frac{1}{\varepsilon}\ev{\Ncal} \right)$ from \eqref{eq:bound1A}, we arrive at
\bd
\ev{\Lcal_N(t)} \geq  \ev{\Kcal+\tilV} - C\norm{\ph}_{H^2}^2 \left( \frac{1}{\varepsilon}\ev{\frac{1}{N}\Ncal^2 +\Ncal+1} + \varepsilon \ev{\Kcal+\tilV} \right).
\ed
Now choose $\varepsilon = 1/(2C\norm{\ph}_{H^2}^2)$ (with $C$ having the same value as in the previous equation) to conclude
\bd
\ev{\Lcal_N(t)} + 2\left( C \norm{\ph}_{H^2}^2 \right)^2 \ev{\frac{1}{N}\Ncal^2 + \Ncal + 1} \geq \frac{1}{2}\ev{\Kcal+\tilV},
\ed
thus the proof is finished.
\end{proof}

\begin{lem}
\label{lem:Llowerbound}
There exists a constant $C$ such that
\bd
\ev{\Lcal_N(t)} \geq -C \norm{\ph}_{H^2}^4 \ev{\frac{1}{N}\Ncal^2 + \Ncal + 1}.
\ed 
\end{lem}
\begin{proof}
As $\ev{\Kcal} \geq 0$ and $\ev{\tilV} \geq 0$, this lemma is an easy corollary of lemma \ref{lem:kvbounds}.
\end{proof}

\begin{lem}
\label{lem:ldotbounds} There exists a constant $C$ such that
 \bd
  \lvert \ev{\dot \Lcal_N(t)} \rvert \leq C \norm{\ph}_{H^4}^8 \ev{\frac{1}{N}\Ncal^2 + \Ncal + 1 + \Kcal + \tilV}.
 \ed
\end{lem}
\begin{proof}
Combining Lemma \ref{lm:timederivative} and Lemma \ref{lm:kbounds}, we obtain the estimate
\bd
\lvert\ev{\partial_t\left((\partial_t T^\ast_t) T_t \right)}\rvert \leq C \norm{\ph}_{H^4}^4 \ev{\Ncal+1}.
\ed
(We make no effort to optimize the appearance of $H^n$ norms, just take $n$ and the power as high as you like.)

The term $\ev{\partial_t( T^\ast_t \Lcal_N^{(0)}(t) T_t )}$ can be estimated by the same methods which where already used for estimating $\ev{ T^\ast_t \Lcal_N^{(0)}(t) T_t}$ in appendix \ref{ch:generatorestimates}, however, additionally the following objects are used:
$\norm{\gradone \dot p}$, $\norm{\gradone \dot r}$, $\norm{\dot s}$, $\norm{\dot p}$, $\sup_x \norm{\dot p_x}$, $\sup_x \norm{\dot s_x}$, $\int \di x\di y V_N(x-y) \lvert \dot r(x,y)\rvert^2$, $\int \di x \di y V_N(x-y) \lvert \dot s(x,y)\rvert^2/N$ and Sobolev norms of $\phdot$. These quantities are then estimated using the Lemmata \ref{lem:dottedests1}, \ref{lem:dottedests2} and \ref{lem:dottedests3}.

(Remark: In $\partial_t( T^\ast_t \Lcal_N^{(0)}(t) T_t)$ there are four times as many terms as in $T^\ast_t \Lcal_N^{(0)}(t) T_t$ because of the product rule, but many of them are easy to estimate because $\partial_t a^\ast(c_x) = a^\ast(\dot p_x)$ is regular while $a^\ast(c_x)$ is singular.)
\end{proof}


\begin{lem}
\label{lem:lncommutatorbound}
There exists a constant $C$ such that
 \bd
  \lvert \ev{[\Lcal_N(t),\Ncal]} \rvert \leq C \norm{\ph}_{H^2}^2 \ev{\frac{1}{N}\Ncal^2 + \Ncal + 1 + \Kcal + \tilV}.
 \ed
\end{lem}
\begin{proof}
We start by calculating $[T^\ast_t \Lcal_N^{(0)}(t)T_t,\Ncal]$. Summands which contain an equal number of annihilation and creation operators commute with $\Ncal$ and thus drop out. The other summands get numerical prefactors, but except for that stay unchanged. %(Because of these prefactors, the sign of the $+\hc$-part changes, but this is not important for our estimates.)
Therefor we can use the estimates from appendix \ref{ch:generatorestimates} (choose e.\,g.\ $\varepsilon = 1$) to bound all summands of the commutator $[T^\ast_t \Lcal_N^{(0)}(t)T_t,\Ncal]$.

The contribution $[(\partial_t T^\ast_t)T_t,\Ncal]$ is of the same form as $(\partial_t T^\ast_t)T_t$, the only difference being that the particle-number conserving summands of the series drop out. Thus, the term can be estimated in the same way as $(\partial_t T^\ast_t)T_t$ in Lemma \ref{lm:timederivative}.
\end{proof}


\begin{prp}[Bound on Number of Fluctuations]
\label{prp:Nbound}
Let $\Psi \in \fock$ with $\scal{\Psi}{\left(\frac{1}{N}\Ncal^2 + \Ncal \right)\Psi} \leq C$ and $\scal{T^\ast_0 \Psi}{\Lcal_N(0)T^\ast_0 \Psi} \leq C$ for some constant $C$ independent of $N$. Then
\bd
0 \leq \scal{U_t T^\ast_0 \Psi}{\left(\Ncal+1\right)U_t T^\ast_0 \Psi} \leq C e^{K_1 e^{K_2 t}},
\ed
for some $C$, $K_1$ and $K_2$, all independent of $N$ and $t$.
\end{prp}
\begin{proof}
By Lemma \ref{lem:Llowerbound}, Corollary \ref{cor:N2} and Corollary \ref{c:reg1}, we obtain
\bd
\scal{U_t T^\ast_0 \Psi}{\Lcal_N(t) U_t T^\ast_0 \Psi} \geq - C_1 e^{M_1 t}\scal{U_t T^\ast_0 \Psi}{(\Ncal+1)U_t T^\ast_0 \Psi},
\ed
whith fixed constants $C_1$ and $M_1$. Therefore the operator
\bd
\tLcal := \Lcal_N(t) + C_1 e^{M_1 t}(\Ncal+1)
\ed
has non-negative expectation value $\scal{U_t T^\ast_0 \Psi}{\tLcal U_t T^\ast_0 \Psi} \geq 0$, so it is sufficient to prove an upper bound for $u(t) := \scal{U_t T^\ast_0 \Psi}{(\tLcal+\Ncal+1)U_t T^\ast_0 \Psi}$. We want to apply Gronwall's Lemma, so we calculate the time derivative:
\begin{align*}
 u'(t) & = \scal{U_t T^\ast_0 \Psi}{\dot \Lcal_N(t)U_t T^\ast_0 \Psi} + C_1 M_1 e^{M_1 t}\scal{U_t T^\ast_0 \Psi}{(\Ncal+1)U_t T^\ast_0 \Psi} \\
& \quad + (C_1 e^{M_1 t}+1)\scal{U_t T^\ast_0 \Psi}{i[\Lcal_N(t),\Ncal]U_t T^\ast_0 \Psi}.
\end{align*}
These expectation values can be bounded using Lemma \ref{lem:ldotbounds}, Lemma \ref{lem:lncommutatorbound} and Corollary \ref{c:reg1}:
\bd
u'(t) \leq C e^{M t} \scal{U_t T^\ast_0 \Psi}{\left(\frac{\Ncal^2}{N}+\Ncal+1+\Kcal+\tilV \right)U_t T^\ast_0 \Psi}.
\ed
By Lemma \ref{lem:kvbounds} and Corollary \ref{cor:N2} we can eliminate first $\Kcal$, $\tilV$ and then $\Ncal^2/N$ at the cost of $\Lcal_N(t)$ appearing. Then we use Lemma \ref{l:pdes} to estimate the $H^n$ norms. Then we add non-negative summands $\Ncal+1$ with an appropriate exponential prefactor to convert the $\Lcal_N(t)$ on the rhs into $\tLcal$ and arrive at
\bd
u'(t) \leq \tilde C e^{\tilde M t} u(t).
\ed
We now apply Gronwall's Lemma to conclude that
\bd
u(t) \leq u(0) \exp(K_1 e^{K_2 t})
\ed
for some constants $K_1$ and $K_2$, both independent of $N$. The factor $u(0)$ is given by
\bd
u(0) = \scal{T^\ast_0 \Psi}{(\tLcalo + \Ncal+1)T^\ast_0 \Psi}.
\ed
By Proposition \ref{p:TNT}, we know that $\scal{T^\ast_0 \Psi}{(\Ncal+1)T^\ast_0 \Psi} \leq C\scal{\Psi}{(\Ncal+1)\Psi}$. Now by assumption we see that $u(0) \leq C$ for some constant $C$.
\end{proof}

\begin{lem}
\label{lem:tilV}
 There exists a constant $C$ such that
\bd
\ev{\tilV} \leq C \ev{\Vcal_N} + C \norm{\ph}_{H^2}^2\ev{\frac{1}{N}(\Ncal+1)^2}.
\ed
 Therefor we have the following example satisfying the assumptions of Proposition \ref{prp:Nbound}:
$\Psi = T_0 \tilde \Psi$ where $\tilde \Psi$ satisfies $\scal{\tilde \Psi}{\Hcal_N \tilde \Psi} \leq C$. 
\end{lem}
\begin{proof}
Plug in $a(c_x) = a_x + a(p_x)$, multiply out and use Hoelder's inequality.
\end{proof}

\subsection{A-priori estimates}

We use short-hands for the operators at time $t=0$:
\[
  W = W_0 = W(\sqrt{N} \varphi) \qquad \text{and} \qquad T = T_0 = T(k\rvert_{t=0}).
\]
Consider two operators $A$ and $B$ on the Fock space $\mathcal{F}$. The
notation $ A \le B$ means that $\langle \psi, A \psi \rangle \le \langle \psi, B \psi \rangle$ for
all $\psi \in \mathcal{F}$.


\begin{lem} \label{l:ap}
There exists a constant $C$, uniform in $N$ and $t$,
      that depends only on $\| \varphi \|_{H^1}$ and $V$, such that
        \[
          U_t^* \N^2 U_t \le C \big( N U_t^* \N U_t + N (\N+1) + (\N+1)^2
          \big).
        \]
\end{lem}


The proof of Lemma \ref{l:ap} is based on two propositions, which we prove
first.


\begin{prp} \label{p:TNT}
  Let $k \in L^2(\R^3 \times \R^3)$ with $\nabla_1 k \in L^2(\R^3 \times
  \R^3)$, and let $f \in H^1(\R^3)$. Then, there exists a universal constant
  $C_1$, and constant $C$, that depends only on $\| k \|_{L^2}$, such that:
  \begin{align}
    T^* \N T & \le C (\N+1), \label{TNT} \tag{i} \\
    T^* \K T & \le C (\K + \| \nabla_1 k \|_{L^2}^2), \label{TKT} \tag{ii} \\
    T^* \N^2 T & \le C (\N+1)^2, \label{TN2T} \tag{iii} \\
    \phi(f) \K \phi(f) & \le C_1 \big( \| f \|_{L^2}^2 \K (\N+1) + \| \nabla f
    \|_{L^2}^2 (\N + 1) \big). \label{fKf} \tag{v}
  \end{align}
  Moreover, the same inequalities hold with $T$ replaced by $T^*$.
\end{prp}


\begin{prp} \label{p:f}
  Let $\varphi \in L^2(\R^3)$ with $\| \varphi \|_{L^2} = 1$, and let $k \in
  L^2(\R^3 \times \R^3)$. The following pull-through formulae hold:
  \begin{align}
    \N W(\sqrt{N} \varphi)^* & = W(\sqrt{N} \varphi)^* (\N - \sqrt{N}
    \phi(\varphi) + N), \tag{i} \label{f1} \\
    \N W(\sqrt{N} \varphi) & = W(\sqrt{N} \varphi) (\N + \sqrt{N}
    \phi(\varphi) + N), \tag{ii} \label{f2} \\
    W(\sqrt{N} \varphi)^* \phi(\varphi) & = (\phi(\varphi) + 2 \sqrt{N})
    W(\sqrt{N} \varphi)^*, \tag{iii} \label{f3} \\
    \phi(\varphi) T(k) & = T(k) \phi(C \varphi + S \overline{\varphi}),
    \tag{iv} \label{f4} 
  \end{align}
  where $C$ and $S$ are integral operators on $L^2(\R^3)$, with integral
  kernels $c$ and $s$ as in Lemma \ref{l:bt}, respectively.
\end{prp}

\begin{cor}
\label{cor:N2}
If $\Psi \in \fock$ with a constant $C_1$ such that $\scal{\Psi}{\left( \frac{1}{N}\Ncal^2+\Ncal \right)\Psi} \leq C_1 \scal{\Psi}{\Psi}$, then there exists a constant $C_2$ such that
\bd
\frac{1}{N}\scal{U_t T^\ast_0 \Psi}{\Ncal^2 U_t T^\ast_0 \Psi} \leq C_2 \scal{U_t T^\ast_0 \Psi}{\left(\Ncal+1\right)U_t T^\ast_0 \Psi}.
\ed
\end{cor}
\begin{proof}[Proof of Corollary \ref{cor:N2}]
This is evident from Lemma \ref{l:ap} and Proposition \ref{p:TNT}.
\end{proof}

\begin{proof}[Proof of Proposition \ref{p:f}]
  We give only an outline of the proof. Recall that $\phi(\varphi) =
  a^*(\varphi) + a(\varphi)$. Then parts \eqref{f1}, \eqref{f2} and \eqref{f3}
  follow easily by a brief calculation using parts \ref{l:W1} and \ref{l:W3}
  of Lemma \ref{l:W}. Similarly, part \eqref{f4} follows from Lemma
  \ref{l:bt}.
\end{proof}


\begin{proof}[Proof of Proposition \ref{p:TNT}]
  We first remark that it is clear that all the steps in the proof hold with
  $T$ replaced by $T^*$ because $T^* a_x T = a(c_x) + a^*(s_x)$ and $T a_x T^*
  = a(c_x) - a^*(s_x)$ differ only by a minus sign. We make no further
  comments about this.


  \eqref{TNT} and \eqref{TKT} Write
  \[
    \langle \psi, T^* \N T \psi \rangle = \int dx \, \langle T^* a_x T \psi,
    T^* a_x T \psi \rangle = \int dx \, \| (a_x + a(p_x) + a^*(s_x)) \psi
    \|^2
  \]
  and
  \[
    \langle \psi, T^* \K T \psi \rangle = \int dx \, \langle T^* \nabla_x a_x
    T \psi, T^* \nabla_x a_x T \psi \rangle = \int dx \, \| (\nabla a_x +
    a(\nabla_x p_x) + a^*(\nabla_x s_x)) \psi \|^2.
  \]
  Then, by Cauchy-Schwarz inequality, and Lemma \ref{l:a},
  \begin{align*}
    \langle \psi, T^* \N T \psi \rangle & \apprle \int dx \, \| a_x \psi \|^2
    + \int dx \, \| a(p_x) \psi \|^2 + \int dx \, \| a^*(s_x) \psi \|^2 \\
    & \apprle \langle \psi, \N \psi \rangle + \int dx \, \| p_x \|_{L^2}^2
    \langle \psi, \N \psi \rangle + \int dx \, \| s_x \|_{L^2}^2 \langle
    \psi, (\N+1) \psi \rangle \\
    & \apprle (1 + \| p \|_{L^2}^2 + \| s \|_{L^2}^2) \langle \psi, (\N+1) \psi
    \rangle
  \end{align*}
  and
  \begin{align*}
    \langle \psi, T^* \K T \psi \rangle & \apprle \int dx \, \| \nabla_x a_x
    \psi \|^2 + \int dx \, \| a(\nabla_x p_x) \psi \|^2 + \int dx \, \|
    a^*(\nabla_x s_x) \psi \|^2 \\
    & = \langle \psi, \K \psi \rangle + \int dx \, \| a(\nabla_x p_x) \psi
    \|^2 + \int dx \, \| a(\nabla_x s_x) \psi \|^2 + \| \nabla_1 s \|_{L^2}^2
    \\
    & \apprle (1 + \| p \|_{L^2}^2 + \| s \|_{L^2}^2) \langle \psi, \K \psi
    \rangle + \| \nabla_1 s \|_{L^2}^2.
  \end{align*}
  Furthermore, by Lemma \ref{l:bt}, there exists a universal
  constant $C_1$, such that
  \begin{equation} \label{c1}
    \| p \|_{L^2}^2 + \| s \|_{L^2}^2 \le e^{C_1 (1+\| k \|_{L^2})} \qquad
    \text{and} \qquad \| \nabla_1 s \|_{L^2}^2 \le e^{C_1 (1+\|k \|_{L^2})} \|
    \nabla_1 k \|_{L^2}^2.
  \end{equation}
  All this together proves parts \eqref{TNT} and \eqref{TKT}.
  

  \eqref{TN2T} Write
  \begin{align*}
    & \langle \psi, T^* \N^2 T \psi \rangle \\
    & = \int dxdy \, \langle \psi, T^* a_x^* a_x a_y^* a_y T \psi \rangle \\
    & = \int dx \, \langle \psi, T^* a_x^* \N a_x T \psi \rangle + \langle
    \psi, T^* \N T \psi \rangle \\
    & = \int dx \, \langle (a_x + a(p_x) + a^*(s_x)) \psi, T^* \N T (a_x +
    a(p_x) + a^*(s_x)) \psi \rangle + \langle \psi, T^* \N T \psi \rangle.
  \end{align*}
  Then, applying part \eqref{TNT} and Cauchy-Schwarz inequality, and using the
  pull-through formula $a_x \N^{1/2} = (\N+1)^{1/2} a_x$ and Lemma \ref{l:a},
  we obtain
  \begin{align*}
    & \langle \psi, T^* \N^2 T \psi \rangle \\
    & \apprle C \int dx \, \| (\N+1)^{1/2} (a_x + a(p_x) +
    a^*(s_x)) \psi \|^2 + C \langle \psi, (\N+1) \psi \rangle \\
    & \apprle C \int dx \, (\| a_x \N \psi \|^2 + \| a(p_x)
    \N^{1/2} \psi \|^2 + \| a^*(s_x) (\N+2)^{1/2} \psi \|^2 ) + C \langle
    \psi, (\N+1) \psi \rangle \\
    & \apprle C(1 + \| p \|_{L^2}^2 + \| s \|_{L^2}^2) \langle \psi, (\N+1)^2
    \psi \rangle.
  \end{align*}
  Recalling \eqref{c1}, this proves part \eqref{TN2T}.


   \eqref{fKf} By Cauchy-Schwarz inequality, a brief calculation, and Lemma
  \ref{l:a},
  \begin{align*}
    \langle \psi, \phi(\varphi) \K \phi(\varphi) \psi \rangle & = \| \K^{1/2}
    (a^*(\varphi) + a(\varphi) ) \psi \|^2 \\
    & \apprle \langle \psi, a(\varphi) \K a^*(\varphi) \psi \rangle + \langle
    \psi, a^*(\varphi) \K a(\varphi) \psi \rangle \\
    & = \int dx \, \| a^*(\varphi) \nabla_x a_x \psi \|^2 + \int dx \, \|
    a(\varphi) \nabla_x a_x \psi \|^2 + \int dx \, |\nabla \varphi(x)|^2 \\
    & \quad - 2 \Re \int dx dy \, \langle \nabla \varphi(x) a_y \psi, f(y)
    \nabla_x a_x \psi \rangle \\
    & \apprle \| \varphi \|_{L^2}^2 \int dx \, \| (\N + 1)^{1/2} \nabla_x a_x
    \psi \|^2 + \int dx \, | \nabla \varphi(x) |^2 \\
    & \quad + \int dx dy \, | \nabla \varphi(x)|^2 \| a_y \psi \|^2 + \int dx
    dy \, |f(y)|^2 \| \nabla_x a_x \psi \|^2 \\
    & = \| \varphi \|_{L^2}^2 \langle \psi, \K (\N + 1) \psi \rangle + \|
    \nabla \varphi \|_{L^2}^2 \langle \psi, (\N + 1) \psi \rangle.
  \end{align*}
  This proves part \eqref{fKf} and completes the proof of the proposition.
\end{proof}


\begin{proof}[Proof of Lemma \ref{l:ap}]
  Observe that, by Lemmata \ref{l:bt}, \ref{l:kernels}\ref{k} and
  \ref{l:pdes}\eqref{H1}, there exists a constant $C$, uniform in $N$ and $t$,
  that depends only on $\| \varphi \|_{H^1}$ and $V$, such that
  \begin{equation} \label{c2}
    \begin{gathered}
      \| k \|_{L^2} \le C, \qquad \| \nabla_1 k \|_{L^2} \le C \sqrt{N},
      \qquad \| \nabla_1 k \overline{k} \|_{L^2} \le C. \\
      \| p \|_{L^2}^2 + \| s \|_{L^2}^2 \le C, \qquad \| \nabla \ph
      \|_{L^2}^2 + \| \nabla_1 p \|_{L^2}^2 \le C, \qquad \| \nabla_1 s
      \|_{L^2}^2 \le C N.
    \end{gathered}
  \end{equation}


  By parts \eqref{TNT} and \eqref{TN2T} of Proposition \ref{p:TNT},
  \begin{equation}
    \label{ep4}
    \begin{split}
      \langle U_t \psi, \N^2 U_t \psi \rangle & = \langle T_t U_t \psi, T_t
      \N^2 T_t^* T_t U_t \psi \rangle \\
      & \le C \langle T_t U_t \psi, (\N+1)^2 T_t U_t \psi \rangle \\
      & \le C \langle T_t U_t \psi, \N^2 T_t U_t \psi \rangle + 2 C^2 \langle
      U_t \psi, \N U_t \psi \rangle + C. \\
    \end{split}
  \end{equation} 
  Now, using the formulae in Proposition \ref{p:f}, and noting that $\N$
  commutes with $\mathcal{H}_N$,
  \begin{align*}
    & \langle T_t U_t \psi, \N^2 T_t U_t \psi \rangle \\
    & = \langle T_t U_t \psi, \N^2 W_t^* e^{-it \mathcal{H}_N} WT \psi \rangle
    \\
    & = \langle T_t U_t \psi, \N W_t^* (\N - \sqrt{N} \phi(\ph) + N)
    e^{-it \mathcal{H}_N} WT \psi \rangle \\
    & = N \langle T_t U_t \psi, \N T_t U_t \psi \rangle - \sqrt{N} \langle T_t
    U_t \psi, \N ( \phi(\ph) + 2\sqrt{N}) W_t^* e^{-it\mathcal{H}_N} WT
    \psi \rangle \\
    & \quad + \langle T_t U_t \psi, \N W_t^* e^{-it\mathcal{H}_N} W(\N +
    \sqrt{N} \phi(\varphi) + N) T \psi \rangle \\
    & = - \sqrt{N} \langle T_t U_t \psi, \N \phi(\ph) W_t^*
    e^{-it\mathcal{H}_N} WT \psi \rangle + \sqrt{N} \langle T_t U_t \psi, \N
    W_t^* e^{-it\mathcal{H}_N} W T \phi(C \varphi + S \overline{\varphi}) \psi
    \rangle \\
    & \quad + \langle T_t U_t \psi, \N W_t^* e^{-it\mathcal{H}_N} W \N T \psi
    \rangle \\
    & = - \sqrt{N} \langle \N T_t U_t \psi, \phi(\ph) T_t U_t \psi
    \rangle + \sqrt{N} \langle \N T_t U_t \psi, T_t U_t \phi(C \varphi + S
    \overline{\varphi}) \psi \rangle \\
    & \quad + \langle \N T_t U_t \psi, T_t U_t T^* \N T \psi \rangle.
  \end{align*}
  Hence, applying Cauchy-Schwarz inequality and Lemma \ref{l:a}, and observing
  that the operator norm of $P$ and $S$ is controlled by their Hilbert-Schmidt
  norm, we get
  \begin{align*}
    & \langle T_t U_t \psi, \N^2 T_t U_t \psi \rangle \\
    & \le \| \N T_t U_t \psi \| ( \sqrt{N} \| \phi(\ph) T_t U_t \psi \|
    + \sqrt{N} \| \phi(C \varphi + S \overline{\varphi}) \psi \| + \| \N T
    \psi \| ) \\
    & \le \| \N T_t U_t \psi \| ( 2 \sqrt{N} \| \ph \|_{L^2} \|
    (\N+1)^{1/2} T_t U_t \psi \| \\
    & \quad + 2 \sqrt{N} ( 1 + \| p \|_{L^2} + \| s \|_{L^2}) \| \varphi
    \|_{L^2} \| (\N+1)^{1/2} \psi \| + \| \N T \psi \| ) \\
    & \le \frac{3}{4} \| \N T_t U_t \psi \|^2 + 16N \| (\N + 1)^{1/2} T_t U_t
    \psi \|^2 \\
    & \quad + 16N (1 + \| p \|_{L^2} + \| s \|_{L^2})^2 \| (\N + 1)^{1/2}
    \psi \|^2 + 4\| \N T \psi \|^2.
  \end{align*}
  Thus, using again Proposition \ref{p:TNT}, and recalling \eqref{c2},
  \begin{align*}
    & \langle T_t U_t \psi, \N^2 T_t U_t \psi \rangle \\
    & \le C_1 \big( N \langle U_t \psi, T_t^* (\N+1) T_t U_t \psi \rangle + N
    \langle \psi, (\N+1) \psi \rangle + \langle \psi, T^* \N^2 T \psi \rangle
    \big) \\
    & \le C_2 \big( N \langle U_t \psi, (\N+1) U_t \psi \rangle + N \langle
    \psi, (\N+1) \psi \rangle + \langle \psi, (\N+1)^2 \psi \rangle \big),
  \end{align*}
  for some constants $C_1$ and $C_2$ that depend only on $\| \varphi \|_{H^1}$
  and $V$. Combining this with \eqref{ep4}, we obtain
  \begin{align*}
    \langle U_t \psi, \N^2 U_t \psi \rangle 
    & \le C \langle T_t U_t \psi, \N^2 T_t U_t \psi \rangle + 2 C^2
    \langle U_t \psi, \N U_t \psi \rangle + C. \\
    & \le C_3 \big( N \langle U_t \psi, \N U_t \psi \rangle + N \langle
    \psi, (\N+1) \psi \rangle + \langle \psi, (\N+1)^2 \psi \rangle \big),
  \end{align*}
  for some constant $C_3$ as above. This concludes the proof.
\end{proof}



\section{Convergence of Expectation Values}
\begin{lem}
\label{lem:TrJ}
Let $\Psi \in \fock$ and assume there is a constant $C_1$ such that $\scal{\Psi}{\left(\frac{1}{N}\Ncal^2 + \Ncal\right)\Psi} \leq C_1 \scal{\Psi}{\Psi}$. Let $J$ be a Hilbert-Schmidt operator (a one-particle observable). Then there exists a constant $C_2$ (independent of $N$ and $t$) such that
\bd
\left\lvert \Tr\left(J \gamma_{N,t}^{(1)} \right) - \Tr\left( J \project{\ph}  \right) \right\rvert \leq \frac{d_N}{\sqrt{N}}C_2 \norm{J}_{HS} \left( \scal{U_N(t) T^\ast_0 \Psi}{\left( \Ncal+1 \right)U_N(t) T^\ast_0 \Psi} \right)^{1/2},
\ed
where $d_N = \norm{P_N W_0\Psi}^{-1}$ and 
\bd
\gamma_{N,t}^{(1)}(x;y) = \frac{\scal{e^{-it \Hcal_N} d_N P_N W_0 \Psi}{a^\ast_y a_x e^{-it \Hcal_N} d_N P_N W_0 \Psi}}{\scal{d_N P_N W_0 \Psi}{\Ncal d_N P_N W_0 \Psi}}.
\ed
The operator $P_N$ is the projection on the $N$-particle subspace of Fock space.
%
%Remark: $\ph$ needn't be a solution of the Hartree equation here.
\end{lem}
\begin{proof}
In the first step we use that $P_N$ commutes with $e^{-it \Hcal_N}$ (because $\Hcal_N$ conserves the particle number) and that $P_N$ commutes with $a^\ast_y a_x$, so because of $P_N^2 = P_N$, one of the projections $P_N$ can be eliminated. After that, we insert $W^\ast_t W_t$ and apply Lemma \ref{l:W} \ref{l:W3}.
\begin{align}
& \Tr\left(J\gamma_{N,t}^{(1)}\right) \nonumber\\
& = \frac{d_N^2}{N} \int \di x\di y \scal{e^{-it\Hcal_N}P_N W_0 \Psi}{ a^\ast_y a_x e^{-it\Hcal_N t}P_N W_0 \Psi} J(x,y) \nonumber\\
& = \frac{d_N^2}{N} \int \di x\di y \scal{e^{-it\Hcal_N}P_N W_0 \Psi}{ a^\ast_y a_x e^{-it\Hcal_N t}W_0 \Psi} J(x,y) \nonumber\\
& = \frac{d_N^2}{N} \int \di x\di y \scal{W^\ast_t e^{-it\Hcal_N}P_N W_0 \Psi}{\left(a^\ast_y + \sqrt{N} \ph(y) \right) \times \nonumber\\
& \qquad\qquad\qquad\qquad \times \left(a_x + \sqrt{N} \ph(x) \right) W^\ast_t e^{-it\Hcal_N t}W_0 \Psi} J(x,y) \nonumber\\
& = \frac{d_N^2}{N} \int \di x\di y J(x,y) \scal{W^\ast_t e^{-it\Hcal_N}P_N W_0 \Psi}{a^\ast_y a_x W^\ast_t e^{-it \Hcal_N} W_0 \Psi} \label{eq:quad}\\
& \quad + \frac{d_N^2}{N} \int \di x\di y J(x,y) \sqrt{N} \ph(x) \scal{W^\ast_t e^{-it\Hcal_N} P_N W_0 \Psi}{a^\ast_y W^\ast_t e^{-it \Hcal_N} W_0 \Psi} \label{eq:lin1} \\
& \quad + \frac{d_N^2}{N} \int \di x\di y J(x,y) \sqrt{N} \cc{\ph(y)} \scal{W^\ast_t e^{-it\Hcal_N}P_N W_0 \Psi}{a_x W^\ast_t e^{-it\Hcal_N} W_0 \Psi} \label{eq:lin2} \\
& \quad + \frac{d_N^2}{N} \int \di x\di y J(x,y) N \cc{\ph(y)}\ph(x) \scal{W^\ast_t e^{-it\Hcal_N} P_N W_0 \Psi}{W^\ast_t e^{-it\Hcal_N} W_0 \Psi}. \label{eq:gamma}
\end{align}
The last line, \eqref{eq:gamma}, is the expectation value of the factorized state:
\begin{align*}
& \frac{d_N^2}{N} \int \di x\di y J(x,y) N \cc{\ph(y)}\ph(x) \scal{W^\ast_t e^{-it\Hcal_N} P_N W_0 \Psi}{W^\ast_t e^{-it\Hcal_N} W_0 \Psi} \\
& = \frac{d_N^2}{N} \int \di x\di y J(x,y) N \cc{\ph(y)}\ph(x) \scal{P_N W_0 \Psi}{W_0 \Psi} \\
& = \int \di x\di y J(x,y) \cc{\ph(y)} \ph(x) = \Tr\left( J\project{\ph} \right).
\end{align*}
Summands \eqref{eq:quad} - \eqref{eq:lin2} have to be estimated. We start with line \eqref{eq:lin1}:
\begin{align*}
& \left\lvert \frac{d_N^2}{N} \int \di x\di y J(x,y) \sqrt{N} \ph(x) \scal{W^\ast_t e^{-it\Hcal_N} P_N W_0 \Psi}{a^\ast_y W^\ast_t e^{-it \Hcal_N} W_0 \Psi} \right\rvert \\
& \leq \frac{d_N^2}{N} \int \di x \sqrt{N} \lvert \ph(x)\rvert \norm{W^\ast_t e^{-it \Hcal_N} P_N W_0 \Psi} \norm{ a^\ast(J(x,\cdot))W^\ast_t e^{-it \Hcal_N} W_0 \Psi} \\
& \leq \frac{d_N}{\sqrt{N}} \int \di x \lvert \ph(x)\rvert \norm{J(x,\cdot)}_{L^2} \norm{(\Ncal+1)^{1/2}W^\ast_t e^{-it\Hcal_N}W_0 \Psi} \\
& \leq \frac{d_N}{\sqrt{N}} \norm{\ph}_{L^2} \norm{J}_{\textrm{HS}} \left( \scal{W^\ast_t e^{-it \Hcal_N}W_0 \Psi}{(\Ncal+1)W^\ast_t e^{-it\Hcal_N} W_0 \Psi} \right)^{1/2} \\
& \leq \frac{d_N}{\sqrt{N}} \norm{J}_{\textrm{HS}} \left(C \scal{U_t T^\ast_0 \Psi}{(\Ncal+1)U_t T^\ast_0 \Psi} \right)^{1/2}.
\end{align*}
Line \eqref{eq:lin2} can be estimated in the same way as line \eqref{eq:lin1}.

Recall that $\di\Gamma(J) := \int \di x\di y J(y,x) a^\ast_x a_y$ can be estimated by $\norm{\di\Gamma(J)\zeta} \leq \norm{J}_{\textrm{HS}} \norm{\Ncal \zeta}$ for all $\zeta \in D(\Ncal) \subset \fock$. We now estimate line \eqref{eq:quad}.
\begin{align*}
& \left\lvert \frac{d_N^2}{N} \int \di x\di y J(x,y) \scal{W^\ast_t e^{-it\Hcal_N} P_N W_0 \Psi}{a^\ast_y a_x W^\ast_t e^{-it \Hcal_N}W_0 \Psi} \right\rvert \\
& = \frac{d_N^2}{N} \scal{W^\ast_t e^{-it\Hcal_N}P_N W_0 \Psi}{\di\Gamma(J) W^\ast_t e^{-it\Hcal_N}W_0 \Psi} \\
& \leq \frac{d_N^2}{N} \underbrace{\norm{W^\ast_t e^{-it\Hcal_N}P_N W_0 \Psi}}_{=\norm{P_N W_0 \Psi}= d_N^{-1}} \norm{\di\Gamma(J)W^\ast_t e^{-it \Hcal_N}W_0 \Psi} \\
& \leq \frac{d_N}{N} \norm{J}_{\textrm{HS}} \norm{\Ncal W^\ast_t e^{-it\Hcal_N}W_0 \Psi} \\
& = \frac{d_N}{\sqrt{N}} \norm{J}_{\textrm{HS}} \left( \frac{1}{N} \scal{W^\ast_t e^{-it\Hcal_N}W_0 \Psi}{\Ncal^2 W^\ast_t e^{-it\Hcal_N}W_0 \Psi} \right)^{1/2} \\
& \leq \frac{d_N}{\sqrt{N}} \norm{J}_{\textrm{HS}} \left( \frac{C}{N} \scal{U_t T^\ast_0 \Psi}{(\Ncal+1)^2 U_t T^\ast_0 \Psi} \right)^{1/2}.
\end{align*}
In the last step, Proposition \ref{p:TNT} (\ref{TN2T}) has been used in the form of $\Ncal^2 \leq C T_t (\Ncal+1)^2 T^\ast_t$. The estimate is completed using Corollary \ref{cor:N2} to bound $\Ncal^2/N$ by $\Ncal+1$.
\end{proof}

\begin{lem}
\label{lem:phNtoph}
Let $\ph$ be the solution to the modified Hartree equation with initial data $\varphi_0 = \varphi$ and let $\varphi_t$ be the solution to the Gross-Pitaevskii equation with initial data $\varphi_0 = \varphi$.

Then there exists a constant $C$ independent of $N$ and $t$ such that for any one-particle Hilbert-Schmidt operator $J$ the following estimate holds:
\bd
\left\lvert \Tr\left(J \project{\ph}\right) - \Tr\left(J \project{\varphi_t}\right) \right\rvert \leq \norm{J}_{\textrm{HS}} \frac{C}{N} e^{e^{Kt}}.
\ed
\end{lem}
\begin{proof}
Using Hoelder's inequality, we calculate that
\begin{align*}
& \left\lvert \int \di x \di y J(x,y) \cc{\ph(y)} \ph(x) - \int \di x\di y J(x,y) \cc{\varphi_t(y)} \varphi_t(x) \right\rvert \\ 
& \leq \int \di x \di y \lvert J(x,y)\rvert \lvert \ph(y) - \varphi_t(y)\rvert \lvert \ph(x)\rvert + \int \di x \di y \lvert J(x,y) \rvert \lvert \varphi_t(y)\rvert \lvert \ph(x)-\varphi_t(x)\rvert \\
& \leq \norm{\ph}_{L^2} \norm{J}_{\textrm{HS}} \norm{\ph - \varphi_t}_{L^2} + \norm{\varphi_t}_{L^2} \norm{J}_{\textrm{HS}} \norm{\ph - \varphi_t}_{L^2}. 
\end{align*}
\marginpar{I would write the last inequality and they say by Lemma\dots}
The proof is finished noticing that $\norm{\varphi_t}_{L^2} = \norm{\ph}_{L^2} = 1$ and, by Lemma \ref{lem:phitN2phit}, $\norm{\ph - \varphi_t}_{L^2} \leq C e^{e^{KT}}/N$.
\end{proof}

\begin{proof}[Proof of Theorem \ref{thm:main_factorized}]
We choose $\Psi = \Omega$ in Lemma \ref{lem:TrJ}. Then $d_N P_N W_0 \Psi = \varphi^{\otimes N}$ and $d_N = \frac{\sqrt{N!}}{e^{-N/2}N^{N/2}} \simeq N^{1/4}$.

We want to apply Proposition \ref{prp:Nbound} now. Clearly $\scal{\Omega}{\left(\frac{1}{N}\Ncal^2 + \Ncal\right)\Omega} = 0$ satisfies the assumption of the proposition. We have to check the assumption on 
\bd
\scal{T^\ast_0 \Omega}{\Lcal_N(0)T^\ast_0 \Omega} = \scal{\Omega}{\left(T_0(i\partial_t T^\ast_t)\rvert_{t=0} + \Lcal_N^{(0)}(0)\right)\Omega}.
\ed
According to \eqref{eq:no3}, $\Lcal_N^{(0)}(0)$ is normal-ordered and thus $\scal{\Omega}{\Lcal_N^{(0)}(0)\Omega} = 0$ (remember that the scalar term in $\Lcal_N^{(0)}(0)$ was dropped because it corresponds to an overall phase). The expectation value $\scal{\Omega}{T_0(i\partial_t T^\ast_t)\rvert_{t=0} \Omega}$ can be bounded by Lemma \ref{lm:timederivative} with $t=0$.

The proof is completed by employing Lemma \ref{lem:phNtoph}.
\end{proof}

%%%%%%%%%%%%%%%%%%%%%%%%%%%% APPENDIX %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\appendix
\section{Estimates for the terms of the generator}
\label{ch:generatorestimates}
The estimates in this section hold for the expectation value $\ev{\cdot} = \scal{\psi}{\cdot\psi}$ in any state $\psi \in \fock$. Especially, $C$ stands for constants independent of $N$, $t$ and $\psi$.

For convenience, we remind the reader of the simple but useful estimate
\bd
\int \di x\, \norm{a(c_x)\psi}^2 \leq 2(1+\norm{p}^2)\scal{\psi}{\Ncal\psi} \leq C\ev{\Ncal}.
\ed
We now have the following list of estimates for the terms of the generator.\newline
\underline{We start with estimates for the kinetic terms:}\newline
\estlist{7}{1} (here, the cancellation is important!)
\begin{align*}
& \lvert \scal{\psi}{\frac{1}{2}\int \di x\,a^\ast(c_x) \int \di y\,a^\ast_y N\nabla_x w_N(x-y)\nabla_x \ph(x) 2\ph(y) \psi}\rvert \\
& \leq \lvert \int \di x \di y\, Nw_N(x-y) \nabla_x \ph(x)  \nabla_y \ph(y) \scal{a_y\psi}{a^\ast_x\psi} \rvert \\
& \quad + \lvert \int \di x \di y\,  Nw_N(x-y) \nabla_x \ph(x) \ph(y)  \scal{(\nabla_y a_y)\psi}{a^\ast_x \psi} \rvert \\
& \quad + \lvert \int \di x \di y\, Nw_N(x-y) \nabla_x  \ph(x) \nabla_y \ph(y) \scal{a_y \psi}{a^\ast(p_x)\psi} \rvert \\
& \quad + \lvert \int \di x \di y\, Nw_N(x-y) \nabla_x \ph(x) \ph(y) \scal{(\nabla_y a_y)\psi}{a^\ast(p_x)\psi} \rvert \\
&\leq \int \di y \lvert \nabla_y \ph(y)\rvert \norm{a_y \psi} \norm{a^\ast(Nw_N(\cdot -y)\nabla\ph(\cdot))\psi} \\
& \quad + \int \di y \lvert \ph(y)\rvert \norm{(\nabla_y a_y)\psi} \norm{a^\ast(Nw_N(\cdot-y)\nabla\varphi(\cdot))\psi} \\
& \quad + \int \di x\di y\, \frac{C}{\lvert x-y\rvert} \lvert \nabla_x\ph(x)\rvert \lvert \nabla_y \ph(y)\rvert \norm{a_y \psi} \norm{p_x} \norm{(\Ncal+1)^{1/2}\psi} \\
& \quad + \int \di x\di y\, \frac{C}{\lvert x-y\rvert} \lvert \nabla_x\ph(x)\rvert \lvert \ph(y)\rvert \norm{(\nabla_y a_y)\psi} \norm{p_x} \norm{(\Ncal+1)^{1/2}\psi} \\
&\leq C \norm{\Delta\ph}_{L^2} \norm{(\Ncal+1)^{1/2}\psi} \int \di y \lvert \nabla_y \ph(y) \rvert \norm{a_y \psi} \\
& \quad + C \norm{\Delta \ph}_{L^2} \norm{(\Ncal+1)^{1/2}\psi} \int \di y \frac{1}{\sqrt{\varepsilon}} \lvert \ph(y)\rvert \sqrt{\varepsilon} \norm{(\nabla_y a_y)\psi} \\
& \quad + C \norm{(\Ncal+1)^{1/2}\psi} \left(\int \di x\di y \lvert \nabla_x\ph(x)\rvert^2 \frac{\lvert\nabla_y \ph(y)\rvert^2}{\lvert x-y \rvert^2} \right)^{1/2} \left(\int \di x\di y \norm{a_y \psi}^2 \norm{p_x}^2 \right)^{1/2} \\
& \quad + C \norm{(\Ncal+1)^{1/2}\psi} \left(\int \di x\di y \lvert \nabla_x\ph(x)\rvert^2 \frac{\lvert \ph(y)\rvert^2}{\lvert x-y\rvert^2} \right)^{1/2} \left(\int \di x\di y \norm{(\nabla_y a_y)\psi}^2 \norm{p_x}^2 \right)^{1/2} \\
& \leq C \norm{\Delta \ph}_{L^2} \norm{(\Ncal+1)^{1/2}\psi} \norm{\nabla \ph}_{L^2} \norm{\Ncal^{1/2}\psi} \\
& \quad + C\norm{\Delta \ph}_{L^2} \frac{1}{\sqrt{\varepsilon}} \norm{(\Ncal+1)^{1/2}\psi}  \sqrt{\varepsilon}\norm{\Kcal^{1/2}\psi} \norm{\ph}_{L^2} \\
& \quad + C \norm{(\Ncal+1)^{1/2}\psi} \norm{\nabla \ph}_{L^2} \norm{\Delta \ph}_{L^2} \norm{p} \norm{\Ncal^{1/2}\psi} \\
& \quad + C \frac{1}{\sqrt{\varepsilon}}\norm{(\Ncal+1)^{1/2}\psi} \sqrt{\varepsilon}\norm{\Kcal^{1/2}\psi} \norm{\nabla \ph}_{L^2}^2 \norm{p} \\
& \leq C \norm{\ph}_{H^2} \left( (1+\frac{1}{\varepsilon})\ev{\Ncal+1} + \varepsilon\ev{\Kcal} \right) + C \left( \frac{1}{\varepsilon}\ev{\Ncal+1} + \varepsilon \ev{\Kcal} \right).
\end{align*}
\estlist{8}{1} (here, the cancellation is important!)
\begin{align*}
&\lvert \scal{\psi}{\frac{1}{2}\int \di x\di y\,a^\ast(c_x) a^\ast_y N w_N(x-y) \Delta_x \ph(x) \ph(y) \psi}\rvert\\
& \leq \frac{1}{2} \int \di x\, \norm{a(c_x)\psi} \lvert \Delta_x \ph(x)\rvert \norm{a^\ast(Nw_N(x-\cdot)\ph(\cdot))\psi} \\
& \leq \frac{1}{2} \int \di x\, \norm{a(c_x)\psi} \lvert \Delta_x \ph(x)\rvert \norm{N w_N(x-\cdot)\ph(\cdot)}_{L^2} \norm{(\Ncal+1)^{1/2}\psi} \\
& \leq \frac{1}{2} C \norm{\nabla\ph}_{L^2} \norm{(\Ncal+1)^{1/2} \psi} \left( \int \di x\, \lvert \Delta_x \ph(x)\rvert^2 \right)^{1/2} \left( \int \di x\, \norm{a(c_x)\psi}^2 \right)^{1/2} \\
& \leq \frac{1}{2} C \norm{\ph}_{H^1} \norm{\ph}_{H^2} \ev{\Ncal+1} \\
& \leq C \norm{\ph}_{H^2} \ev{\Ncal+1}
\end{align*}
where $\norm{Nw_N(x-\cdot)\ph(\cdot)}_{L^2} \leq C\norm{\nabla \ph}_{L^2}$ was used.\\
\estlist{8}{2}
For this estimate, it is useful to know that
\begin{equation} \label{eq:bound1B}                                     
\begin{split}
 & \scal{\psi}{\frac{1}{2}\int \di x a^\ast(c_x) a(-\Delta_x c_x)\psi} = \int \di x\, \norm{\nabla_x a(c_x)\psi}^2 \\
 & \leq 2 \int \di x\, \norm{\nabla_x a_x \psi}^2 + 2\int \di x\, \norm{a(\nabla_x p_x)\psi}^2 \leq 2\ev{\Kcal} + 2\int \di x\, \norm{\nabla_x p_x}^2 \norm{\Ncal^{1/2}\psi}^2 \\
 & = 2\ev{\Kcal}+ 2\norm{\gradone p}^2 \ev{\Ncal} \leq C\ev{\Kcal + \Ncal}.
\end{split}
\end{equation}
Using \eqref{eq:bound1B} and integration by parts we get
\begin{align*}
& \lvert \scal{\psi}{\frac{1}{2}\int \di x\, a^\ast(c_x) \int \di y\, (-\Delta_x r(y,x))\psi} \rvert \\
& = \lvert \scal{\psi}{\frac{1}{2}\int \di x\, \nabla_x a^\ast(c_x) \int \di y\, a^\ast_y \nabla_x r(y,x) \psi}\rvert \\
& \leq \frac{1}{2}\int \di x\, \norm{\nabla_x a(c_x)\psi} \norm{a^\ast(\nabla_x r_x)\psi} \\
& \leq \frac{1}{2}\left( \varepsilon \int \di x\, \norm{\nabla_x a(c_x) \psi}^2 \right)^{1/2} \left( \int \di x\, \norm{\nabla_x r_x}^2 \right)^{1/2} \frac{1}{\sqrt{\varepsilon}} \norm{(\Ncal+1)^{1/2}\psi} \\
& \leq \frac{1}{2}\norm{\gradone r} \left( \varepsilon 2\ev{\Kcal} + \varepsilon 2 \norm{\gradone p}^2 \ev{\Ncal} + \frac{1}{\varepsilon}\ev{\Ncal+1} \right) \\
& \leq C \left( \varepsilon \ev{\Kcal} + (\varepsilon+\frac{1}{\varepsilon})\ev{\Ncal+1} \right).
\end{align*}
\estlist{9}{1}
First notice that
\begin{align*}
 & \scal{\psi}{\frac{1}{2}\int \di x\, a^\ast(c_x) a(-\Delta_x c_x)\psi} = \scal{\psi}{\frac{1}{2}\int \di x\, a^\ast(\nabla_x c_x)a(\nabla_x c_x)\psi} \\
& = \scal{\psi}{\frac{1}{2}\int \di x \left( \nabla_x a^\ast_x + a^\ast(\nabla_x p_x) \right)\left(  \nabla_x a_x + a(\nabla_x p_x) \right) \psi} \\
& = \scal{\psi}{\frac{1}{2}\Kcal \psi} + \frac{1}{2}\int \di x\scal{\nabla_x
a_x \psi}{a(\nabla_x p_x)\psi} \\
& \quad + \frac{1}{2}\int \di x\, \scal{a(\nabla_x p_x)\psi}{\nabla_x a_x \psi} + \frac{1}{2}\int \di x\, \norm{a(\nabla_x p_x)\psi}^2.
\end{align*}
Leaving away the last summand, which is positive, we get
\begin{equation}
\label{eq:bound1A}
\begin{split}
 \ev{\Kcal} & \leq \scal{\psi}{\int \di x\, a^\ast(c_x) a(-\Delta_x c_x)\psi} + 2\int \di x\, \sqrt{\varepsilon} \norm{\nabla_x a_x \psi} \frac{1}{\sqrt{\varepsilon}} \norm{a(\nabla_x p_x)\psi} \\
& \leq \scal{\psi}{\int \di x\, a^\ast(c_x) a(-\Delta_x c_x)\psi} + 2\left( \varepsilon \ev{\Kcal} + \frac{1}{\varepsilon}  \norm{\gradone p}^2 \ev{\Ncal}\right) \\
& \leq \scal{\psi}{\int \di x\,a^\ast(c_x) a(-\Delta_x c_x)\psi} + C\left( \varepsilon \ev{\Kcal} + \frac{1}{\varepsilon}\ev{\Ncal} \right).
\end{split}
\end{equation}
\estlist{9}{2}
First, notice that, using the product rule, integration by parts and the fact that $-\nabla_x w_N(x-y) = \nabla_y w_N(x-y)$, we have
\begin{align*}
 a(\nabla_x s_x) & = \cc{\ph(x)} a(-Nw_N(x-\cdot)\nabla\ph(\cdot)) + \cc{\ph(x)}\,a\left(\nabla(-N w_N(x-\cdot)\ph(\cdot))\right) \\
 & + \cc{\nabla_x \ph(x)} a(-Nw_N(x-\cdot)\ph(\cdot)) + a(\nabla_x r_x).
\end{align*}
(The $\nabla$ in the second summand of the first line has to be understood with respect to the 'dot'-variable.)
Using $(a+b+c+d)^2 \leq 4(a^2+b^2+c^2+d^2)$, we now conclude
\begin{equation}
\label{eq:bound2B}
\begin{split}
 & \scal{\psi}{\frac{1}{2}\int \di x\, a^\ast(-\Delta s_x) a(s_x)\psi} = \frac{1}{2}\int \di x\, \norm{a(\nabla_x s_x)\psi}^2 \\
& \leq \frac{1}{2} \int \di x \bigg( \lvert \ph(x)\rvert \norm{a(-Nw_N(x-\cdot)\nabla\ph(\cdot))\psi} \\
& \qquad\qquad\quad + \lvert \ph(x)\rvert \norm{a\left(\nabla(-N w_N(x-\cdot)\ph(\cdot))\right)\psi} \\
& \qquad\qquad\quad + \lvert \nabla_x \ph(x)\rvert \norm{a(-Nw_N(x-\cdot)\ph(\cdot))\psi} + \norm{a(\nabla_x r_x)\psi}  \bigg)^2 \\
& \stackrel{\eqr{agradnorm}}{\leq} 2\int \di x\, \bigg( \lvert \ph(x)\rvert^2 \norm{-N w_N(x-\cdot)\nabla\ph(\cdot)}_{L^2}^2 \norm{\Ncal^{1/2}\psi}^2  \\
& \qquad\qquad\quad + \lvert \ph(x)\rvert^2 \norm{-Nw_N(x-\cdot) \ph(\cdot)}_{L^2}^2 \norm{\Kcal^{1/2}\psi}^2  \\
& \qquad\qquad\quad + \lvert \nabla_x \ph(x)\rvert^2 \norm{-N w_N(x-\cdot) \ph(\cdot)}_{L^2}^2 \norm{\Ncal^{1/2}\psi}^2 + \norm{\nabla_x r_x}^2 \norm{\Ncal^{1/2}\psi}^2 \bigg) \\
& \leq 2 \int \di x\, \bigg( \lvert \ph(x)\rvert^2 \norm{\Delta \ph}_{L^2}^2 C \norm{\Ncal^{1/2}\psi}^2 + \lvert \ph(x)\rvert^2 \norm{\nabla \ph}_{L^2}^2 C \norm{\Kcal^{1/2}\psi}^2 \\
& \qquad\qquad\quad + \lvert \nabla_x \ph(x)\rvert^2 \norm{\nabla \ph}_{L^2}^2 C \norm{\Ncal^{1/2}\psi}^2 + \norm{\nabla_x r_x}^2 \norm{\Ncal^{1/2}\psi}^2 \bigg)\\
& \leq C \norm{\ph}_{H^2}^2 \ev{\Ncal} + C\ev{\Kcal} + C\ev{\Ncal}.
\end{split} 
\end{equation}
Here we made use of the following estimates: $\norm{-N w_N(x-\cdot) \nabla\ph(\cdot)}_{L^2}^2 \leq C\norm{\Delta \ph}_{L^2}$, $\norm{-N w_N(x-\cdot)\ph(\cdot)}^2 \leq C \norm{\nabla \ph}^2$  and $ \norm{\gradone r} \leq C$.

\underline{Estimates for the non-kinetic terms:}\newline
In proving the following estimates, the important ideas are
\begin{itemize}
 \item $a^*(c_x)\psi$ is ill-defined because $c_x = \delta_x + p_x$, thus each $a^\ast(c_x)$ has to be moved to the other argument of the scalar product as $a(c_x)$
\item use Cauchy-Schwarz in such a way that at most two operators $a^\#$ act on each $\psi$. Usually, following Cauchy-Schwarz we also apply Hoelder's inequality in the form
\bd
\begin{split}
& \int \di x \di y\, V_N(x-y) f(x,y) g(x,y) = \int \di x \di y\, \sqrt{V_N(x-y)}^2 f(x,y) g(x,y)\\
&  \leq \int \di x\di y\, V_N(x-y) \lvert f(x,y)\rvert^2 + \int \di x\di y\, V_N(x-y) \lvert g(x,y)\rvert^2.
\end{split}
\ed
 \item for summands containing $a(c_x) a(c_y) \psi$, insert $\sqrt{\varepsilon} \frac{1}{\sqrt{\varepsilon}}$ and then use Hoelder, so that $\varepsilon\ev{\tilV}$ is obtained
 \item $a^\#(s_x)$ and $a^\#(p_x)$ are always ok, and can easily be estimated using Lemma \ref{l:a}.
 \item pull out $\sup_x \norm{s_x}^2$, $\sup_x \norm{p_x}^2$ and $\norm{\ph}_\infty$ from the integrals, then $\int \di y\, NV_N(x-y) = b_0$ (independent of $x$) can be used
\item for terms containing $a^\# a^\# a^\#$ or $a^\# a^\# a^\# a^\#$ we need $\Ncal^2$, so a prefactor $1/N$ is necessary. Cf.\ \ref{cor:N2}. 
\end{itemize}

\estlist{10}{1}
By definition of $\tilV$, we have
\bd
\scal{\psi}{\frac{1}{2}\int \di x\di y\, NV_N(x-y)\frac{1}{2N} a^\ast(c_x) a^\ast(c_y) a(c_y) a(c_x)\psi} = \ev{\tilV}.
\ed
\estlist{10}{2}
\begin{align*}
 & \lvert \scal{\psi}{\dxyNV \frac{1}{2N} 4 a^\ast(c_x)a^\ast(c_y) a^\ast(s_x)a(c_y)\psi}\rvert \\
& \leq \int \di x\di y V_N(x-y) \frac{\sqrt{\varepsilon}}{2} \norm{a(c_y) a(c_x)\psi} \frac{2}{\sqrt{\varepsilon}} \norm{a^\ast(s_x)a(c_y)\psi} \\
& \leq \frac{\varepsilon}{4} \int \di x\di y V_N(x-y) \scal{\psi}{a^\ast(c_x)a^\ast(c_y)a(c_y)a(c_x)\psi} + \frac{4}{\varepsilon} \int \di x\di y V_N(x-y) \norm{a^\ast(s_x)a(c_y)\psi}^2 \\
& \leq \varepsilon \ev{\tilV} + \frac{4}{\varepsilon}\int \di x\di y V_N(x-y) \norm{s_x}^2 \norm{a(c_y)\Ncal^{1/2}\psi}^2 \\
& \leq \varepsilon \ev{\tilV} + \frac{4}{\varepsilon} \sup_x \norm{s_x}^2 \int \di y\, \norm{a(c_y)\Ncal^{1/2}\psi}^2 \int \di x\, V_N(x-y)\\
& \leq \varepsilon \ev{\tilV} + \frac{4}{\varepsilon} \sup_x \norm{s_x}^2 \int \di y\, \norm{a(c_y)\Ncal^{1/2}\psi}^2 \frac{b_0}{N}\\
& \leq \varepsilon \ev{\tilV} + \frac{4}{\varepsilon} \sup_x \norm{s_x}^2 \frac{b_0}{N} 2 (1+\norm{p}^2)\ev{\Ncal^2} \\
& \leq \varepsilon \ev{\tilV} + C\norm{\ph}_{H^2}^2 \frac{1}{\varepsilon} \frac{1}{N}\ev{\Ncal^2}.
\end{align*}
\estlist{11}{1}
\begin{align*}
& \lvert \scal{\psi}{\dxyNV \frac{1}{2N}2a^\ast(c_x)a^\ast(c_y) a^\ast(s_y) a^\ast(s_x) \psi}\rvert \\
& \leq 2\frac{1}{4}\int \di x\di y\, V_N(x-y)  \norm{a(c_y)a(c_x)\psi} \norm{a^\ast(s_y)a^\ast(s_x)\psi} \\
& \leq \varepsilon 2 \ev{\tilV} + \frac{1}{2\varepsilon} \int \di x\di y\, V_N(x-y) \norm{a^\ast(s_y)a^\ast(s_x)\psi}^2 \\
& \leq \varepsilon 2 \ev{\tilV} + \frac{1}{2\varepsilon} \int \di x\di y\, V_N(x-y) \norm{s_y}^2 \norm{s_x}^2 \ev{(\Ncal+2)^2} \\
& \leq \varepsilon 2 \ev{\tilV} + \frac{1}{2\varepsilon} \sup_x \norm{s_x}^2 \int \di y\, \norm{s_y}^2 \int \di x\, V_N(x-y) \ev{(\Ncal+2)^2} \\
& \leq \varepsilon 2\ev{\tilV} + C\norm{\ph}_{H^2}^2 \frac{1}{\varepsilon} \frac{1}{N}\ev{(\Ncal+2)^2}.
\end{align*}
\estlist{11}{2}
\begin{align*}
& \lvert \scal{\psi}{\dxyNV \frac{1}{2N} 2 a^\ast(c_x) a^\ast(s_x) a(s_y) a(c_y)\psi}\rvert \\
& \leq \frac{1}{2}\int \di x\di y\, V_N(x-y) \norm{a(s_x) a(c_x) \psi} \norm{a(s_y) a(c_y)\psi} \\
& \leq \int \di x\di y\, V_N(x-y) \norm{s_y}^2 \norm{a(c_y) \Ncal^{1/2}\psi}^2\\
& \leq \sup_y \norm{s_y}^2 \int \di y\, \norm{a(c_y)\Ncal^{1/2}\psi}^2 \int \di x\, V_N(x-y)\\
& \leq C \norm{\ph}_{H^2}^2 \frac{1}{N}\ev{\Ncal^2}.
\end{align*}
Here we made use of the fact that both summands originating from the Hoelder inequality are equal, as can be seen by interchanging the integration variables $x$ and $y$.\newline
\underline{\Nestlist{12}{1}, \nestlist{12}{2} and \nestlist{13}{1}:} can be estimated in the same way as \nestlist{11}{2}.\newline
\estlist{14}{1} (here, cancellation is important!)
\begin{align*}
& \lvert \scal{\psi}{\dxyNV \frac{1}{N}a^\ast(c_x) a^\ast(c_y) \left( r(y,x)+\scal{p_y}{s_x} \right)\psi} \rvert \\
& \leq \varepsilon \dxyV \norm{a(c_y)a(c_x)\psi}^2 + \frac{1}{\varepsilon} \dxyV \lvert r(y,x)+\scal{p_y}{s_x} \rvert^2 \\
& \leq \varepsilon 2\ev{\tilV} + \frac{1}{\varepsilon} \int \di x\di y\, V_N(x-y) \left( C\lvert\ph(x)\rvert^2\lvert\ph(y)\rvert^2 +\norm{p_y}^2\norm{s_x}^2 \right) \\
& \leq \varepsilon 2\ev{\tilV} + \frac{C}{\varepsilon} \norm{\ph}_\infty^2 \int \di x \di y\, \lvert \ph(y)\rvert^2 V_N(x-y) + \frac{1}{\varepsilon} \sup_x\norm{s_x}^2 \int \di x\di y\, \norm{p_y}^2 V_N(x-y) \\
& \leq \varepsilon 2\ev{\tilV} + C\norm{\ph}_{H^2}^2 \frac{1}{\varepsilon N}.
\end{align*}
\estlist{14}{2}
\begin{align*}
& \lvert \scal{\psi}{\dxyNV \frac{1}{N} a^\ast(c_x) a^\ast(p_y) k(y,x)\psi} \rvert \\
& \leq \dxyV \norm{a(c_x)\psi} \norm{a^\ast(p_y)\psi} \underbrace{\lvert k(y,x)\rvert}_{\leq\, N\lvert \ph(x)\rvert\lvert \ph(y)\rvert} \\
& \leq \dxyNV \norm{a(c_x)\psi}^2 \lvert\ph(x)\rvert^2 + \dxyNV \norm{a^\ast(p_y)\psi}^2 \lvert \ph(y)\rvert^2\\
& \leq \frac{1}{2} \norm{\ph}_\infty^2 \left( b_0 \int \di x\,\norm{a(c_x)\psi}^2 + b_0 \int \di y\,\norm{a^\ast(p_y)\psi}^2 \right) \\
& \leq C \norm{\ph}_{H^2}^2 \ev{\Ncal+1}.
\end{align*}
\estlist{15}{1}
\begin{align*}
& \lvert \scal{\psi}{\dxyNV \frac{1}{N}a^\ast(c_x)a(c_y) \scal{s_y}{s_x}\psi} \rvert \\
& \leq \dxyV \lvert \scal{s_y}{s_x}\rvert \norm{a(c_x)\psi} \norm{a(c_y)\psi} \\
& \leq \dxyV \norm{s_y} \norm{s_x} \norm{a(c_x)\psi} \norm{a(c_y)\psi} \\
& \leq \int \di x \di y\, V_N(x-y) \norm{s_y}^2 \norm{a(c_y)\psi}^2 \\
%\leq & \frac{b_0}{N} \sup_y \norm{s_y}^2 \int \di x \norm{a(c_x)\psi}^2 \\
& \leq C \norm{\ph}_{H^2}^2 \frac{1}{N}\ev{\Ncal}. 
\end{align*}
\underline{\Nestlist{15}{2} and \nestlist{15}{3}:} like \nestlist{15}{1}.\newline
\estlist{16}{1}
\begin{align*}
& \lvert \scal{\psi}{\dxyNV \frac{1}{N}a^\ast(c_x) a(s_y) \scal{c_y}{s_x}\psi} \rvert \\
& \leq \dxyV \norm{a(c_x)\psi} \norm{a(s_y)\psi} \lvert s(y,x)+\scal{p_y}{s_x} \rvert \\
& \leq \frac{C}{2}\int \di x\di y N V_N(x-y) \norm{a(c_x)\psi}^2 \lvert \ph(x)\rvert^2 + \frac{C}{2}\int \di x\di y N V_N(x-y) \norm{a(s_y)\psi}^2 \lvert \ph(y)\rvert^2\\
& \quad + \dxyV \norm{a(c_x)\psi}^2 \norm{s_x}^2 + \dxyV \norm{a(s_y)\psi}^2 \norm{p_y}^2 \\
& \leq \frac{C}{2} \norm{\ph}_\infty^2 \int \di x\, \norm{a(c_x)\psi}^2 \int \di y\, NV_N(x-y) + \frac{C}{2} \norm{\ph}_\infty^2 \int \di y\, \norm{a(s_y)\psi}^2 b_0 \\
& \quad + \frac{1}{2}\sup_x\norm{s_x}^2 \int \di x\, \norm{a(c_x)\psi}^2 \frac{b_0}{N} + \frac{1}{2} \sup_y \norm{p_y}^2 \int \di y\, \norm{a(s_y)\psi}^2 b_0/N \\
& \leq \frac{C b_0}{2} \norm{\ph}_{H^2}^2(1+\frac{1}{N})\left( \int \di x\,\norm{a(c_x)\psi}^2 + \int \di y\,\norm{a(s_y)\psi}^2 \right) \\
& \leq C\norm{\ph}_{H^2}^2 \left(1+\frac{1}{N}\right)\ev{\Ncal}.
\end{align*}
\estlist{16}{2}
\begin{align*}
& \lvert \scal{\psi}{\dxyNV \frac{1}{N} a^\ast(c_x) a(c_x)\scal{s_y}{s_y}\psi} \rvert \\
& \leq \dxyV \norm{s_y}^2 \norm{a(c_x)\psi}^2 \\
& \leq \frac{1}{2} \sup_y \norm{s_y}^2 \int \di x\, \norm{a(c_x)\psi}^2 \int \di y\, V_N(x-y) \\
& \leq C\norm{\ph}_{H^2}^2 \frac{1}{N}\ev{\Ncal}.
\end{align*}
\underline{\Nestlist{16}{3}:} like \nestlist{16}{1}.\newline
\estlist{17}{1}
\begin{align*}
 & \lvert \scal{\psi}{\dxyNV \frac{1}{N}2 a^\ast(c_x)a^\ast(s_x) \scal{s_y}{s_y}\psi} \rvert \\
& \leq \int \di x\di y\, V_N(x-y) \norm{s_y}^2 \lvert \scal{a(c_x)\psi}{a^\ast(s_x)\psi}\rvert \\
& \leq \sup_y \norm{s_y}^2 \int \di x\, \frac{b_0}{N} \norm{a(c_x)\psi}^2 + \sup_y \norm{s_y}^2 \int \di x\, \frac{b_0}{N} \norm{a^\ast(s_x)\psi}^2 \\
& \leq C \norm{\ph}_{H^2}^2 \frac{1}{N}\ev{\Ncal+1}.
\end{align*}
\underline{\Nestlist{17}{2}:} like \nestlist{17}{1}.\newline
\estlist{17}{3}
\begin{align*}
& \lvert \scal{\psi}{\dxyNV \frac{1}{N} a^\ast(c_y) a(s_x) \scal{c_y}{s_x} \psi} \rvert \\
& \leq \dxyV \lvert \scal{c_y}{s_x} \rvert \norm{a(c_y)\psi} \norm{a(s_x)\psi} \\
& \leq \frac{C}{2}\int \di x\di y N V_N(x-y) \norm{a(c_y)\psi}^2 \lvert\ph(y)\rvert^2 + \frac{C}{2}\int \di x\di y N V_N(x-y) \norm{a(s_x)\psi}^2 \lvert \ph(x)\rvert^2 \\
& \quad + \dxyV \norm{a(c_y)\psi}^2 \norm{p_y}^2 + \dxyV \norm{a(s_x)\psi}^2 \norm{s_x}^2 \\
& \leq C \norm{\ph}_{H^2}^2 \left(1+\frac{1}{N}\right)\ev{\Ncal}.
\end{align*}
\estlist{18}{1} (here, cancellation is important!)
\begin{align*}
& \lvert \scal{\psi}{\dxyNV \ph(x)\ph(y) a^\ast(c_x) a^\ast(p_y)\psi} \rvert \\
& \leq \dxyNV \lvert\ph(x)\rvert \lvert\ph(y)\rvert \norm{a(c_x)\psi} \norm{a^\ast(p_y)\psi}\\
& \leq \dxyNV \lvert \ph(x)\rvert^2 \norm{a(c_x)\psi}^2 + \dxyNV \lvert\ph(y)\rvert^2 \norm{a^\ast(p_y)\psi}^2 \\
& \leq C\norm{\ph}_{H^2}^2 \ev{\Ncal+1}. 
\end{align*}
\estlist{18}{2} %29.2
\begin{align*}
& \lvert \scal{\psi}{\dxyNV \ph(x)\ph(y) 2a^\ast(c_x)a(s_y)\psi} \rvert \\
& \leq \dxyNV \lvert\ph(x)\rvert^2 \norm{a(c_x)\psi}^2 + \dxyNV \lvert \ph(y)\rvert^2 \norm{a(s_y)\psi}^2 \\
& \leq C\norm{\ph}_{H^2}^2 \ev{\Ncal+1}.
\end{align*}
\underline{\Nestlist{18}{3} through \nestlist{20}{3}:} like \nestlist{18}{2}.\newline
\estlist{21}{1}
\begin{align*}
 & \lvert \scal{\psi}{\dxyNV \frac{2}{\sqrt{N}}\cc{\ph(y)}a^\ast(c_x)a^\ast(s_x)a^\ast(s_y)\psi} \rvert \\
& \leq \int \di x\di y\, NV_N(x-y) \lvert\ph(y)\rvert \norm{a(c_x)\psi}\frac{1}{\sqrt{N}}\norm{a^\ast(s_x)a^\ast(s_y)\psi} \\
& \leq \norm{\ph}_\infty^2 \int \di x\di y\, NV_N(x-y) \norm{a(c_x)\psi}^2 + \int \di x\di y\, NV_N(x-y) \frac{1}{N} \norm{a^\ast(s_x)a^\ast(s_y)\psi}^2 \\
& \leq \norm{\ph}_{H^2}^2 C \ev{\Ncal} + \frac{1}{N}\ev{(\Ncal+2)^2} \int \di x\di y\, NV_N(x-y) \norm{s_x}^2 \norm{s_y}^2 \\
& \leq C\norm{\ph}_{H^2}^2 \left( \ev{\Ncal} + \frac{1}{N}\ev{(\Ncal+2)^2} \right).
\end{align*}
\underline{\Nestlist{21}{2} and \nestlist{22}{1}:} like \nestlist{21}{1}.\newline
\estlist{22}{2}
\begin{align*}
 & \lvert \scal{\psi}{\dxyNV \frac{2}{\sqrt{N}}\cc{\ph(y)} a^\ast(c_x)a(c_x)a(c_y)\psi} \rvert \\
& \leq \int \di x\di y\, NV_N(x-y) \lvert \ph(y)\rvert \frac{1}{\sqrt{\varepsilon}} \norm{a(c_x)\psi} \norm{a(c_x)a(c_y)\psi} \frac{1}{\sqrt{N}}\sqrt{\varepsilon} \\
& \leq \frac{1}{\varepsilon}\int \di x\di y\, NV_N(x-y) \lvert \ph(y)\rvert^2
  \norm{a(c_x)\psi}^2 \\
& \quad  + \varepsilon \int \di x\di y\, V_N(x-y) \scal{\psi}{a^\ast(c_y)a^\ast(c_x)a(c_x)a(c_y) \psi} \\
& \leq C\norm{\ph}_{H^2}^2 \frac{1}{\varepsilon}\ev{\Ncal} + \varepsilon 4\ev{\tilV}.
\end{align*}
\estlist{22}{3}
\begin{align*}
& \lvert \scal{\psi}{\dxyNV \frac{2}{\sqrt{N}} \cc{\ph(y)}a^\ast(s_y)a(s_x)a(c_x)\psi} \rvert \\
& \leq \int \di x\di y\, NV_N(x-y) \lvert \ph(y)\rvert \norm{a(s_y)\psi} \norm{a(s_x)a(c_x)\psi}\frac{1}{\sqrt{N}} \\
& \leq \int \di x \di y\, NV_N(x-y) \lvert\ph(y)\rvert^2 \norm{a(s_y)\psi}^2 + \int \di x\di y\, NV_N(x-y) \norm{a(s_x)a(c_x)\psi}^2 \frac{1}{N} \\
& \leq \norm{\ph}_\infty^2 b_0 \norm{s}^2 \ev{\Ncal} + \frac{1}{N}b_0 \sup_x\norm{s_x}^2 \int \di x\, \norm{a(c_x)\Ncal^{1/2}\psi}^2 \\
& \leq C \norm{\ph}_{H^2}^2 \left( \ev{\Ncal} + \frac{1}{N}\ev{\Ncal^2}\right). 
\end{align*}
\underline{\Nestlist{23}{1} and \nestlist{23}{2}:} %34
like \nestlist{22}{2}.\newline
\estlist{23}{3}
\begin{align*}
& \lvert \scal{\psi}{\dxyNV \frac{2}{\sqrt{N}} \cc{\ph(y)} a(s_x) a(c_x) a(c_y)\psi} \rvert \\
& \leq \int \di x\di y\, NV_N(x-y) \lvert \ph(y)\rvert \frac{1}{\sqrt{\varepsilon}} \norm{a^\ast(s_x)\psi} \norm{a(c_x)a(c_y)\psi}\frac{1}{\sqrt{N}}\sqrt{\varepsilon} \\
& \leq \int \di x\di y\, NV_N(x-y) \lvert \ph(y)\rvert^2
  \norm{a^\ast(s_x)\psi}^2\frac{1}{\varepsilon} \\
& \quad + \int \di x\di y\, NV_N(x-y) \frac{1}{N} \scal{\psi}{a^\ast(c_y)a^\ast(c_x)a(c_x)a(c_y)\psi}\varepsilon \\
& \leq \frac{1}{\varepsilon} \norm{\ph}_\infty^2 b_0 \int \di x\, \norm{s_x}^2 \ev{\Ncal+1} + \varepsilon 4 \ev{\tilV}\\
& \leq \varepsilon 4 \ev{\tilV} + C\norm{\ph}_{H^2}^2 \frac{1}{\varepsilon}\ev{\Ncal+1}.
\end{align*}
\estlist{24}{1}
\begin{align*}
 & \lvert \scal{\psi}{\dxyNV \frac{2}{\sqrt{N}}\cc{\ph(y)}a^\ast(s_x)\scal{s_x}{s_y}\psi} \rvert \\
& \leq \int \di x\di y\, NV_N(x-y) \lvert \ph(y)\rvert \frac{1}{\sqrt{N}} \norm{s_x} \norm{s_y} \norm{\psi} \norm{a(s_x)\psi} \\
& \leq \int \di x\di y\, NV_N(x-y) \lvert \ph(y)\rvert \frac{1}{\sqrt{N}} \norm{s_x}^2 \norm{s_y} \norm{\Ncal^{1/2}\psi} \norm{\psi} \\
& \leq \sup_x \norm{s_x}^2 \frac{1}{\sqrt{N}} \int \di x\di y\, NV_N(x-y) \lvert \ph(y)\rvert \norm{s_y} \ev{\Ncal+1} \\
& \leq \sup_x \norm{s_x}^2 \frac{1}{\sqrt{N}} b_0 \ev{\Ncal+1} \left( \int \di y\, \lvert \ph(y)\rvert^2 \right)^{1/2} \left( \int \di y\, \norm{s_y}^2 \right)^{1/2} \\
& \leq C\norm{\ph}_{H^2}^2 \frac{1}{\sqrt{N}}\ev{\Ncal+1}.
\end{align*}
\underline{\Nestlist{24}{2} through \nestlist{25}{4}:} like \nestlist{24}{1}.\newline
This completes the list of estimates for the terms of $T^*_t \Lcal_N^{(0)}(t) T_t$.\vspace{1em}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

We still have to give a bound for the $(\partial_t T^*_t)T_t$-part of the generator. We will expand $(\partial_t T^*_t)T_t$ as a series and bound the summands individually, using the following lemma.
\begin{lem}
\label{lm:Bbound}
Let $f_1, f_2 \in L^2(\Rbb^3\times \Rbb^3)$. Then for all $\psi \in \fock$
 \[
\lvert \scal{\psi}{\frac{1}{2} \int \di x\di y \left( f_1(x,y) a^\ast_x a^\ast_y + f_2(x,y) a_x a_y \right) \psi} \rvert \leq \scal{\psi}{(\Ncal+1)\psi} \frac{\norm{f_1}+\norm{f_2}}{2}.
\]
and
\[
 \lvert \scal{\psi}{\frac{1}{2} \int \di x\di y \left( f_1(x,y) a^\ast_x
a_y + f_2(x,y) a_x a^\ast_y \right)  \psi} \rvert
 \leq \scal{\psi}{\Ncal\psi} \frac{\norm{f_1}+\norm{f_2}}{2} + \left\lvert \int f_2(x,x) \di x \right\rvert \frac{\scal{\psi}{\psi}}{2}.
\]
\end{lem}
\begin{proof} Proof of the first estimate, using Hoelder's inequality:
 \begin{align*}
  & \lvert \scal{\psi}{\frac{1}{2} \int \di x\di y \left( f_1(x,y) a^\ast_x a^\ast_y + f_2(x,y) a_x a_y \right) \psi} \rvert \\
& \leq \frac{1}{2} \sum_{i=1}^2 \lvert \scal{\psi}{\int \di x\di y\, f_i(x,y) a^\ast_x a^\ast_y \psi }\rvert \\
& \leq \frac{1}{2} \sum_{i=1}^2 \int \di y \norm{a_y \psi} \norm{a^\ast(f_i(\cdot,y))\psi} \\
& \leq \frac{1}{2} \sum_{i=1}^2 \left( \int \di y_1\, \norm{a_{y_1}\psi}^2 \int \di y_2\, \norm{f_i(\cdot,y_2)}^2 \norm{(\Ncal+1)^{1/2} \psi}^2 \right)^{1/2} \\
& \leq \ev{\Ncal+1} \frac{\norm{f_1}+\norm{f_2}}{2}.
 \end{align*}
Proof of the second estimate, using the CCR and Hoelder's inequality:
 \begin{align*}
& \lvert \scal{\psi}{\frac{1}{2} \int \di x\di y \left( f_1(x,y) a^\ast_x a_y + f_2(x,y) a_x a^\ast_y \right)  \psi} \rvert\\
& \leq \frac{1}{2} \lvert \scal{\psi}{\int \di x\di y\, f_1(x,y) a^\ast_x a_y \psi} \rvert + \frac{1}{2}\lvert \scal{\psi}{\int \di x \di y\, f_2(x,y) a^\ast_y a_x \psi}\rvert \\
&\quad + \frac{1}{2} \lvert \scal{\psi}{\int \di x \di y\, f_2(x,y) \delta(x-y) \psi}\rvert \\
& \leq \frac{1}{2} \int \di x\, \norm{a_x \psi} \norm{a(f_1(x,\cdot))\psi} + \frac{1}{2} \int \di y\, \norm{a_y\psi} \norm{a(f_2(\cdot,y))\psi} + \frac{1}{2} \lvert \int f_2(x,x) \di x \rvert \scal{\psi}{\psi} \\
& \leq \frac{1}{2} \left( \int \di x_1 \norm{a_{x_1}\psi}^2 \int \di x_2 \norm{f_1(x_2,\cdot)}^2 \norm{\Ncal^{1/2}\psi}^2 \right)^{1/2}\\
& \quad + \frac{1}{2} \left( \int \di x_1 \norm{a_{x_1}\psi}^2 \int \di x_2 \norm{f_2(\cdot,x_2)}^2 \norm{\Ncal^{1/2}\psi}^2 \right)^{1/2} + \frac{1}{2}\lvert \int f_2(x,x) \di x\rvert \scal{\psi}{\psi} \\
& \leq \frac{1}{2}\ev{\Ncal} \left(\left(\int \di x \norm{f_1(x,\cdot)}^2 \right)^{1/2} + \left(\int \di x \norm{f_2(\cdot,x)}^2 \right)^{1/2} \right) + \frac{1}{2}\lvert \int f_2(x,x) \di x\rvert \scal{\psi}{\psi}. 	\qedhere
 \end{align*}
\end{proof}

We now calculate and estimate the functions $f_i$ which appear in the series for $(\partial_t T^*_t)T_t$. Recall that for two operators $A$ and $B$
\[
 \ad^0_A(B) = B \qquad \mbox{and} \qquad \ad^n_A(B) = [A,\ad^{n-1}_A(B)] \mbox{ for } n \geq 1.
\]


\begin{lem}
\label{lm:highercommutators}
 For each $n \in \Nbb$ and each $i \in \{1,2\}$, there exists $f_{n,i} \in L^2(\Rbb^3 \times \Rbb^3)$ such that
\begin{itemize}
 \item \underline{for $n$ even we have}
\bd
\ad^n_B(\dot B) = \frac{1}{2} \int \di x\di y\left( f_{n,1}(x,y) a^\ast_y a^\ast_x + f_{n,2}(x,y) a_x a_y \right)
\ed
and $\norm{f_{n,i}} \leq \norm{\dot k} (2\norm{k})^n$ for all $n \in \Nbb$ and $i \in \{1,2\}$. 
 \item \underline{for $n$ odd we have}
\bd
\ad^n_B(\dot B) = \frac{1}{2} \int \di x\di y\left( f_{n,1}(x,y) a^\ast_x a_y + f_{n,2}(x,y) a_x a^\ast_y \right)
\ed
and the following bounds hold: $\norm{f_{n,i}} \leq \norm{\dot k} (2\norm{k})^n$ and $\int \lvert f_{n,i}(x,x)\rvert \di x \leq \norm{\dot k} (2\norm{k})^n$ for all $n \in \Nbb$ and $i \in \{1,2\}$. 
\end{itemize}
\end{lem}
\begin{proof} The proof is by induction in $n$. In the inductive step, we have to treat the cases of even $n$ and odd $n$ separately (but the calculations are similar).\\
\underline{basis:}\\
We take the case of $n=0$ as the basis. For
\bd
\ad^0_B(\dot B) = \dot B = \frac{1}{2}\int \di x\di y\left( \dot k(x,y) a^\ast_x a^\ast_y - \cc{\dot k(x,y)} a_x a_y \right)
\ed
the estimate stated in the even case is clearly fulfilled.\\
\underline{inductive step, starting from even $n$:}\\
We calculate (by using the CCR and appropriately renaming integration variables)
\begin{align*}
& \ad^{n+1}_B(\dot B) = [B,\ad^n_B(\dot B)] \\
& = \left[\frac{1}{2} \int \di x\di y\left( k(x,y)a^\ast_x a^\ast_y - \cc{k(x,y)}a_x a_y \right), \frac{1}{2}\int \di x\di y\left( f_{n,1}(x,y) a^\ast_x a^\ast_y + f_{n,2}(x,y) a_x a_y \right)\right] \\
& = \frac{1}{2} \int \di x\di z \left(f_{n+1,1}(x,z) a^\ast_x a_z + f_{n+1,2}(x,z) a_x a^\ast_z \right),
\end{align*}
where
\begin{equation}
\label{eq:even}
\begin{split}
f_{n+1,1}(x,z) & = -\frac{1}{2} \int \di y \left( k(x,y) \left( f_{n,2}(z,y) + f_{n,2}(y,z) \right) + \cc{k(y,z)}\left( f_{n,2}(x,y) + f_{n,2}(y,x)\right) \right)\\
f_{n+1,2}(x,z) & = -\frac{1}{2} \int \di y \left( k(y,z) \left( f_{n,1}(x,y) + f_{n,1}(y,x) \right) + \cc{k(x,y)}\left( f_{n,1}(z,y) + f_{n,1}(y,z)\right) \right), 
\end{split}
\end{equation}
so, as $n+1$ is odd, we have the correct expression for $\ad^{n+1}_B(\dot B)$. We still have to check for validity of the estimates.
Clearly
\be{normnorm}
\begin{split}
\norm{f_{n+1,1}}_{L^2} & \leq \frac{1}{2} \bigg( \norm{\int \di y\, k(x,y) f_{n,2}(z,y)}_{L^2(dxdz)} + \norm{\int \di y\, k(x,y) f_{n,2}(y,z)}_{L^2(dxdz)} \\
& \quad + \norm{\int \di y\, \cc{k(y,z)}f_{n,2}(x,y)}_{L^2(dxdz)} + \norm{\int \di y\, \cc{k(y,z)} f_{n,2}(y,x)}_{L^2(dxdz)} \bigg),
\end{split}
\ee
Using Hoelder's inequality we get
\begin{align*}
& \norm{\int \di y\,k(x,y) f_{n,2}(z,y)}^2_{L^2(dxdz)} = \int \di x\di z \left\lvert \int \di y\,k(x,y) f_{n,2}(z,y) \right\rvert^2 \\
& \leq \int \di x \di z \int \di y_1\,\lvert k(x,y_1) \rvert^2 \int \di y_2\,\lvert f_{n,2}(z,y_2) \rvert^2 = \norm{k}^2 \norm{f_{n,2}}^2. 
\end{align*}
The other three summands in \eqr{normnorm} obey the same bound, so by making use of the inductive hypothesis, we obtain
\bd
\norm{f_{n+1,1}}_{L^2} \leq \norm{\dot k} (2\norm{k})^{n+1},
\ed
which was to be proven. The calculation for $\norm{f_{n+1,2}}_{L^2}$ works the same way. We still have to proof the second estimate of the lemma, so we calculate using Hoelder's inequality that
\bd
\int \lvert f_{n+1,1}(x,x) \rvert \di x \leq 2\norm{k} \norm{f_{n,2}} \leq \norm{\dot k} (2\norm{k})^{n+1}
\ed
and in the same way $\int \lvert f_{n+1,2}(x,x) \rvert \di x \leq \norm{\dot k}(2\norm{k})^{n+1}$.\\
\underline{inductive step, starting from odd $n$:}\\
We calculate (by using the CCR and appropriately renaming integration variables)
\begin{align*}
& \ad^{n+1}_B(\dot B)\\
& = \left[ \frac{1}{2}\int \di x \di y \left( k(x,y)a^\ast_x a^\ast_y - \cc{k(x,y)} a_x a_y \right) , \frac{1}{2}\int \di x\di y \left( f_{n,1}(x,y) a^\ast_x a_y + f_{n,2}(x,y) a_x a^\ast_y \right) \right] \\
& = \frac{1}{2} \int \di x\di z \left( a^\ast_x a^\ast_z f_{n+1,1}(x,z) + a_x a_z f_{n+1,2}(x,z) \right)
\end{align*}
where
\begin{equation}
\label{eq:odd}
\begin{split}
f_{n+1,1}(x,z) & = - \int \di y\, k(x,y)\left( f_{n,1}(z,y) + f_{n,2}(y,z) \right) \\
f_{n+1,2}(x,z) & = - \int \di y\, \cc{k(x,y)}\left( f_{n,1}(y,z) + f_{n,2}(z,y) \right),
\end{split}
\end{equation}
so, as $n+1$ is even, we have the correct expression for $\ad^{n+1}_B(\dot B)$. Validity of the estimate for $\norm{f_{n+1,1}}$ and $\norm{f_{n+1,2}}$ again follows by invoking Hoelder's inequality and the inductive hypothesis.
\end{proof}

The operator $\partial_t\left((\partial_t T^*_t)T_t\right)$ can be bounded by applying $\partial_t$ to all summands of the series of $(\partial_t T^*_t)T_t$ individually and then employing lemma \ref{lm:Bbound} and the following lemma. The second estimate is only needed for odd $n$.
\begin{lem}
\label{lm:deldelt}
For all $n \in \Nbb$ and all $i \in \{1,2\}$, we have the estimates
\bd
\norm{\dot f_{n,i}} \leq 2n \norm{\dot k}^2 (2\norm{k})^{n-1} + \norm{\ddot k}(2\norm{k})^n.
\ed
For odd $n$, we have the estimate
\bd
\int \lvert \dot f_{n,i}(x,x) \rvert \di x \leq 2n \norm{\dot k}^2 (2\norm{k})^{n-1} + \norm{\ddot k}(2\norm{k})^n .
\ed
\end{lem}
\begin{proof}
The first estimate is proved by induction. The basis is trivial. For the inductive step, we again have to treat the cases of even and odd $n$ separately: We employ \eqref{eq:even} respectively \eqref{eq:odd}, use Hoelder's inequality, then make use of $\norm{f_{n,i}} \leq \norm{\dot k} (2\norm{k})^n$ and finally apply the inductive hypothesis.

For the second estimate, we use \eqref{eq:even} to express $f_{n,i}$ in terms of the $f_{n-1,i}$, use Hoelder's inequality and apply the first estimate.
\end{proof}

We now combine the bounds on the individual summands to obtain an estimate for the series.
\begin{lem}
\label{lm:timederivative}
There exists a constant $C$ independent of $N$ and $t$ such that the following estimate holds for all $t \in \Rbb$ and all $\psi \in \fock$:
 \bd
  \lvert \scal{\psi}{(\partial_t T^*_t)T_t \psi} \rvert \leq \norm{\dot k} e^{2\norm{k}} \scal{\psi}{(\Ncal+1)\psi} \leq C \norm{\ph}_{H^2}^2 \scal{\psi}{(\Ncal+1)\psi}.
 \ed
Furthermore
 \bd
    \lvert \scal{\psi}{\partial_t \left[ \left(\partial_t T^\ast_t\right) T_t \right] \psi} \rvert \leq \left( 2\norm{\dot k}^2 + \norm{\ddot k} \right) e^{2\norm{k}} \scal{\psi}{(\Ncal+1)\psi}.
 \ed
\end{lem}
\begin{proof}
The first estimate is proved by expanding the time derivative as a series,
\bd
\left(\partial_t e^{-B(t)} \right) e^{B(t)} = - \dot B(t) +
\frac{1}{2!}[B(t),\dot B(t)] - \frac{1}{3!}[B(t),[B(t),\dot B(t)]] + \dots = \sum_{n=0}^\infty \frac{(-1)^{n+1}}{(n+1)!} \ad^n_B(\dot B),
\ed
and then using the Lemmata \ref{lm:highercommutators}, \ref{lm:Bbound} and \ref{lm:kbounds}.\\
For the second estimate, differentiate the summands individually (i.\,e. place a dot on the respective $f_{n,i}$) and then estimate all summands like before, now using lemma \ref{lm:deldelt}.
\end{proof}

\section{Nonlinear Hartree and Gross-Pitaevskii equations}
The result of this appendix is the following corollary, which states uniform (i.\,e.\ independent of $N$) $H^n$ regularity for the solutions of the modified Hartree equation and, as the limiting case $N\to \infty$, the Gross-Pitaevskii equation. We will also state that solutions to the modified Hartree equation converge to solutions of the Gross-Pitaevskii equation as $N \to \infty$.

\begin{cor} \label{l:pdes} \label{c:reg1} \label{c:reg2}
  Let $\varphi \in H^n(\R^3)$ with $\| \varphi \|_{L^2} = 1$. Suppose that $f
  \in L^1(\R^3)$ and $V \in C_c^\infty(\R^3)$ with $fV \ge 0$. For $N > 0$,
  consider a solution $\varphi_t^{(N)} \in H^1(\R^3)$ of the nonlinear Hartree
  equation
  \[
    i \partial_t \varphi_t^{(N)} = - \Delta \varphi_t^{(N)} + (N f_N V_N *
    |\varphi_t^{(N)}|^2) \varphi_t^{(N)}
  \]
  with initial data $\varphi^{(N)}_0 = \varphi$, where $f_N V_N(x) = N^2
  f(Nx)V(Nx)$. Consider also a solution $\varphi_t \in H^1(\R^3)$ of the
  nonlinear Gross-Pitaevskii equation
  \[
    i \partial_t \varphi_t = - \Delta \varphi_t + 8 \pi a_0 |\varphi_t|^2
    \varphi_t
  \]
  with initial data $\varphi_0 = \varphi$, where $8 \pi a_0 = \int f V$. Then,
  for all $N > 0$ and $t \ge 0$,
  \begin{alignat}{2}
    \| \varphi_t^{(N)} \|_{H^1} & \le C_1, & \qquad \| \varphi_t \|_{H^1} &
    \le C_1, \tag{i} \label{H1} \\
    \| \varphi_t^{(N)} \|_{H^n} & \le C_n e^{K_n t}, & \qquad \| \varphi_t
    \|_{H^n} & \le C_n e^{K_n t}, \tag{ii}
  \end{alignat}
  where $C_1$ and $K_n$ are constants that depend only on $\| fV \|_{L^1}$ or
  $a_0$, and $\| \varphi \|_{H^1}$, and $C_n$ is a constant that depends only
  on $\| fV \|_{L^1}$ or $a_0$, and $\| \varphi \|_{H^n}$. Furthermore,
  \begin{equation}
    \| \varphi_t^{(N)} - \varphi_t \|_{L^2} \le \frac{C}{N} e^{e^{K t}},
    \tag{iii}
  \end{equation}
  where $C$ and $K$ are constants that depend only on $\| fV \|_{L^1}$, $a_0$
  and $\| \varphi \|_{H^2}$.
\end{cor}

Nonlinear Hartree equation
\[
  i \partial_t \varphi_t = - \Delta \varphi_t + (V * |\varphi_t|^2) \varphi_t
\]
with initial data $\varphi_0 = \varphi$, and energy
\[
  \mathcal{E}(\varphi) = \int dx \, |\nabla \varphi(x)|^2 + \frac{1}{2} \int
  dx \, (V * |\varphi|^2)(x) |\varphi(x)|^2.
\]


Nonlinear Gross-Pitaevskii equation
\[
  i \partial_t \varphi_t = - \Delta \varphi_t + 8 \pi a_0 |\varphi_t|^2
  \varphi_t
\]
with initial data $\varphi_0 = \varphi$, and energy
\[
  \mathcal{E}_{GP}(\varphi) = \int dx \, |\nabla \varphi(x)|^2 + 4 \pi a_0
  \int dx \, |\varphi(x)|^4,
\]
where $8 \pi a_0 = \int f V$.


\begin{prp} \label{p:energy}
  Let $\varphi \in H^1(\R^3)$ and $V \in L^1(\R^3)$. Then,
  \[
    \mathcal{E}(\varphi) \apprle \| \varphi \|_{H^1}^2 + \| V \|_{L^1} \|
    \varphi \|_{H^1}^4 \qquad \text{and} \qquad \mathcal{E}_{GP}(\varphi)
    \apprle \| \varphi \|_{H^1}^2 + |a_0| \| \varphi \|_{L^2} \| \varphi
    \|_{H^1}^3.
  \]
\end{prp}


\begin{proof}
  By Young's inequality, Sobolev's inequality, and H\"older's inequality, 
  \[
    \int dx \, (V * |\varphi|^2)(x) |\varphi(x)|^2 \le \| V \|_{L^1} \|
    \varphi^2 \|_{L^2}^2 = \| V \|_{L^1} \| \varphi \|_{L^4}^4 \apprle \| V
    \|_{L^1} \| \varphi \|_{H^1}^4
  \]
  and
  \[
    \int dx \, |\varphi(x)|^4 \le \| \varphi \|_{L^2} \| \varphi^3 \|_{L^2} =
    \| \varphi \|_{L^2} \| \varphi \|_{L^6}^3 \apprle \| \varphi \|_{L^2} \|
    \varphi \|_{H^1}^3.
  \]
  Observing that $\| \varphi \|_{H^1}^2 = \| \varphi \|_{L^2}^2 + \| \nabla
  \varphi \|_{L^2}^2$, we obtain the desired estimates.
\end{proof}


\subsection{Uniform $H^n$-regularity}


\begin{prp} \label{p:lregn}
  Let $\varphi \in H^n(\R^3)$ and $V \in L^1(\R^3)$ with $V \ge 0$. Consider a
  solution $\varphi_t \in H^1(\R^3)$ of the nonlinear Hartree equation
  \[
    i \partial_t \varphi_t = - \Delta \varphi_t + (V * |\varphi_t|^2)
    \varphi_t
  \]
  with initial data $\varphi_0 = \varphi$. Then, there exist constants $T > 0$
  and $C$, which depend only on $\| V \|_{L^1}$, $\| \varphi \|_{H^1}$ and
  $n$, such that
  \[
    \sup_{t \in [0,T]} \| \varphi_t \|_{H^n} \le C \| \varphi \|_{H^n} + C
    \sup_{t \in [0,T]} \| \varphi_t \|_{H^{n-1}}^3.
  \]
\end{prp}


\begin{cor} \label{c:regn}
  Under the hypothesis of Proposition \ref{p:lregn}, there exist constants
  $B_n$ and $K_n$, where $B_n$ depends only on $\| V \|_{L^1}$, $\| \varphi
  \|_{H^n}$ and $n$, and $K_n$ depends only on $\| V \|_{L^1}$, $\| \varphi
  \|_{H^1}$ and $n$, such that, for all $t \ge 0$,
  \[
    \| \varphi_t \|_{H^1} \le B_1 \qquad \text{and} \qquad \| \varphi_t
    \|_{H^n} \le B_n e^{K_n t}.
  \]
\end{cor}

The proof of Proposition \ref{p:lregn} is based on well-known Strichartz
estimates for the free Schr\"odinger evolution and the following lemma.


For $T > 0$ set
\[
  L_t^q L_x^r = L^q([0,T], L^r(\R^3)).
\]


\begin{lem} \label{l:interp}
  Let $V \in L^1(\R^3)$, $f \in L_t^{q_1} L_x^{r_1}$ and $g \in L_t^{q_2}
  L_x^{r_2}$ with $q_j, r_j \in [1,\infty]$ for $j \in \{1,2\}$. Then $(V * f)
  g \in L_t^q L_x^r$ with $q^{-1} = s^{-1} + q_1^{-1} + q_2^{-1}$ and $r^{-1}
  = r_1^{-1} + r_2^{-1}$ for $s \in [1, \infty]$. Furthermore,
  \[
    \| (V * f)g \|_{L_t^q L_x^r} \le \| V \|_{L^1} T^{1/s} \| f \|_{L_t^{q_1}
    L_x^{r_1}} \| g \|_{L_t^{q_2} L_x^{r_2}}.
  \]
\end{lem}


\begin{proof}
  Applying H\"older's inequality in space, and then in time, we find that
  \[
    \| (V * f) g \|_{L_t^q L_x^r} \le \| V * f \|_{L_t^u L_x^{r_1}} \| g
    \|_{L_t^{q_2} L_x^{r_2}}
  \]
  with $q^{-1} = u^{-1} + q_2^{-1}$ and $r^{-1} = r_1^{-1} + r_2^{-1}$. Now,
  applying Young's inequality in space, H\"older's inequality in time, and
  observing that $V$ is time-independent, we get
  \[
    \| V * f \|_{L_t^u L_x^{r_1}} \le \| V \|_{L^1} T^{1/s} \| f \|_{L_t^{q_1}
    L_x^{r_1}}
  \]
  with $u^{-1} = s^{-1} + q_1^{-1}$. Combining all this we obtain the desired
  result.
\end{proof}


\begin{proof}[Proof of Proposition \ref{p:lregn}]
  By Duhamel's principle, the nonlinear Hartree equation is reformulated as an integral equation:
  \[
    \varphi_t = e^{it\Delta} \varphi - i \int_0^t ds \, e^{i(t-s)\Delta} (V *
    |\varphi_s|^2) \varphi_s.
  \]
  Differentiating this equation w.\,r.\,t.\ the spatial variables and using integration by parts we find that
  \[
    \partial^\alpha \varphi_t = e^{it \Delta} \partial^\alpha \varphi - i
    \int_0^t ds \, e^{i(t-s) \Delta} \sum_{\beta \le \alpha} \sum_{\nu \le
    \beta} \binom{\alpha}{\beta} \binom{\beta}{\nu} \big( V * (\partial^\nu
    \overline{\varphi_s} \partial^{\beta - \nu} \varphi_s) \big)
    \partial^{\alpha - \beta} \varphi_s.
  \]
  Here $\alpha$ is a three-dimensional multi-index of non-negative integers,
  and we are using standard multi-index notation. The length of a multi-index
  $\gamma$ is defined as $|\gamma| = \gamma_1 + \gamma_2 + \gamma_3$.


  The $L_t^\infty L_x^2$-norm of the above expression can be controlled using
  Strichartz estimates for the free Schr\"odinger evolution $e^{it\Delta}$
  (see \cite[Theorem 1.2]{KT}). By these estimates, triangle inequality, Lemma
  \ref{l:interp}, and H\"older's inequality,
  \begin{equation} \label{Dphi}
    \begin{split}
      & \| \partial^\alpha \varphi_{(\cdot)} \|_{L_t^\infty L_x^2} - \|
      \partial^\alpha \varphi \|_{L^2} \\
      & \le \sum_{\beta \le \alpha} \sum_{\nu \le \beta} \binom{\alpha}{\beta}
      \binom{\beta}{\nu} \| \big( V * (\partial^\nu
      \overline{\varphi_{(\cdot)}} \partial^{\beta - \nu} \varphi_{(\cdot)})
      \big) \partial^{\alpha - \beta} \varphi_{(\cdot)} \|_{L_t^2 L_x^{6/5}}
      \\
      & \le \| V \|_{L^1} T^{1/2} \sum_{\beta \le \alpha} \sum_{\nu \le \beta}
      \binom{\alpha}{\beta} \binom{\beta}{\nu} \sup_{t \in [0,T]} \|
      \partial^\nu \varphi_t \|_{L^{p_1}} \| \partial^{\beta - \nu} \varphi_t
      \|_{L^{p_2}} \sup_{t \in [0,T]} \| \partial^{\alpha - \beta} \varphi_t
      \|_{L^{p_3}}
    \end{split}
  \end{equation}
  with $p_1^{-1} + p_2^{-1} + p_3^{-1} = 5/6$. Note that $(p_1, p_2, p_3)$ can
  be chosen differently for each term in the summation. We will appropriatedly
  choose it to be either $(2,6,6)$, $(6,2,6)$ or $(6,6,2)$, as we describe
  next.


  Consider a term in \eqref{Dphi}, and consider the order of each partial
  derivative in it: $|\nu|$, $|\beta-\nu|$ and $|\alpha-\beta|$. Then choose
  $p_j = 2$ for one of the $p_j$'s corresponding to the derivatives of highest
  order, and choose the other two $p_j$'s equal to $6$. For the factors with
  $p_j = 6$, use the estimate
  \[
    \| \partial^\gamma \varphi_t \|_{L^6} \le \| \varphi_t \|_{W^{|\gamma|,6}}
    \apprle \| \varphi_t \|_{H^{|\gamma|+1}},
  \]
  which holds for any multi-index $\gamma$. This follows from the definition
  of Sobolev norm and Sobolev's inequality. For the factor with $p_j = 2$,
  simply note that
  \[
    \| \partial^\gamma \varphi_t \|_{L^2} \le \| \varphi_t \|_{H^{|\gamma|}}.
  \]


  Now, consider a term that has a factor with derivative of highest order
  $|\alpha| - k$, where $k$ is an integer such that $0 \le k \le |\alpha| -
  2$, and let $\gamma_1$ and $\gamma_2$ be the multi-indexes in the
  derivatives of the other two factors in this term. Note that $|\gamma_1 +
  \gamma_2|=k$ so that $|\gamma_1| \le k$ and $|\gamma_2| \le k$. Hence, using
  the above estimates to bound the factor with highest order derivative and
  the other two factors, we conclude that the term under consideration is
  bounded by
  \begin{align*}
    & \apprle \sup_{t \in [0,T]} \| \varphi_t \|_{H^{|\gamma_1|+1}} \sup_{t
    \in [0,T]} \| \varphi_t \|_{H^{|\gamma_2|+1}} \sup_{t \in [0,T]} \|
    \varphi_t \|_{H^{|\alpha|-k}} \\
    & \le \sup_{t \in [0,T]} \| \varphi_t \|_{H^{|k|+1}}^2 \sup_{t \in [0,T]}
    \| \varphi_t \|_{H^{|\alpha|-k}}.
  \end{align*}
  Observe that, by varying $k$ in the range $0 \le k \le |\alpha|-2$, we can
  estimate all terms in \eqref{Dphi}. In fact, it follows that
  \begin{equation} \label{dal}
    \begin{split}
      & \sup_{t \in [0,T]} \| \partial^\alpha \varphi_t \|_{L^2} \\
      & \le \| \partial^\alpha \varphi \|_{L^2} + C_1 4^{|\alpha|} \| V
      \|_{L^1} T^{1/2} \Big[ \sup_{t \in [0,T]} \| \varphi_t \|_{H^1}^2
      \sup_{t \in [0,T]} \| \varphi_t \|_{H^{|\alpha|}} + \sup_{t \in [0,T]}
      \| \varphi_t \|_{H^{|\alpha|-1}}^3 \Big]
    \end{split}
  \end{equation}
  for some universal constant $C_1$. By Corollary \ref{c:reg1}, there is a
  constant $C_2$, depending only on $\| V \|_{L^1}$ and $\| \varphi \|_{H^1}$,
  such that $\| \varphi_t \|_{H^1} \le C_2$. Furthermore, there are universal
  constants $c$ and $C$ such that
  \[
    c \sum_{|\alpha| \le n} \| \partial^\alpha f \|_{L^2} \le \| f \|_{H^n}
    \le C \sum_{|\alpha| \le n} \| \partial^\alpha f \|_{L^2}.
  \]
  Thus, by summing \eqref{dal} over $|\alpha| \le n$, we obtain
  \[
    \sup_{t \in [0,T]} \| \varphi_t \|_{H^n} \le C_1 \| \varphi \|_{H^n} + C_2
    T^{1/2} 4^n n \Big[ \sup_{t \in [0,T]} \| \varphi_t \|_{H^n} + \sup_{t \in
    [0,T]} \| \varphi_t \|_{H^{n-1}}^3 \Big]
  \]
  for some constants $C_1$ and $C_2$ as above. Therefore, by choosing $T > 0$
  sufficiently small, but depending only on $\| V \|_{L^1}$, $\| \varphi
  \|_{H^1}$ and $n$, we conclude that
  \[
    \sup_{t \in [0,T_n]} \| \varphi_t \|_{H^n} \le C \| \varphi \|_{H^n} + C
    \sup_{t \in [0,T_n]} \| \varphi_t \|_{H^{n-1}}^3,
  \]
  where $C$ is a constant that depends only on $\| V \|_{L^1}$, $\| \varphi
  \|_{H^1}$ and $n$.
\end{proof}


\begin{proof}[Proof of Corollary \ref{c:regn}]
  For simplicity, we will omit the dependence of the constants with respect to
  $\| V \|_{L^1}$. Recall that $V \ge 0$. By conservation of mass and energy,
  and by Proposition \ref{p:energy},
  \[
    \| \varphi_t \|_{H^1}^2 \le \| \varphi_t \|_{L^2}^2 +
    \mathcal{E}(\varphi_t) = 1 + \mathcal{E}(\varphi) \apprle \| \varphi
    \|_{H^1}^2 + \| V \|_{L^1} \| \varphi \|_{H^1}^4 \eqqcolon B_1^2.
  \]
  This proves the first estimate in the corollary.


  We now prove that $\| \varphi_t \|_{H^n} \le B_n e^{K_n t}$ by induction in
  $n$. First observe that, from the above estimate, it follows trivially that
  $\| \varphi_t \|_{H^1} \le B_1 e^{K_1 t}$ for some constants $B_1$ and $K_1$
  that depend only on $\| \varphi \|_{H^1}$. This proves the desired estimate
  for $n=1$.


  Suppose that $\| \varphi_t \|_{H^{n-1}} \le B_{n-1} e^{K_{n-1} t}$, where
  $B_{n-1}$ is a constant that depends only on $\| \varphi \|_{H^{n-1}}$ and
  $n-1$, and $K_{n-1}$ is a constant that depends only on $\| \varphi
  \|_{H^1}$ and $n-1$. In view of Proposition \ref{p:lregn}, for any $t > 0$,
  we can find an integer $j$ sufficiently large, depending only on $\|
  \varphi_{(j-1)T} \|_{H^1}$ and $n$, such that $0 < t/j < T$.
  Consequently,
  \begin{align*}
    \| \varphi_t \|_{H^n} & \le \sup_{s \in [(j-1)T, jT]} \| \varphi_s
    \|_{H^n} \\
    & \le C \| \varphi_{(j-1)T} \|_{H^n} + C \sup_{s \in [(j-1)T,
    jT]} \| \varphi_s \|_{H^{n-1}}^3 \\
    & \le C \| \varphi_{(j-1)T} \|_{H^n} + C B_{n-1}^3 e^{3 K_{n-1} j
    T},
  \end{align*}
  where $C$ is a constant that depends only on $\| \varphi_{(j-1)T}
  \|_{H^1}$ and $n$. Now observe that, since $\| \varphi_{(j-1)T} \|_{H^1}
  \le B_1$, the constants $T$ and $C$ can be chosen uniformly in time. Thus,
  we can iterate de above expression $j$ times to cover the interval $[0,t]$
  and obtain
  \begin{align*}
    \| \varphi_t \|_{H^n} & \le C^j \| \varphi \|_{H^n} + C B_n^3
    \sum_{l=1}^j e^{3 K_{n-1} (j-l+1)T} \\
    & \le (C^{2T^{-1}})^t \| \varphi \|_{H^n} + C B_{n-1}^3
    \frac{2t}{T} e^{3 K_{n-1} t} \le B_n e^{K_n t},
  \end{align*}
  for some constant $B_n$ depending only on $\| V \|_{L^1}$, $\| \varphi
  \|_{H^n}$ and $n$, and some constant $K_n$ depending only on $\| V
  \|_{L^1}$, $\| \varphi \|_{H^1}$ and $n$. This completes the induction step
  and the proof of the corollary.
\end{proof}


\subsection{$\ph$ converges to $\varphi_t$ in $L^2$}


\begin{lem}
\label{lem:phitN2phit}
  Let $\varphi \in H^2(\R^3)$ with $\| \varphi \|_{L^2} = 1$. Suppose that $f
  \in L^1(\R^3)$ and $V \in C_c^\infty(\R^3)$ with $fV \ge 0$. For $N > 0$,
  consider a solution $\varphi_t^{(N)} \in H^1(\R^3)$ of the nonlinear Hartree
  equation
  \[
    i \partial_t \varphi_t^{(N)} = - \Delta \varphi_t^{(N)} + (N f_N V_N *
    |\varphi_t^{(N)}|^2) \varphi_t^{(N)}
  \]
  with initial data $\varphi^{(N)}_0 = \varphi$, where $f_N V_N(x) = N^2
  f(Nx)V(Nx)$. Consider also a solution $\varphi_t \in H^1(\R^3)$ of the
  nonlinear Gross-Pitaevskii equation
  \[
    i \partial_t \varphi_t = - \Delta \varphi_t + 8 \pi a_0 |\varphi_t|^2
    \varphi_t
  \]
  with initial data $\varphi_0 = \varphi$, where $8 \pi a_0 = \int f V$. Then,
  for all $N > 0$ and $t \ge 0$,
  \[
    \| \varphi_t^{(N)} - \varphi_t \|_{L^2} \le \frac{C}{N} e^{e^{K t}},
  \]
  where $C$ and $K$ are constants that depend only on $\| fV \|_{L^1}$,
  $a_0$ and $\| \varphi \|_{H^2}$.
\end{lem}


\begin{proof}
  Observing that $\langle \Delta \varphi_t, \varphi_t^{(N)} \rangle = \langle
  \varphi_t, \Delta \varphi_t^{(N)} \rangle$, we easily find
  \begin{equation}\label{ddt}
    \begin{aligned}
      \partial_t \| \varphi_t - \varphi_t^{(N)} \|_{L^2}^2 & = -2 \Im \langle
      \varphi_t, (N f_N V_N * |\varphi_t^{(N)}|^2 - 8 \pi a_0 |\varphi_t|^2)
      \varphi_t^{(N)} \rangle \\
      & = 2 \Im \langle \varphi_t, (N f_N V_N * |\varphi_t^{(N)}|^2 - 8 \pi
      a_0 |\varphi_t|^2) (\varphi_t - \varphi_t^{(N)}) \rangle \\
      & = 2 \Im \langle \varphi_t, (N f_N V_N * |\varphi_t|^2 - 8 \pi a_0
      |\varphi_t|^2) (\varphi_t - \varphi_t^{(N)}) \rangle \\
      & \quad + 2 \Im \langle \varphi_t, N f_N V_N * (|\varphi_t^{(N)}|^2 -
      |\varphi_t|^2) (\varphi_t - \varphi_t^{(N)}) \rangle.
    \end{aligned}
  \end{equation}
  In order to apply Gronwall's inequality, we next estimate each term in this
  expression.


  By H\"older's and Sobolev's inequalities,
  \begin{align*}
    & |\langle \varphi_t, (N f_N V_N * |\varphi_t|^2 - 8 \pi a_0
    |\varphi_t|^2) (\varphi_t - \varphi_t^{(N)}) \rangle| \\
    & \qquad \le \| \varphi_t \|_{L^6} \| (N f_N V_N * |\varphi_t|^2 - 8 \pi
    a_0 |\varphi_t|^2) (\varphi_t - \varphi_t^{(N)}) \|_{L^{6/5}} \\
    & \qquad \apprle \| \varphi_t \|_{H^1} (\| \varphi_t \|_{L^2} + \|
    \varphi_t^{(N)} \|_{L^2}) \| N f_N V_N * |\varphi_t|^2 - 8 \pi a_0
    |\varphi_t|^2 \|_{L^3}.
  \end{align*}
  By triangle inequality, Sobolev's inequality, and Young's inequality,
  \begin{align*}
    & |\langle \varphi_t, N f_N V_N * (|\varphi_t^{(N)}|^2 - |\varphi_t|^2)
    (\varphi_t - \varphi_t^{(N)}) \rangle| \\
    & \le \int dx dy \, |\varphi_t(x)| |\varphi_t(x) - \varphi_t^{(N)}(x)| N
    f_N V_N(x-y) (|\varphi_t^{(N)}(y)| + |\varphi_t(y)|) |\varphi_t^{(N)}(y) -
    \varphi_t(y)| \\
    & \le \| \varphi_t \|_{L^\infty} ( \| \varphi_t^{(N)} \|_{L^\infty} + \|
    \varphi_t \|_{L^\infty} ) \int dx dy \, |\varphi_t(x) -
    \varphi_t^{(N)}(x)| N f_N V_N(x-y) |\varphi_t^{(N)}(y) - \varphi_t(y)| \\
    & \apprle \| \varphi_t \|_{H^2} ( \| \varphi_t^{(N)} \|_{H^2} + \|
    \varphi_t \|_{H^2} ) \| fV \|_{L^1} \| \varphi_t^{(N)} - \varphi_t
    \|_{L^2}^2.
  \end{align*}
  Thus, substituting all this into \eqref{ddt}, and using Corollaries
  \ref{c:regn} and \ref{c:reg2} to estimate $\| \varphi_t^{(N)} \|_{H^1}$, $\|
  \varphi_t^{(N)} \|_{H^2}$, $\| \varphi_t \|_{H^1}$ and $\| \varphi_t
  \|_{H^2}$, we obtain
  \begin{equation} \label{endproof2}
    \partial_t \| \varphi_t^{(N)} - \varphi_t \|_{L^2}^2 \le C \| \varphi
    \|_{H^2}^2 e^{Kt} \| \varphi_t^{(N)} - \varphi_t \|_{L^2}^2 + C \| N f_N
    V_N * |\varphi_t|^2 - 8 \pi a_0 |\varphi_t|^2 \|_{L^3},
  \end{equation}
  where $C$ and $K$ are constants that depend only on $\| fV \|_{L^1}$ and $\|
  \varphi \|_{H^1}$. We are left to estimating the second term in
  \eqref{endproof2}.


  Write
  \begin{align*}
    N f_N V_N * |\varphi_t|^2(x) - 8 \pi a_0 |\varphi_t|^2(x) & = \int dy
    \big( |\varphi_t(x-y)|^2 - |\varphi_t(x)|^2 \big) N^3 fV(Ny) \\
    & = \int dz \big( |\varphi_t(x-z/N)|^2 - |\varphi_t(x)|^2 \big) fV(z),
  \end{align*}
  and let $R$ be such that $\text{supp} \ V \subset \{ x \in \R^3 \; | \;\;
  |x| \le R \}$. By Minkowski's, H\"older's, and Sobolev's inequalities,
  \begin{align*}
    \| N f_N V_N * |\varphi_t|^2 - 8 \pi a_0 |\varphi_t|^2 \|_{L^3} & \le \int
    dz \, \| |\varphi_t(\, \cdot \, -z/N)|^2 - |\varphi_t|^2 \|_{L^3} |fV(z)|
    \\
    & \le \| fV \|_{L^1} \sup_{|z| \le R} \| |\varphi_t(\, \cdot \, - z/N)|^2
    - |\varphi_t|^2 \|_{L^3}.
  \end{align*}
  Given $\varepsilon = 1/N$, there exists $\psi_t \in C^\infty(\R^3)$ such
  that $\| \varphi_t - \psi_t \|_{H^2} < 1/N$. Hence, by H\"older's
  inequality, Sobolev's inequality and an $\varepsilon/3$-argument, the mean
  value theorem (with some constant $0 \le c \le 1$), and Sobolev's inequality
  again,
  \begin{align*}
    \| |\varphi_t(\, \cdot \, - z/N)|^2 - |\varphi_t|^2 \|_{L^3} & \le 2 \|
    \varphi_t \|_{L^6} \| |\varphi_t(\, \cdot \, - z/N)| - |\varphi_t|
    \|_{L^6} \\
    & \apprle \| \varphi_t \|_{H^1} \big( 1/N + \| |\psi_t(\, \cdot \, - z/N)|
    - |\psi_t| \|_{L^6} \big) \\
    & \apprle \| \varphi_t \|_{H^1} \big( 1/N + |z|/N \| \nabla |\psi_t(\,
    \cdot \, - c z/N)| \|_{L^6} \big) \\
    & \apprle \| \varphi_t \|_{H^1} \big( 1/N + |z|/N \| \psi_t \|_{H^2}
    \big) \\
    & \apprle \| \varphi_t \|_{H^1} \big( 1/N + |z|/N^2 + |z|/N \| \varphi_t
    \|_{H^2} \big).
  \end{align*}
  Therefore, using again Corollary \ref{c:reg2},
  \begin{align*}
    & \| N f_N V_N * |\varphi_t|^2 - 8 \pi a_0 |\varphi_t|^2 \|_{L^3} \\
    & \apprle \| fV \|_{L^1} \| \varphi_t \|_{H^1} \Big( \frac{1}{N} +
    \frac{R}{N^2} + \frac{R}{N} \| \varphi_t \|_{H^2} \Big) \le
    \frac{C}{N}(1 + \| \varphi_t \|_{H^2}) \le \frac{2C}{N} \| \varphi
    \|_{H^2} e^{Kt},
  \end{align*}
  where $C$ is a constant that depends only on $\| fV \|_{L^1}$, $a_0$ and $\|
  \varphi \|_{H^1}$. Substituting this into \eqref{endproof2}, we obtain
  \[
    \partial_t \| \varphi_t^{(N)} - \varphi_t \|_{L^2}^2 \le C e^{Kt} \|
    \varphi_t^{(N)} - \varphi_t \|_{L^2}^2 + \frac{C}{N} e^{Kt}.
  \]
  Finally, by Gronwall's inequality,
  \[
    \| \varphi_t^{(N)} - \varphi_t \|_{L^2} \le e^{K^{-1} C e^{Kt}} \Big( \|
    \varphi_0^{(N)} - \varphi_0 \|_{L^2} + \frac{C}{KN} e^{Kt} \Big) \le
    \frac{C_2}{N} e^{e^{K_2 t}},
  \]
  for some constants $C_2$ and $K_2$ depending only on $\| fV \|_{L^1}$,
  $a_0$, and $\| \varphi \|_{H^2}$.
\end{proof}


\subsection{Regularity of $\phdot$ and $\phddot$}


\begin{lem} \label{lm:phdotregularity}
Let $\ph$ be a solution of the modified Hartree equation
\be{modHartree}
i \phdot = -\Delta \ph + \left(N f_N V_N \ast \lvert \ph \rvert^2 \right) \ph.
\ee
Then there exists a constant $C$ independent of $N$ and $t$ such that:
\begin{enumerate}
 \item $\norm{\phdot}_{L^2} \leq \norm{\ph}_{H^2} + 8\pi a_0 \norm{\ph}_{H^2}^2 \leq C \norm{\ph}_{H^2}^2.$
\item Furthermore, for $i, j \in \{1,2,3\}$,
\bd
\norm{\nabla \phdot}_{L^2} \leq C \norm{\ph}_{H^3}^2, \quad
\norm{\partial_i \partial_j \phdot}_{L^2} \leq C \norm{\ph}_{H^4}^3, \quad \norm{\phdot}_\infty \leq C \norm{\ph}_{H^4}^3
\ed
\item and \bd
\norm{\phddot}_{L^2} \leq C \norm{\ph}_{H^4}^4.
\ed
\end{enumerate}
\end{lem}
\begin{proof}(i) According to \eqr{modHartree}, we get
\be{no11}
\norm{\phdot}_{L^2} \leq \norm{\ph}_{H^2} + \norm{\left(N f_N V_N \ast \lvert \ph\rvert^2 \right)\ph}_{L^2}.
\ee
Now we calculate
\begin{align*}
\norm{\left(N f_N V_N \ast \lvert \ph\rvert^2 \right)\ph}_{L^2}^2 & = \int \di x\, \lvert \ph(x)\rvert^2 \left\lvert \int \di y\, N f_NV_N(x-y) \lvert \ph(y)\rvert^2 \right\rvert^2 \\
& \leq \int \di x\, \lvert \ph(x)\rvert^2 \left\lvert \norm{\ph}_\infty^2 \int \di y\, N f_N V_N(x-y) \right\rvert^2 \\
& \leq \norm{\ph}_{L^2}^2 \norm{\ph}_\infty^4 (8\pi a_0)^2.
\end{align*}
This combined with \eqr{no11} proves (i).

(ii)
Applying the gradient $\nabla$ to the modified Hartree equation, the product rule yields
\begin{align}
i \nabla \phdot & = - \nabla \Delta \ph + \left( N f_N V_N \ast \lvert \ph \rvert^2 \right) \nabla \ph \label{eq:firstline}\\
& \quad + \left( N f_N \ast \cc{\ph} \nabla \ph \right) \ph + \left( N f_N V_N \ast \cc{\nabla \ph} \ph \right) \ph. \label{eq:secondline}
\end{align}
Clearly, $\norm{\nabla \Delta \ph}_{L^2} \leq \norm{\ph}_{H^3}$. Now for line \eqref{eq:firstline}, we have the estimate
\begin{align*}
\norm{\left( N f_N V_N \ast \lvert \ph \rvert^2 \right)\nabla \ph}_{L^2}^2 & = \int \di x \lvert \nabla \ph(x)\rvert^2 \left\lvert \int \di y N f_N V_N(y) \lvert\ph(x-y) \rvert^2\right\rvert^2\\
& \leq \int \di x \lvert \nabla \ph(x)\rvert^2 \norm{\ph}_\infty^4 \left\lvert \int \di y N f_N V_N(y) \right\rvert^2 \\
& = \norm{\nabla \ph}_{L^2}^2 \norm{\ph}_\infty^4 (8 \pi a_0)^2. 
\end{align*}
Similarly, we show that the $L^2$-norms of the summands in line \eqref{eq:secondline} are both bounded by $C \norm{\ph}_{H^2}^2 \norm{\ph}_{H^3}^2$. We then conclude that
\bd
\norm{\nabla \phdot}_{L^2} \leq \norm{\ph}_{H^3} + C \norm{\nabla \ph}_{L^2} \norm{\ph}_\infty^2 + C \norm{\ph}_{H^2} \norm{\ph}_{H^3} \leq C \norm{\ph}_{H^3}^2.
\ed
The bound for $\norm{\partial_i \partial_j \phdot}_{L^2}$ is proven by the same strategy. Now the bound for $\norm{\phdot}_\infty$ is a consequence of the fact that the $L^\infty$-norm can be estimated by the $H^2$-norm through a Sobolev inequality.

(iii) To prove that $\phddot$ is in $L^2$, we apply $i\partial_t$ to the modified Hartree equation \eqr{modHartree} and get
\begin{align*}
ii\phddot & = - \Delta i \phdot + \left( N f_N V_N \ast \cc{\ph}i \phdot \right) \ph \\
& \quad + \left( N f_N V_N \ast \cc{(-i\phdot)} \ph \right) \ph + \left( N f_N V_N \ast \lvert\ph\rvert^2 \right) i\phdot.
\end{align*}
Now for $i\phdot$ we plug in the modified Hartree equation and arrive at
\begin{align*}
ii \phddot & = \Delta^2 \ph - \Delta \left( (N f_N V_N \ast \lvert \ph\rvert^2)\ph \right) + \left( N f_N V_N \ast \lvert \ph\rvert^2 \right)^2 \ph \\
& + (N f_N V_N \ast \cc{\ph}(-\Delta \ph))\ph + 2 \left[ N f_N V_N \ast \left( \lvert \ph\rvert^2 (N f_N V_N \ast \lvert \ph\rvert^2) \right) \right] \ph \\
& + (N f_N V_N \ast \cc{(-\Delta \ph)} \ph)\ph + \left( N f_N V_N \ast \lvert \ph \rvert^2 \right)(-\Delta \ph).
\end{align*}
The $L^2$-norms of the summands on the right hand side can be estimated by the same methods as in (i) and (ii), e.\,g.\ 
\begin{align*}
 \norm{\left( N f_N V_N \ast \lvert \ph\rvert^2 \right) \Delta \ph}^2 & = \int \di x \lvert \Delta \ph(x)\rvert^2 \left\lvert \int \di y\, N f_N V_N(y) \lvert \ph(x-y) \rvert^2 \right\rvert^2 \\
& \leq \norm{\ph}_\infty^4 (8 \pi a_0)^2 \norm{\Delta \ph}_{L^2}^2 \leq C \norm{\ph}_{H^4}^6.
\end{align*}
(Actually, the $H^2$-norm is enough for this term, but we need the $H^4$-norm anyway for some of the other summands.)
\end{proof}

\begin{lem} \label{lm:kbounds} Let $k(x,y) = -N w_N(x-y) \ph(x) \ph(y)$ with $\ph$ a solution of the modified Hartree equation \eqr{modHartree}. Then there exists a constant $C$ independent of $N$ and $t$ such that:
\bd
\norm{\dot k} \leq C \norm{\ph}_{H^2}^2
 \quad \mbox{and} \quad
\norm{\ddot k} \leq C \norm{\ph}_{H^4}^4.
\ed
\end{lem}
\begin{proof} (i) We use Hardy's inequality and Lemma \ref{lm:phdotregularity} to estimate
\begin{align*}
\norm{\dot k}^2 & = \int \di x\di y\, \left\lvert \frac{\di}{\di t} \left( -N w_N(x-y) \ph(x)\ph(y) \right) \right\rvert^2 \\
& \leq 2 \int \di x\di y\, \lvert N w_N(x-y) \phdot(x) \ph(y) \rvert^2 + 2 \int \di x \di y\, \lvert N w_N(x-y) \ph(x) \phdot(y) \rvert^2 \\
& \leq 4 \left( \max\{R,a_0\} \right)^2 \int \di x\di y\, \lvert \phdot(x)\rvert^2 \frac{\lvert\ph(y)\rvert^2}{\lvert x-y\rvert^2} \\
& \leq 16 \left( \max\{R,a_0\} \right)^2 \int \di x\di y\, \lvert \phdot(x)\rvert^2 \lvert \nabla_y \ph(y)\rvert^2 \\
& \leq \left( 4 \max\{R,a_0\} \right)^2 \norm{\phdot}_{L^2}^2 \norm{\ph}_{H^1}^2 \leq C \norm{\ph}_{H^2}^4.
\end{align*}

(ii) First, we use $\lvert N w_N(x-y) \rvert \leq \max \{R,a_0\} \lvert x-y\rvert^{-1}$ and Hardy's inequality to show
\bd
\norm{\ddot k} \leq C \norm{\phddot}_{L^2} + C \norm{\phdot}_{L^2} \norm{\nabla \phdot}_{L^2}.
\ed
Employing Lemma \ref{lm:phdotregularity} the proof is finished.
\end{proof}

\section{Bounds for the Bogoliubov Transformation}
\begin{lem}
\label{lem:dottedests1}
Let $p$ and $s$ be the integral kernels defined in Lemma \ref{l:bt}. Then, the following estimates hold:
\begin{enumerate}
\item If $k_t \in L^2(\Rbb^3\times\Rbb^3)$ is an arbitraty time-dependent integral kernel then
\bd
\norm{\dot p} \leq \norm{\dot k} \cosh(\norm{k}) \quad \mbox{and} \quad \norm{\dot s} \leq \norm{\dot k} \cosh(\norm{k}).
\ed
\item If $k(x,y) = - N w_N(x-y) \ph(x) \ph(y)$ with $\ph$ a solution of the modified Hartree equation, then there exists a constant $C$ independent of $N$ and $t$ such that
\bd
\norm{\dot p} \leq C \norm{\ph}_{H^2}^2 \quad \mbox{and} \quad \norm{\dot s} \leq C \norm{\ph}_{H^2}^2
\ed
\item
and
\bd
\sup_x \norm{\dot p_x}_{L^2} \leq C \norm{\ph}_{H^4}^3 \quad \mbox{and} \quad \sup_x \norm{\dot s_x}_{L^2} \leq C \norm{\ph}_{H^4}^3.
\ed
\end{enumerate}
\end{lem}
\begin{proof} (i) Differentiate the summands of the series individually and make use of the estimate $\norm{fg}_{L^2} \leq \norm{f}_{L^2} \norm{g}_{L^2}$ for $f,g \in L^2(\Rbb^3\times \Rbb^3)$.

(ii) Use (i) and employ the estimates $\norm{k} \leq C$ and $\norm{\dot k} \leq C \norm{\ph}_{H^2}^2$ (see Lemma \ref{lm:kbounds}).

(iii) Notice that for functions $f_i \in L^2(\Rbb^3 \times \Rbb^3)$, $i=1,\dots n$, by Hoelder's inequality we have the estimate
\begin{align*}
\norm{\left[ f_1 f_2 \cdots f_n\right]_x}^2 & = \int \di y \left\lvert \int \di z_1 \cdots \di z_{n-1}\ f_1(y,z_1) f_2(z_1,z_2) \cdots f_n(z_{n-1},x) \right\rvert^2 \\
& \leq \norm{f_1}^2 \norm{f_2}^2 \cdots \norm{f_{n-1}}^2 \int \di z_{n-1} \lvert f_n(z_{n-1},x) \rvert^2 
\end{align*}
(notice that on the lhs $\norm{\cdot}= \norm{\cdot}_{L^2(\Rbb^3)}$, while on the rhs $\norm{\cdot} = \norm{\cdot}_{L^2(\Rbb^3\times\Rbb^3)}$).
For $f_n = k$ or $f_n = \cc{k}$ we use Hardy's inequality to prove $\int \di z_{n-1} \lvert f_n(z_{n-1},x) \rvert^2 \leq C \lvert \ph(x) \rvert^2 \norm{\nabla \ph}^2$. For $f_n = \cc{\dot k}$, again by Hardy's inequality, we have the estimate $\int \di z_{n-1} \lvert f_n(z_{n-1},x) \rvert^2 \leq C\lvert \ph(x)\rvert^2 \norm{\nabla \phdot}^2 + C \lvert \phdot(x)\rvert^2 \norm{\nabla \ph}^2$. Then use the Lemmata \ref{lm:phdotregularity} and \ref{lm:kbounds} and the fact that $\norm{\ph}_{H^1} \leq C$ by Corollary \ref{c:regn}.
\end{proof}

\begin{lem}
\label{lem:dottedests2}
Let $k(x,y) = -N w_N(x-y) \ph(x) \ph(y)$, where $\ph$ is a solution of the modified Hartree equation. Then there exists a constant $C$ independent of $N$ and $t$ such that
\begin{enumerate}
 \item
\bd
\int \di x \di y \frac{1}{N} V_N(x-y) \lvert \dot k(x,y)\rvert^2 \leq C \norm{\ph}_{H^3}^4
\ed 
 \item
\bd
\int \di x\di y\, V_N(x-y) \lvert \dot r(x,y)\rvert^2 \leq \frac{C}{N} \norm{\ph}_{H^3}^4 \norm{\ph}_{H^2}^2
\ed
 \item
\bd
\int \di x\di y\frac{1}{N} V_N(x-y) \lvert \dot s(x,y)\rvert^2 \leq C \norm{\ph}_{H^3}^4 + \frac{C}{N^2} \norm{\ph}_{H^3}^4 \norm{\ph}_{H^2}^2.
\ed
\end{enumerate}
Notice that in (i) and (iii) compared to (ii) an additional $1/N$ is required because $s$ is more singular than $r$.
\end{lem}
\begin{proof} (iii) is a trivial corollary from (i) and (ii).

(i) The calculation works as follows:
\begin{align*}
& \int \di x\di y \frac{1}{N}V_N(x-y) \lvert \dot k(x,y)\rvert^2 \\
& = \int \di x\di y \frac{1}{N} V_N(x-y) \lvert -N w_N(x-y) \phdot(x) \ph(y) - N w_N(x-y) \ph(x) \phdot(y)\rvert^2 \\
& \leq \frac{4}{N} \int \di x\di y V_N(x-y) \lvert N w_N(x-y) \rvert^2 \lvert \phdot(x)\rvert^2 \lvert \ph(y)\rvert^2 \\
& = 4 \int \di x \di y N^3V(N(x-y)) w(N(x-y))^2 \lvert \phdot(x)\rvert^2 \lvert \ph(y)\rvert^2 \\
& \leq 4 \norm{N^3 V(N(\cdot))w(N(\cdot))^2}_{L^1} \norm{\lvert\phdot\rvert^2}_{L^2} \norm{\lvert \ph\rvert^2}_{L^2}.
\end{align*}
In the last step, Young's inequality was used. Now by substituting $Nx = z$ and using $\lvert w(z)\rvert \leq 1$ we have
\bd
\norm{N^3 V(N(\cdot))w(N(\cdot))^2}_{L^1} = \int \di x N^3 V(Nx)w(Nx)^2 = \int \di z V(z) w(z)^2 \leq \int \di z V(z) = b_0.
\ed
Furthermore, by Sobolev inequality and using the Lemma \ref{lm:phdotregularity} on regularity of $\phdot$ we get
\bd
\norm{\lvert \phdot\rvert^2}_{L^2} = \norm{\phdot}_{L^4}^2 \leq C \norm{\phdot}_{H^1}^2 \leq C(\norm{\ph}_{H^2}^2 + \norm{\ph}_{H^3}^2)^2 \leq C \norm{\ph}_{H^3}^4.
\ed
Also by a Sobolev inequality $\norm{\lvert \ph\rvert^2}_{L^2} \leq C$ because $\norm{\ph}_{H^1} \leq C$.

(ii) By induction in $n$, one first proves that for the concetanation of integral kernels $f_1, \dots f_n \in L^2(\Rbb^3\times\Rbb^3)$ the following estimate holds:
\bd
\lvert (f_1 \cdots f_N)(x,y)\rvert \leq \left( \int \di z \lvert f_1(x,z)\rvert^2 \right)^{1/2} \left( \int \di z \lvert f_n(z,y)\rvert^2\right)^{1/2} \norm{f_2} \cdots \norm{f_{n-1}}.
\ed
We now apply this to
\be{no2}
\begin{split}
& \lvert \dot r(x,y) \rvert = \left\lvert \sum_{n=1}^\infty \frac{1}{(2n+1)!} \partial_t \left(k(\cc k k)^n \right)(x,y)\right\rvert \\
& \leq \sum_{n=1}^\infty \frac{1}{(2n+1)!} \bigg\lvert\Big( \dot k(\cc k k)^n + \sum_{j=1}^{n-1} k(\cc k k)^{j-1}(\cc{\dot k}k + \cc k \dot k)(\cc k k)^{n-j} + k (\cc k k)^{n-1} \cc{\dot k} k + k(\cc{k}k)^{n-1}\cc{k}\dot k \Big)(x,y)\bigg\rvert \\
& \leq \left(\int \di z \lvert \dot k(x,z)\rvert^2 \right)^{1/2} \left( \int \di z \lvert k(z,y)\rvert^2 \right)^{1/2} \sum_{n=1}^\infty \frac{\norm{k}^{2n-1}}{(2n+1)!} \\
& \quad + \norm{\dot k} \left( \int \di z \lvert k(x,z)\rvert^2 \right)^{1/2} \left( \int \di z \lvert k(z,y)\rvert^2 \right)^{1/2} \sum_{n=1}^\infty \frac{\norm{k}^{2n-2}}{(2n+1)!} (2n-1) \\
& \quad + \left( \int \di z \lvert k(x,z)\rvert^2 \right)^{1/2} \left( \int \di z \lvert \dot k(z,y)\rvert^2 \right)^{1/2} \sum_{n=1}^\infty \frac{\norm{k}^{2n-1}}{(2n+1)!}.
\end{split}
\ee
As $\norm{k}$ can be bounded by a constant $C$ independent of $N$ and $t$, so can the series appearing here (clearly, the series are summable). From Lemma \ref{lm:kbounds} we know that $\norm{\dot k} \leq C \norm{\ph}_{H^2}^2$. Using Hardy's inequality, one can easily show that
\bd
\int \di z \lvert k(x,z)\rvert^2 \leq \lvert \ph(x)\rvert^2 C
\ed
and
\bd
\int \di z \lvert \dot k(x,z)\rvert^2 \leq \lvert \ph(x)\rvert^2 C \norm{\nabla \phdot}_{L^2}^2 + \lvert \phdot(x)\rvert^2 C \norm{\nabla \ph}_{L^2}^2.
\ed
These estimates and the estimate \eqr{no2} for $\lvert \dot r(x,y)\rvert$ are now used to conclude
\begin{align*}
& \int \di x \di y V_N(x-y) \lvert \dot r(x,y)\rvert^2 \\
& \leq C \int \di x \di y V_N(x-y) \int \di z_1 \lvert \dot k(x,z_1)\rvert^2 \int \di z_2 \lvert k(z_2,y)\rvert^2 \\
& \quad + C \norm{\ph}_{H^2}^4 \int \di x \di y V_N(x-y) \int \di z_1 \lvert k(x,z_1)\rvert^2 \int \di z_2 \lvert k(z_2,y)\rvert^2 \\
& \leq C \norm{\nabla \phdot}_{L^2}^2 \int \di x \di y V_N(x-y) \lvert \ph(x)\rvert^2 \lvert \ph(y)\rvert^2 \\
& \quad + C \norm{\nabla \ph}_{L^2}^2 \int \di x \di y V_N(x-y) \lvert \phdot(x)\rvert^2 \lvert \ph(y)\rvert^2 \\
& \quad + C \norm{\ph}_{H^2}^4 \int \di x \di y V_N(x-y) \lvert \ph(x)\rvert^2 \lvert \ph(y)\rvert^2.
\end{align*}
In each summand, we can pull out $\norm{\ph}_\infty^2$ and use Lemma \ref{lm:phdotregularity} to conclude the proof.
\end{proof}

\begin{lem}
\label{lem:dottedests3}
Let $k(x,y) = -N w_N(x-y) \ph(x)\ph(y)$ where $\ph$ is a solution to the modified Hartree equation. Then there exists a constant $C$ such that
\bd
\norm{\nabla_1 \dot p} \leq C \norm{\ph}_{H^3}^2 \quad \mbox{and} \quad \norm{\nabla _1 \dot r} \leq C \norm{\ph}_{H^3}^2.
\ed
\end{lem}
\begin{proof}
 This is an application of Hoelder's inequality for convolution of integral kernels
\be{hoelder}
\norm{f_1 \cdots f_n} \leq \norm{f_1} \cdots \norm{f_n}.
\ee
It has to be noticed, that $\norm{\nabla_1 k} \sim N^{1/2}$, which is not desired. Therefore, we always have to keep $\norm{\nabla_1 k \cc k}$, which is of order $N^0$ according to Lemma \ref{l:kernels} \ref{k}.

Estimate for $\nabla_1 \dot p$ (the proof for $\nabla_1 \dot r$ works similarly and will be omitted):
\bd
\nabla_1 \dot p = \frac{\partial}{\partial_t} \left( \sum_{n=1}^\infty (\nabla_1 k)\cc k (k \cc k)^{n-1} \frac{1}{(2n)!} \right).
\ed
Notice that $\nabla_1$ acts only on the first $k$. After using the product rule for the time derivative and \eqr{hoelder} we have the estimate
\bd
\norm{\nabla_1 \dot p} \leq C \left(\norm{\nabla_1 \dot k \cc k} + \norm{\nabla_1 k \cc{\dot k}} + \norm{\nabla_1 k \cc{k}}\norm{\dot k} \right),
\ed
where summable series depending on $\norm{k}$ where absorbed in $C$.

We are left with the task of giving an estimate for $\nabla_1 \dot k \cc k$ (an estimate for $\nabla_1 k \cc{\dot k}$ is proven in the same way). We start by applying the product rule:
\begin{align}
& \norm{\nabla_1 \dot k \cc k}^2 \nonumber \\
& = \int \di x \di y \bigg\lvert \int \nabla_x\left( N w_N(x-z) \phdot(x) \ph(z) + N w_N(x-z) \ph(x) \phdot(z) \right) \times \nonumber \\
& \qquad\qquad\qquad \times N w_N(z-y) \cc{\ph(z)} \cc{\ph(y)} \di z \bigg\rvert^2 \nonumber \\
& \leq 4 \int \di x \di y \left\lvert \int N \nabla w_N(x-z) \phdot(x) \lvert\ph(z)\rvert^2 \cc{\ph(y)} N w_N(z-y) \di z \right\rvert^2 \label{eq:kk1} \\
& \quad + 4 \int \di x \di y \left\lvert N w_N(x-z) \nabla_x \phdot(x) \lvert \ph(z)\rvert^2 \cc{\ph(y)} N w_N(z-y) \di z \right\rvert^2 \label{eq:kk2}\\
& \quad + 4 \int \di x \di y \left\lvert N \nabla w_N(x-z) \ph(x) \phdot(z) \cc{\ph(z)} \cc{\ph(y)} N w_N(z-y) \di z \right\rvert^2 \label{eq:kk3}\\
& \quad + 4 \int \di x \di y \left\lvert N w_N(x-z) \nabla \ph(x) \phdot(z)\cc{\ph(z)} \cc{\ph(y)} N w_N(z-y) \right\rvert^2. \label{eq:kk4}
\end{align}

We now prove estimates for these four terms. For the summands \eqref{eq:kk2} and \eqref{eq:kk4}, this is the usual application of Hardy's inequality; both terms are bounded by $C \norm{\nabla \phdot}_{L^2}^2$.
For \eqref{eq:kk1} and \eqref{eq:kk3} it is a non-trivial task to find an estimate because $\nabla w_N$ has a stronger singularity than $w_N$. We will show the proof for \eqref{eq:kk1}; the proof for \eqref{eq:kk3} works similarly and yields the bound $C \norm{\nabla \phdot}_{L^2}^2$.\\
\underline{Bound for \eqref{eq:kk1}}:
\begin{align*}
\eqref{eq:kk1} & \leq C \int \di x \di y \left\lvert \int \di z \frac{1}{\lvert x-z\rvert^2} \phdot(x) \lvert \ph(z)\rvert^2 \cc{\ph(y)} \frac{1}{\lvert z-y\rvert} \right\rvert^2 \\
& = C \int \di x \di y \di z_1 \di z_2 \frac{\lvert\phdot(x)\rvert^2 \lvert \ph(y)\rvert^2 \lvert \ph(z_1)\rvert^2 \lvert \ph(z_2)\rvert^2}{\lvert z_1-y\rvert \lvert z_2 -y\rvert \lvert x-z_1\rvert^2 \lvert x-z_2\rvert^2} \\
& = C \int \di x \lvert\phdot(x)\rvert^2 \int \di z_1 \di z_2 \frac{\lvert \ph(z_1)\rvert^2 \lvert \ph(z_2)\rvert^2}{\lvert x-z_1\rvert^2 \lvert x-z_2\rvert^2} \int \di y \frac{\lvert \ph(y)\rvert^2}{\lvert z_1-y\rvert \lvert z_2 - y\rvert}
\end{align*}
The integral w.\,r.\ to $y$ can be bounded by $C \norm{\nabla \ph}_{L^2}^2$ using Hoelder's inequality and then Hardy's inequality. Using $\norm{\nabla \ph}_{L^2}^2 \leq C$ we get
\bd
\eqref{eq:kk1} \leq C \int \di x \lvert\phdot(x)\rvert^2 \int \di z_1 \frac{\lvert \ph(z_1)\rvert^2 }{\lvert x-z_1\rvert^2 } \int \di z_2 \frac{\lvert \ph(z_2)\rvert^2}{\lvert x-z_2\rvert^2}
\ed
and by Hardy's inequality, this is bounded by
\bd
\leq C \int \di x \lvert \phdot(x)\rvert^2 \norm{\nabla \ph}_{L^2}^2 \norm{\nabla \ph}_{L^2}^2 \leq C \norm{\phdot}_{L^2}^2. \qedhere
\ed
\end{proof}


\bibliographystyle{plain}
\bibliography{gross-pitaevskii}


\end{document}
